---
title: "combine_forecast_obs_WOW"
author: "Wenkai_Zhong"
date: "2025-07-25"
output: html_document
---

############################### before run this file u should run three individual data import files first (forecast,obs,wow)#######################################
#Visualise all offical stations, cities and wow stations
```{r}
# Load required libraries
library(ggplot2)
library(ggrepel)
library(dplyr)
library(maps)
library(mapdata)

# Create the combined map
gridpoint_station_map <- ggplot() +
  # Add Netherlands boundary using maps package
  borders("world", regions = "Netherlands", 
          fill = NA, colour = "black", size = 0.8) +
  
  # Connection lines between gridpoints and stations
  geom_segment(data = gridpoint_station_table,
               aes(x = gp_lon, y = gp_lat, xend = sta_lon, yend = sta_lat),
               alpha = 0.3) +
  
  # Plot gridpoint points (dark blue squares)
  geom_point(data = gridpoint_station_table,
             aes(x = gp_lon, y = gp_lat, shape = "Gridpoints"),
             color = "darkblue", size = 3, alpha = 0.6) +
  
  # Plot primary stations (red circles)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "primary"),
             aes(x = sta_lon, y = sta_lat, shape = "Primary Stations"),
             color = "red", size = 3, alpha = 0.6) +
  
  # Plot secondary stations (yellow triangles)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat, shape = "Secondary Stations"),
             color = "gold", size = 3, alpha = 0.6) +
  
  # Plot WOW stations (green diamonds)
  geom_point(data = unique_stations,
             aes(x = Longitude, y = Latitude, shape = "WOW Stations"),
             color = "darkgreen", size = 2.5, alpha = 0.3) +
  
  # Plot cities with size based on population rank
  geom_point(data = cities,
             aes(x = city_lon, y = city_lat, shape = "Cities", 
                 size = 26 - population_rank),  # Larger size for higher ranked cities
             color = "purple", alpha = 0.8) +
  
  # Set shapes for all point types
  scale_shape_manual(values = c("Gridpoints" = 15,           # Square
                               "Primary Stations" = 16,       # Circle
                               "Secondary Stations" = 17,     # Triangle
                               "WOW Stations" = 18,          # Diamond
                               "Cities" = 19),               # Solid circle
                     name = "Type") +
  
  # Set size scale for cities
  scale_size_continuous(range = c(2, 6), guide = "none") +
  
  # Add gridpoint labels
  geom_text_repel(data = gridpoint_station_table,
                  aes(x = gp_lon, y = gp_lat, label = gridpoint),
                  size = 2.5,
                  color = "darkblue",
                  box.padding = 0.3,
                  point.padding = 0.2,
                  max.overlaps = 20) +
  
  # Add primary station labels
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "primary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "red",
                  nudge_y = 0.02,
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  # Add secondary station labels
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "secondary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "gold",
                  nudge_y = -0.02,
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  # Add city labels (for all cities)
  geom_text_repel(data = cities,
                  aes(x = city_lon, y = city_lat, label = city),
                  size = 2.5,
                  color = "purple",
                  fontface = "bold",
                  box.padding = 0.2,
                  point.padding = 0.2,
                  segment.size = 0.3,
                  segment.alpha = 0.5,
                  max.overlaps = 30,
                  force = 2) +
  
  # Titles and labels
  labs(title = "Weather Observation Network in the Netherlands",
       subtitle = "ECMWF Gridpoints, KNMI Stations (Primary/Secondary), WOW Stations, and Major Cities",
       x = "Longitude",
       y = "Latitude",
       caption = "Cities sized by population rank | WOW stations in green") +
  
  # Theme settings
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "horizontal",
        legend.text = element_text(size = 8),
        plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 10),
        plot.caption = element_text(hjust = 0.5, size = 8, face = "italic")) +
  
  # Set coordinate limits to focus on Netherlands
  coord_cartesian(xlim = c(3.3, 7.3), ylim = c(50.7, 53.6))

# Display the map
gridpoint_station_map

```
#find 1 official station and 5 WOW stations that cloese to big cities
```{r}
library(geosphere)

create_city_station_connections <- function(date_str, n_wow_stations = 5) {
  
  cat("Creating city-station connection table for", date_str, "...\n")
  
  # 1. Get WOW stations for this date
  unique_stations <- get_unique_wow_stations(date_str)
  
  # 2. Check if there are enough WOW stations
  if (nrow(unique_stations) < n_wow_stations) {
    warning(paste("Insufficient WOW stations! Only", nrow(unique_stations), "stations available"))
    n_wow_stations <- nrow(unique_stations)
  }
  
  # 3. Create base city_connections (if not already exists)
  # Assumes city_connections already exists with city and nearest official station info
  # If not, need to create it first
  
  # 4. Add WOW station information to city_connections
  city_connections_with_wow <- city_connections %>%
    rowwise() %>%
    mutate(
      # Calculate distances to all WOW stations
      wow_distances = list(
        distHaversine(
          cbind(city_lon, city_lat), 
          cbind(unique_stations$Longitude, unique_stations$Latitude)
        ) / 1000  # Convert to kilometers
      ),
      # Find indices of nearest n stations
      nearest_wow_idx = list(order(wow_distances)[1:min(n_wow_stations, length(wow_distances))]),
      # Get distances of nearest stations
      nearest_wow_distances = list(wow_distances[nearest_wow_idx]),
      # Get coordinates of nearest stations
      nearest_wow_lat = list(unique_stations$Latitude[nearest_wow_idx]),
      nearest_wow_lon = list(unique_stations$Longitude[nearest_wow_idx]),
      # Add date marker
      wow_data_date = date_str
    ) %>%
    ungroup() %>%
    select(-wow_distances)  # Remove complete distance list
  
  # 5. Add useful summary information
  city_connections_with_wow <- city_connections_with_wow %>%
    mutate(
      # Distance to nearest WOW station
      closest_wow_distance = sapply(nearest_wow_distances, function(x) x[1]),
      # Whether WOW station is closer than official station
      wow_closer_than_official = closest_wow_distance < distance_km,
      # Distance improvement
      distance_improvement = distance_km - closest_wow_distance
    )
  
  # 6. Print summary statistics
  cat("\n===== Summary Statistics =====\n")
  cat("Date:", date_str, "\n")
  cat("Number of cities:", nrow(city_connections_with_wow), "\n")
  cat("Total WOW stations:", nrow(unique_stations), "\n")
  cat("WOW stations connected per city:", n_wow_stations, "\n")
  
  wow_better <- sum(city_connections_with_wow$wow_closer_than_official)
  cat("\nCities where WOW is closer than official:", wow_better, "/", nrow(city_connections_with_wow), "\n")
  cat("Average distance improvement:", 
      round(mean(city_connections_with_wow$distance_improvement[city_connections_with_wow$wow_closer_than_official]), 2), 
      "km\n")
  
  return(city_connections_with_wow)
}

#usage
city_connections_summer <- create_city_station_connections("2022-07-15")
city_connections_summer
```
#plot cities and its 5 closest WOW stations and 1 official station

```{r}
# Function to create city-station connection map
plot_city_station_connections <- function(city_connections_data, selected_cities = NULL) {
  
  # If specific cities are selected, filter the data
  if (!is.null(selected_cities)) {
    city_connections_data <- city_connections_data %>%
      filter(city %in% selected_cities)
  }
  
  # Prepare WOW stations data for plotting
  wow_stations_plot <- city_connections_data %>%
    select(city, nearest_wow_lat, nearest_wow_lon, nearest_wow_distances) %>%
    unnest(c(nearest_wow_lat, nearest_wow_lon, nearest_wow_distances)) %>%
    group_by(city) %>%
    mutate(
      wow_rank = row_number(),
      station_label = paste0("W", wow_rank)
    ) %>%
    ungroup()
  
  # Create the map
  city_station_map <- ggplot() +
    # Add Netherlands boundary
    borders("world", regions = "Netherlands", 
            fill = NA, colour = "black", size = 0.8) +
    
    # Connection lines from cities to official stations
    geom_segment(data = city_connections_data,
                 aes(x = city_lon, y = city_lat, 
                     xend = station_lon, yend = station_lat),
                 color = "red", alpha = 0.3, linetype = "solid", size = 0.8) +
    
    # Connection lines from cities to WOW stations
    geom_segment(data = wow_stations_plot,
                 aes(x = city_connections_data$city_lon[match(city, city_connections_data$city)], 
                     y = city_connections_data$city_lat[match(city, city_connections_data$city)], 
                     xend = nearest_wow_lon, yend = nearest_wow_lat),
                 color = "darkgreen", alpha = 0.2, linetype = "dashed", size = 0.5) +
    
    # Plot official stations (red circles)
    geom_point(data = city_connections_data,
               aes(x = station_lon, y = station_lat, shape = "Official Stations"),
               color = "red", size = 3, alpha = 0.8) +
    
    # Plot WOW stations (green diamonds)
    geom_point(data = wow_stations_plot,
               aes(x = nearest_wow_lon, y = nearest_wow_lat, shape = "WOW Stations"),
               color = "darkgreen", size = 2.5, alpha = 0.6) +
    
    # Plot cities (purple circles, sized by population)
    geom_point(data = city_connections_data,
               aes(x = city_lon, y = city_lat, shape = "Cities"),
               color = "purple", alpha = 0.8,size = 3.5) +
    
    # Set shapes
    scale_shape_manual(values = c("Official Stations" = 16,    # Circle
                                 "WOW Stations" = 18,          # Diamond
                                 "Cities" = 19),               # Solid circle
                       name = "Type") +
    
    # Set size scale for cities
    scale_size_continuous(range = c(3, 7), guide = "none") +
    
    # Add city labels
    geom_text_repel(data = city_connections_data,
                    aes(x = city_lon, y = city_lat, label = city),
                    size = 3,
                    color = "purple",
                    fontface = "bold",
                    box.padding = 0.3,
                    point.padding = 0.3,
                    max.overlaps = 30) +
    
    # Add official station labels
    geom_text_repel(data = city_connections_data,
                    aes(x = station_lon, y = station_lat, 
                        label = paste0("S", nearest_idx)),
                    size = 2,
                    color = "red",
                    box.padding = 0.2,
                    point.padding = 0.1,
                    max.overlaps = 20) +
    
    # Titles and labels
    labs(title = paste("City-Station Connections -", unique(city_connections_data$wow_data_date)),
         subtitle = "Cities with nearest Official Station (red) and 5 closest WOW Stations (green)",
         x = "Longitude",
         y = "Latitude",
         caption = "Solid lines: City to Official Station | Dashed lines: City to WOW Stations") +
    
    # Theme settings
    theme_minimal() +
    theme(legend.position = "bottom",
          legend.box = "horizontal",
          legend.text = element_text(size = 8),
          plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
          plot.subtitle = element_text(hjust = 0.5, size = 10),
          plot.caption = element_text(hjust = 0.5, size = 8, face = "italic")) +
    
    # Set coordinate limits to focus on Netherlands
    coord_cartesian(xlim = c(3.3, 7.3), ylim = c(50.7, 53.6))
  
  return(city_station_map)
}


#plot all
map_all <- plot_city_station_connections(city_connections_summer)
print(map_all)
```
#function to calcualte humudity and wet bulb  temprature
```{r}
e <- function(T) {
  6.112 * exp((17.67 * T) / (T + 243.5))
}

get_rh <- function(temp_C, dew_C) {
  100 * e(dew_C) / e(temp_C)
}

#stull equation
get_wbt <- function(temp_C, RH) {
  RH <- pmax(pmin(RH, 100), 1)
  T <- temp_C
  T_w <- T * atan(0.151977 * sqrt(RH + 8.313659)) +
         atan(T + RH) -
         atan(RH - 1.676331) +
         0.00391838 * RH^(3/2) * atan(0.023101 * RH) -
         4.686035
  return(T_w)
}
```


#combine forecast with obs
```{r}
combine_forecast_obs <- function(date_str, 
                               gridpoint_id, 
                               lead_time_hours = NULL,
                               aggregate_obs = "hourly",
                               include_metadata = TRUE) {
 
 # Get forecast data for the specified date and gridpoint
 forecast_data <- tidy_forecast_with_station_grid_location(date_str, gridpoint_id)
 
 ####### Import observation data for 10 days starting from date_str
 # Convert date_str to Date object
 start_date <- as.Date(date_str)
 
 # Initialize list to store observation data
 all_obs_data <- list()
 
 # Loop through 10 days
 for (i in 0:9) {
   current_date <- start_date + i
   current_date_str <- format(current_date, "%Y-%m-%d")
   
   tryCatch({
     # Import observation data for current date
     daily_obs <- import_knmi_data(current_date_str)
     all_obs_data[[current_date_str]] <- daily_obs
   })
 }
 
 # Combine all observation data
 if (length(all_obs_data) > 0) {
   obs_data <- bind_rows(all_obs_data)
 } else {
   warning("No observation data found for any date")
   return(forecast_data)
 }
 
 # Extract station_id from forecast data
 station_id <- unique(forecast_data$station_id)
 
 # Check if station_id exists
 if(is.na(station_id) || length(station_id) == 0) {
   warning("No station_id found for this gridpoint")
   return(forecast_data)
 }
 
 # Filter observation data for the specific station
 pattern <- paste0("^", station_id, "_")
 
 obs_filtered <- obs_data %>%
   filter(grepl(pattern, LOCATION)) %>%
   # Convert DTG to POSIXct to match forecast data format
   mutate(DTG = as.POSIXct(DTG, tz = "UTC"))
 
 # Check if any observations found
 if(nrow(obs_filtered) == 0) {
   warning(paste("No observations found for station", station_id))
   return(forecast_data)
 }
 
 # Ensure Valid_datetime is POSIXct
 forecast_data$Valid_datetime <- as.POSIXct(forecast_data$Valid_datetime, tz = "UTC")
 
 # Join observation data to forecast data
 combined_data <- forecast_data %>%
   left_join(
     obs_filtered,
     by = c("Valid_datetime" = "DTG"),
     suffix = c("_forecast", "_obs")
   )
 
 #add humudity 
 combined_data <- combined_data %>%
  mutate(
    Relative_humidity_pct = get_rh(Temperature_C,DewPoint_C),
    RH_10 = get_rh(T_DRYB_10,T_DEWP_10)
  )%>%
 relocate(Relative_humidity_pct, .before = Gridpoint_ID)%>%
 relocate(RH_10, .before = U_10)
  
 return(combined_data)
}

# Usage example
combined <- combine_forecast_obs("2021-01-31 12:00:00", 605)
combined
```

##############################combine all data (WOW,official,forecast)#######################################

```{r}
combine_forecast_obs_wow <- function(date_str, 
                                     gridpoint_id, 
                                     lead_time_hours = NULL,
                                     aggregate_obs = "hourly",
                                     include_metadata = TRUE,
                                     n_wow_stations = 5) {

  # Step 1: Use existing function to get forecast + KNMI obs + RH columns
  combined_data <- combine_forecast_obs(
    date_str = date_str,
    gridpoint_id = gridpoint_id,
    lead_time_hours = lead_time_hours,
    aggregate_obs = aggregate_obs,
    include_metadata = include_metadata
  )

  # Step 2: Extract gridpoint coordinates for WOW search
  gridpoint_lat <- unique(combined_data$gridpoint_lat)[1]
  gridpoint_lon <- unique(combined_data$gridpoint_lon)[1]

  # Step 3: Import WOW data over 10 days
  start_date <- as.Date(date_str)
  all_wow_data <- list()

  for (i in 0:9) {
    current_date <- start_date + i
    current_date_str <- format(current_date, "%Y-%m-%d")

    tryCatch({
      wow_obs <- import_WOW_nearest_stations(
        current_date_str, 
        gridpoint_lat, 
        gridpoint_lon, 
        n_stations = n_wow_stations
      )
      if (!is.null(wow_obs)) {
        all_wow_data[[current_date_str]] <- wow_obs
      }
    }, error = function(e) {
      warning(paste("Failed to import WOW data for", current_date_str))
    })
  }

  # Step 4: Process WOW data
  if (length(all_wow_data) > 0) {
    wow_combined <- bind_rows(all_wow_data)

    # Detect station ID column
    station_id_col <- NULL
    if ("ExternalSiteId" %in% names(wow_combined)) {
      station_id_col <- "ExternalSiteId"
    } else if ("SiteId" %in% names(wow_combined)) {
      station_id_col <- "SiteId"
    } else if ("SiteName" %in% names(wow_combined)) {
      station_id_col <- "SiteName"
    } else if ("StationId" %in% names(wow_combined)) {
      station_id_col <- "StationId"
    } else {
      wow_combined <- wow_combined %>%
        mutate(StationId = paste(Latitude, Longitude, sep = "_"))
      station_id_col <- "StationId"
    }

    # Step 5: Aggregate WOW data
    wow_aggregated <- wow_combined %>%
      mutate(
        Valid_datetime = floor_date(ReportEndDateTime, "hour"),
        DryBulbTemperature_Celsius = as.numeric(DryBulbTemperature_Celsius),
        RelativeHumidity = as.numeric(RelativeHumidity),
        DewPointTemperature_Celsius = as.numeric(DewPointTemperature_Celsius)
      ) %>%
      group_by(Valid_datetime) %>%
      summarise(
        wow_temp_mean = mean(DryBulbTemperature_Celsius, na.rm = TRUE),
        wow_temp_sd = sd(DryBulbTemperature_Celsius, na.rm = TRUE),
        wow_temp_min = min(DryBulbTemperature_Celsius, na.rm = TRUE),
        wow_temp_max = max(DryBulbTemperature_Celsius, na.rm = TRUE),
        wow_humidity_mean = mean(RelativeHumidity, na.rm = TRUE),
        wow_dewpoint_mean = mean(DewPointTemperature_Celsius, na.rm = TRUE),
        wow_n_stations = n_distinct(!!sym(station_id_col)),
        wow_n_obs = n(),
        .groups = "drop"
      ) %>%
      mutate(across(where(is.numeric), ~ifelse(is.infinite(.), NA, .))) %>%
      mutate(
        wow_wetbulb_mean = case_when(
          !is.na(wow_temp_mean) & !is.na(wow_humidity_mean) ~ 
            wow_temp_mean * atan(0.151977 * sqrt(wow_humidity_mean + 8.313659)) + 
            atan(wow_temp_mean + wow_humidity_mean) - 
            atan(wow_humidity_mean - 1.676331) + 
            0.00391838 * wow_humidity_mean^(3/2) * atan(0.023101 * wow_humidity_mean) - 
            4.686035,
          TRUE ~ NA_real_
        )
      )

    # Step 6: Join WOW data to combined forecast+obs
    combined_data <- combined_data %>%
      left_join(wow_aggregated, by = "Valid_datetime")

    # Summary
    cat("\nWOW data summary:\n")
    cat("Total WOW observations included:", sum(wow_aggregated$wow_n_obs, na.rm = TRUE), "\n")
    cat("Average stations per hour:", round(mean(wow_aggregated$wow_n_stations, na.rm = TRUE), 1), "\n")
    cat("Temperature coverage:", 
        round(sum(!is.na(wow_aggregated$wow_temp_mean)) / nrow(wow_aggregated) * 100, 1), 
        "% of hours\n")
    cat("Wet bulb temperature coverage:", 
        round(sum(!is.na(wow_aggregated$wow_wetbulb_mean)) / nrow(wow_aggregated) * 100, 1), 
        "% of hours\n")
  }

  # Final metadata
  cat("\nForecast period:", min(combined_data$Valid_datetime), "to", max(combined_data$Valid_datetime), "\n")
  cat("Grid point:", gridpoint_id, "at", round(gridpoint_lat, 2), "N,", round(gridpoint_lon, 2), "E\n")
  cat("Official station:", unique(combined_data$station_id)[1], "\n")

  return(combined_data)
}

# Usage example
combined <- combine_forecast_obs_wow("2021-01-31 12:00:00", 605, n_wow_stations = 5)
combined


combined2 <- combine_forecast_obs_wow("2022-01-28 00:00:00", 605, n_wow_stations = 5)
combined2
```
#data combination visualisation !!!!!!!!!!!!!!!!!!!!!!!!!!
```{r}
plot_forecast_obs_wow_spaghetti <- function(forecast_datetime, 
                                            gridpoint_id, 
                                            variable = "Temperature_C", 
                                            members = 1:51,
                                            n_wow_stations = 5,
                                            show_mean = FALSE) {
  
  # Variable mapping for available data
  var_mapping <- list(
    "Temperature_C" = list(
      forecast = "Temperature_C",
      obs = "T_DRYB_10",
      wow = "wow_temp_mean",
      label = "Temperature (°C)"
    ),
    "Humidity_pct" = list(
      forecast = "Relative_humidity_pct",  
      obs = "RH_10",
      wow = "wow_humidity_mean",
      label = "Relative Humidity (%)"
    )
  )
  
  if (!variable %in% names(var_mapping)) {
    stop(paste("Invalid variable:", variable, 
               ". Valid options are:", paste(names(var_mapping), collapse = ", ")))
  }
  
  var_info <- var_mapping[[variable]]
  forecast_var_name <- var_info$forecast
  obs_var_name <- var_info$obs
  wow_var_name <- var_info$wow
  y_label <- var_info$label
  
  # Get the combined forecast, official obs, and WOW data
  cat("Fetching combined data...\n")
  combined <- combine_forecast_obs_wow(
    date_str = forecast_datetime, 
    gridpoint_id = gridpoint_id,
    n_wow_stations = n_wow_stations
  )
  
  if (is.null(combined) || nrow(combined) == 0) {
    warning(paste("No combined data found for", forecast_datetime, "at gridpoint", gridpoint_id))
    return(NULL)
  }
  
  # Check if forecast variable exists
  if (!forecast_var_name %in% names(combined)) {
    cat("Available forecast columns:", paste(names(combined), collapse = ", "), "\n")
    stop(paste("Forecast variable", forecast_var_name, "not found in data"))
  }
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- combined %>%
    filter(Member %in% member_names)
  
  # Get observation data (take first value per lead time)
  obs_data <- plot_data %>%
    group_by(lead_time_hrs) %>%
    summarise(
      obs_value = first(.data[[obs_var_name]]),
      wow_value = first(.data[[wow_var_name]]),
      wow_n_stations = first(wow_n_stations),
      .groups = "drop"
    )
  
  # Create spaghetti plot
  p <- ggplot() +
    # Spaghetti lines for all ensemble members
    geom_line(data = plot_data,
              aes(x = lead_time_hrs, y = .data[[forecast_var_name]], group = Member),
              alpha = 0.3, 
              color = "gray50", 
              size = 0.4)
  
  # Add ensemble mean if requested
  if (show_mean) {
    p <- p +
      stat_summary(data = plot_data,
                   aes(x = lead_time_hrs, y = .data[[forecast_var_name]]),
                   fun = mean, 
                   geom = "line", 
                   color = "black", 
                   size = 1, 
                   alpha = 0.9)
  }
  
  # Add official observations (red)
  p <- p +
    geom_line(data = obs_data %>% filter(!is.na(obs_value)),
              aes(x = lead_time_hrs, y = obs_value),
              color = "blue", 
              size = 1.2) +
    geom_point(data = obs_data %>% filter(!is.na(obs_value)),
               aes(x = lead_time_hrs, y = obs_value),
               color = "darkblue", 
               size = 2, 
               alpha = 0.8)
  
  # Add WOW crowd-sourced observations (green)
  p <- p +
    geom_line(data = obs_data %>% filter(!is.na(wow_value)),
              aes(x = lead_time_hrs, y = wow_value),
              color = "red", 
              size = 1.2) +
    geom_point(data = obs_data %>% filter(!is.na(wow_value)),
               aes(x = lead_time_hrs, y = wow_value),
               color = "darkred", 
               size = 2, 
               alpha = 0.8)
  
  # Get station info
  station_info <- unique(plot_data$station_id)[1]
  gridpoint_lat <- round(unique(plot_data$gridpoint_lat)[1], 2)
  gridpoint_lon <- round(unique(plot_data$gridpoint_lon)[1], 2)
  
  # Labels and theme
  p <- p +
    labs(
      title = paste("Forecast Spaghetti Plot -", 
                    format(as.POSIXct(forecast_datetime), "%Y-%m-%d %H:%M UTC")),
      subtitle = paste("Gridpoint", gridpoint_id, "(", gridpoint_lat, "°N,", gridpoint_lon, "°E) |",
                      "Station:", station_info, "|",
                      length(members), "ensemble members"),
      x = "Lead Time (hours)",
      y = y_label,
      caption = paste("Gray: Ensemble members | Blue: Official obs | Red: WOW mean (", 
                     n_wow_stations, "nearest stations)",
                     if(show_mean) "| Black: Ensemble mean" else "")
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 11, color = "gray40"),
      plot.caption = element_text(size = 9, color = "gray50", hjust = 0),
      panel.grid.minor = element_blank()
    ) +
    scale_x_continuous(breaks = seq(0, 240, 24)) +
    coord_cartesian(xlim = c(0, 240))
  
  # Add day separation lines
  p <- p +
    geom_vline(xintercept = seq(24, 240, 24), alpha = 0.2, linetype = "dashed")
  
  return(p)
}

# Simplified multi-panel spaghetti plot function
plot_temp_humidity_spaghetti <- function(forecast_datetime, 
                                        gridpoint_id,
                                        members = 1:51,
                                        n_wow_stations = 5,
                                        show_mean = FALSE) {
  
  # Create temperature spaghetti plot
  p_temp <- plot_forecast_obs_wow_spaghetti(
    forecast_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id,
    variable = "Temperature_C",
    members = members,
    n_wow_stations = n_wow_stations,
    show_mean = show_mean
  )
  
  # Create humidity spaghetti plot  
  p_humidity <- plot_forecast_obs_wow_spaghetti(
    forecast_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id,
    variable = "Humidity_pct",
    members = members,
    n_wow_stations = n_wow_stations,
    show_mean = show_mean
  )
  
  # Combine plots
  if (requireNamespace("patchwork", quietly = TRUE)) {
    combined_plot <- p_temp / p_humidity
    return(combined_plot)
  } else {
    warning("Install 'patchwork' package to combine plots")
    return(list(temperature = p_temp, humidity = p_humidity))
  }
}

# Usage examples:

# Basic spaghetti plot for temperature
p_temp <- plot_forecast_obs_wow_spaghetti(
  forecast_datetime = "2021-01-28 12:00:00",
  gridpoint_id = 605,
  variable = "Temperature_C",
  members = 1:51,
  n_wow_stations = 5
)
print(p_temp)

# Spaghetti plot with ensemble mean
p_temp_mean <- plot_forecast_obs_wow_spaghetti(
  forecast_datetime = "2021-01-29 12:00:00",
  gridpoint_id = 605,
  variable = "Temperature_C",
  members = 1:51,
  n_wow_stations = 5,
  show_mean = TRUE
)
print(p_temp_mean)

# Humidity spaghetti plot
p_humidity <- plot_forecast_obs_wow_spaghetti(
  forecast_datetime = "2022-01-28 12:00:00",
  gridpoint_id = 605,
  variable = "Humidity_pct",
  members = 1:51,
  n_wow_stations = 5
)
print(p_humidity)

# Combined temperature and humidity spaghetti plots
p_combined <- plot_temp_humidity_spaghetti(
  forecast_datetime = "2023-09-28 12:00:00",
  gridpoint_id = 605,
  members = 1:51,
  n_wow_stations = 5,
  show_mean = TRUE
)
print(p_combined)
```

```{r}
plot_forecast_obs_wow_comparison <- function(forecast_datetime, 
                                              gridpoint_id, 
                                              variable = "Temperature_C", 
                                              members = 1:51,
                                              n_wow_stations = 5,
                                              show_error_band = TRUE,
                                              show_individual_members = FALSE,
                                              max_lead_time = 240) {
  
  var_mapping <- list(
    "Temperature_C" = list(
      forecast = "Temperature_C",
      obs = "T_DRYB_10",
      wow = "wow_temp_mean",
      wow_sd = "wow_temp_sd",
      label = "Temperature (°C)"
    ),
    "Humidity_pct" = list(
      forecast = "Relative_humidity_pct",  
      obs = "RH_10",
      wow = "wow_humidity_mean",
      wow_sd = NULL,
      label = "Relative Humidity (%)"
    )
  )
  
  if (!variable %in% names(var_mapping)) {
    stop(paste("Invalid variable:", variable, 
               ". Valid options are:", paste(names(var_mapping), collapse = ", ")))
  }
  
  var_info <- var_mapping[[variable]]
  forecast_var_name <- var_info$forecast
  obs_var_name <- var_info$obs
  wow_var_name <- var_info$wow
  wow_sd_name <- var_info$wow_sd
  y_label <- var_info$label
  
  cat("Fetching combined data...\n")
  combined <- combine_forecast_obs_wow(
    date_str = forecast_datetime, 
    gridpoint_id = gridpoint_id,
    n_wow_stations = n_wow_stations
  )
  
  if (is.null(combined) || nrow(combined) == 0) {
    warning(paste("No combined data found for", forecast_datetime, "at gridpoint", gridpoint_id))
    return(NULL)
  }
  
  if (!forecast_var_name %in% names(combined)) {
    cat("Available forecast columns:", paste(names(combined), collapse = ", "), "\n")
    stop(paste("Forecast variable", forecast_var_name, "not found in data"))
  }
  
  member_names <- paste0("M", members)
  plot_data <- combined %>% filter(Member %in% member_names)
  
  ensemble_stats <- plot_data %>%
    group_by(lead_time_hrs) %>%
    summarise(
      ensemble_mean = mean(.data[[forecast_var_name]], na.rm = TRUE),
      ensemble_median = median(.data[[forecast_var_name]], na.rm = TRUE),
      ensemble_q25 = quantile(.data[[forecast_var_name]], 0.25, na.rm = TRUE),
      ensemble_q75 = quantile(.data[[forecast_var_name]], 0.75, na.rm = TRUE),
      ensemble_q10 = quantile(.data[[forecast_var_name]], 0.1, na.rm = TRUE),
      ensemble_q90 = quantile(.data[[forecast_var_name]], 0.9, na.rm = TRUE),
      obs_value = first(.data[[obs_var_name]]),
      wow_value = first(.data[[wow_var_name]]),
      wow_n_stations = first(wow_n_stations),
      .groups = "drop"
    )
  
  if (!is.null(wow_sd_name) && wow_sd_name %in% names(plot_data)) {
    ensemble_stats <- ensemble_stats %>%
      left_join(
        plot_data %>%
          group_by(lead_time_hrs) %>%
          summarise(wow_sd = first(.data[[wow_sd_name]]), .groups = "drop"),
        by = "lead_time_hrs"
      )
  }
  
  p <- ggplot()
  
  if (show_error_band) {
    p <- p +
      geom_ribbon(data = ensemble_stats,
                  aes(x = lead_time_hrs, ymin = ensemble_q10, ymax = ensemble_q90),
                  fill = "lightblue", alpha = 0.2) +
      geom_ribbon(data = ensemble_stats,
                  aes(x = lead_time_hrs, ymin = ensemble_q25, ymax = ensemble_q75),
                  fill = "blue", alpha = 0.3)
    
    if (variable == "Temperature_C" && "wow_sd" %in% names(ensemble_stats)) {
      p <- p +
        geom_ribbon(data = ensemble_stats %>% 
                      filter(!is.na(wow_value) & !is.na(wow_sd)),
                    aes(x = lead_time_hrs, 
                        ymin = wow_value - wow_sd, 
                        ymax = wow_value + wow_sd),
                    fill = "darkgreen", alpha = 0.2)
    }
  }
  
  if (show_individual_members && length(members) <= 20) {
    p <- p +
      geom_line(data = plot_data,
                aes(x = lead_time_hrs, y = .data[[forecast_var_name]], group = Member),
                alpha = 0.2, color = "gray50", size = 0.3)
  }
  
  p <- p +
    geom_line(data = ensemble_stats,
              aes(x = lead_time_hrs, y = ensemble_mean),
              color = "blue", size = 0.8) +
    geom_line(data = ensemble_stats %>% filter(!is.na(obs_value)),
              aes(x = lead_time_hrs, y = obs_value),
              color = "red", size = 0.8) +
    geom_point(data = ensemble_stats %>% filter(!is.na(obs_value)),
               aes(x = lead_time_hrs, y = obs_value),
               color = "darkred", size = 1.5, alpha = 0.8) +
    geom_line(data = ensemble_stats %>% filter(!is.na(wow_value)),
              aes(x = lead_time_hrs, y = wow_value),
              color = "darkgreen", size = 0.8, linetype = "solid") +
    geom_point(data = ensemble_stats %>% filter(!is.na(wow_value)),
               aes(x = lead_time_hrs, y = wow_value, size = wow_n_stations),
               color = "darkgreen", size = 1.5, alpha = 0.8) +
    scale_size_continuous(range = c(1, 4), name = "WOW Stations", guide = "none")
  
  station_info <- unique(plot_data$station_id)[1]
  gridpoint_lat <- round(unique(plot_data$gridpoint_lat)[1], 2)
  gridpoint_lon <- round(unique(plot_data$gridpoint_lon)[1], 2)
  
  p <- p +
    labs(
      title = paste("Forecast vs Observations: Official & Crowd-sourced -", 
                    format(as.POSIXct(forecast_datetime), "%Y-%m-%d %H:%M UTC")),
      subtitle = paste("Gridpoint", gridpoint_id, "(", gridpoint_lat, "°N,", gridpoint_lon, "°E) |",
                       "Station:", station_info, "|",
                       length(members), "ensemble members"),
      x = "Lead Time (hours)",
      y = y_label,
      caption = paste("Blue: Ensemble mean | Red: Official obs | Green: WOW mean (", 
                      n_wow_stations, "nearest stations)")
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 11, color = "gray40"),
      plot.caption = element_text(size = 9, color = "gray50", hjust = 0),
      panel.grid.minor = element_blank()
    ) +
    scale_x_continuous(breaks = seq(0, max_lead_time, 24)) +
    coord_cartesian(xlim = c(0, max_lead_time)) +
    geom_vline(xintercept = seq(24, max_lead_time, 24), alpha = 0.2, linetype = "dashed")
  
  return(p)
}

p_temp_72 <- plot_forecast_obs_wow_comparison(
  forecast_datetime = "2021-01-28 12:00:00",
  gridpoint_id = 605,
  variable = "Temperature_C",
  members = 1:51,
  n_wow_stations = 5,
  show_error_band = TRUE,
  max_lead_time = 72#only accept input from 0,6,12...72
)
print(p_temp_72)
```


