---
title: "API test"
author: "Wenkai Zhong"
date: "2025-07-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#change R language to english
Sys.setlocale("LC_TIME", "English")
rm(list = ls())

library(R.utils)
library(ggplot2)
library(patchwork)
library(lubridate)
library(here)
library(ncdf4)
library(ggrepel)
library(tidyverse)
library(plotly)
#library(sf)
#library(rnaturalearth)

# creat .gitignore file to avoid upload data(too large)
cat("# Ignore all data files
data/
*.RData
*.Rhistory
.Rproj.user/
.RDataTmp*
", file = ".gitignore")
```

## Reading in the netcdf

# Model: These are the files starting with "combined_raw_". It contains ECMWF-IFS ensemble forecasts (50+1 members) over the Netherlands at 6-h time resolution.
#check combined_raw_2d/2t_year data
#2d = dew point temperature
#2t = 2-meter temperature
#NetCDF data type

#Here is basiclly what this nc data set looks like
combined_raw_2t_2021.nc (Temperature data)
combined_raw_2d_2021.nc (Dewpoint data)

Data Structure (4D array):
[location, lead_time, ensemble_member, forecasts number(two forecasts daily)]
[38,       41,        51,              730]

Visual Representation:
┌─────────────────────────────────────────────┐
│              Year 2021 Data                 │
├─────────────────────────────────────────────┤
│  Forecast Axis (730 forecasts)                        │
│  ↓                                          │
│  forecasts 1 
         ┌─────────────────────────┐         │
│        │ Loc1  Loc2 ... Loc38   │ ← 38 locations
│        ├─────────────────────────┤         │
│        │ 0h  ┌─────────────┐    │         │
│        │ 6h  │ M1 M2...M51 │    │ ← 51 ensemble members
│        │ 12h │ Temp values │    │         │
│        │ ... │   matrix    │    │         │
│        │240h └─────────────┘    │ ← 41 lead times
│        └─────────────────────────┘         │
│                                            │
│  forecasts 2 
         ┌─────────────────────────┐         │
│        │ (same structure)        │         │
│        └─────────────────────────┘         │
│  ...                                        │
│                                             │
│  forecasts 730 
           ┌───────────────────────┐         │
│          │ (same structure)      │         │
│          └───────────────────────┘         │
└─────────────────────────────────────────────┘

Example indexing:
all_data[["2021"]]$T2[1, 1, 1, 1] = Location 1, Hour 0, Member 1, Forecast 1
all_data[["2021"]]$T2[38, 41, 51, 730] = Location 38, Hour 240, Member 51, Forecast 730

Dimension meanings:
- gridpoint: [605, 639, 674, ...] (38 station IDs)
- step: [0, 6, 12, ..., 240] (41 forecast hours)
- member: 1-50 are ensemble members, 51 is control forecast
- validTime: [timestamp1, timestamp2, ..., timestamp730] (730 forecast times)

##after test and some preliminary research,we start to import whole dataset
##functions that help us to extract data from nc files
```{r}
rm(list = ls())
#use example: temp_2021 <- read_data(2021, "2t")
read_data <- function(year, var_type, data_dir = here("data", "ToSend-01-20-2025")) {
  # Build filename
  filename <- file.path(data_dir, paste0("combined_raw_", var_type, "_", year, ".nc"))
  
  # Open file
  nc <- nc_open(filename)
  
  # Read main variable
  var_name <- paste0("x", var_type)  # x2t or x2d
  data <- ncvar_get(nc, var_name)
  
  # Read other information
  step <- ncvar_get(nc, "step")
  validTime <- ncvar_get(nc, "validTime")
  gridpoint <- ncvar_get(nc, "gridpoint")
  member <- if("member" %in% names(nc$dim)) ncvar_get(nc, "member") else NULL
  
  runtime_info <- nc$dim$runtime
  
  # Close file
  nc_close(nc)
  
  # Return
  return(list(
    data = data,
    step = step,
    validTime = validTime,
    gridpoint = gridpoint,
    member = member,
    runtime_units = runtime_info$units,
    runtime_vals = runtime_info$vals
  ))
}

# Test
# temp_2021 <- read_data(2021, "2t")  # Read combined_raw_2t_2021.nc
# dewp_2021 <- read_data(2021, "2d")  # Read combined_raw_2d_2021.nc
# temp_2021_start_time <- temp_2021$runtime_units
# temp_2021_start_time
# dewp_2021_start_time <- dewp_2021$runtime_units
# dewp_2021_start_time
```

###function that help us to convert readed data to tidy format
```{r}
#example：example_day <- tidy_formation(temp_2021, gridpoint_idx = 1, validtime_idx = 100)
tidy_formation <- function(data, gridpoint_idx, validtime_idx) {
  # Parse reference date from runtime_units (e.g., "days since 2021-01-31 00:00:00")
  ref_date <- as.Date(gsub(".*since\\s+([0-9-]+).*", "\\1", data$runtime_units))
  
  # validtime_idx is the same as day_i in your original code
  # It directly indexes into runtime_vals
  forecast_date <- ref_date + days(data$runtime_vals[validtime_idx])
  
  # Get the data slice [gridpoint, step, member, validtime]
  # This is equivalent to T2[loc_i, 1:41, 1:51, day_i] in your original code
  data_slice <- data$data[gridpoint_idx, , , validtime_idx]
  
  # Transpose to get members as rows, steps as columns
  df <- as.data.frame(t(data_slice))
  
  # Name columns by step index
  names(df) <- paste0("Step_", 0:40)
  
  # Add member column
  df$Member <- paste0("M", seq_len(nrow(df)))
  
  # Create lead time hours vector (0 to 240 hours in 41 steps)
  lead_times_hours <- seq(0, 240, length.out = 41)
  
  # Pivot to long format and add all necessary columns
  tidy_df <- df %>%
    pivot_longer(
      cols = starts_with("Step_"),
      names_to = "Step_idx",
      values_to = "Forecast_value"
    ) %>%
    mutate(
      Step_idx = as.numeric(gsub("Step_", "", Step_idx)),
      lead_time_hrs = lead_times_hours[Step_idx + 1],  # +1 because R is 1-indexed
      Gridpoint_idx = gridpoint_idx,
      ValidTime_idx = validtime_idx,
      Gridpoint = data$gridpoint[gridpoint_idx],
      Forecast_date = forecast_date  # This is the date from date_lookup_df
    ) %>%
    select(Member, lead_time_hrs, Forecast_date, Forecast_value, 
           Gridpoint, everything())
  
  return(tidy_df)
}


# Example usage and verification
#temp_2021 <- read_data(2021, "2t")
#temp_2021
# 
# # Convert specific validtime to tidy format
# example_day <- tidy_formation(temp_2021, gridpoint_idx = 1, validtime_idx = 100)
# example_day
# 
# dewp_example_day <- tidy_formation(dewp_2021, gridpoint_idx = 1, validtime_idx = 100)
# dewp_example_day
```

##function that we only input forecats_time and gridpoint to generate tidy forecast table
```{r}
#example: tidy_result_2021_01_31_G605 <- tidy_table_ultimate("2021-01-31", 605)
# Helper function to find validtime index for a given date

# helper functions
find_validtime_index <- function(data, target_date) {
  target_date <- as.Date(target_date)
  ref_date <- as.Date(gsub(".*since\\s+([0-9-]+).*", "\\1", data$runtime_units))
  days_since_ref <- as.numeric(target_date - ref_date)
  
  # Find exact match or closest
  idx <- which(data$runtime_vals == days_since_ref)
  if (length(idx) == 0) {
    idx <- which.min(abs(data$runtime_vals - days_since_ref))
  }
  return(idx)
}

find_gridpoint_index <- function(data, gridpoint_id) {
  idx <- which(data$gridpoint == gridpoint_id)
  if (length(idx) == 0) {
    stop("Gridpoint ID ", gridpoint_id, " not found")
  }
  return(idx)
}


# main function!!!!!!!!!!!!!
#example: tidy_result_2021_08_13_G605 <- tidy_table_ultimate("2021-08-13", 605)
tidy_table_ultimate <- function(target_date, gridpoint_id, data_dir = here("data", "ToSend-01-20-2025")) {
  
  # Step 1: Extract year
  year <- year(as.Date(target_date))
  
  # Step 2: Read both datasets
  temp_data <- read_data(year, "2t", data_dir)
  dewp_data <- read_data(year, "2d", data_dir)
  
  # Step 3: Find validtime index for EACH dataset separately
  vt_idx_temp <- find_validtime_index(temp_data, target_date)
  vt_idx_dewp <- find_validtime_index(dewp_data, target_date)
  
  # Step 4: Find gridpoint index
  grid_idx <- find_gridpoint_index(temp_data, gridpoint_id)
  
  # Step 5: Calculate forecast dates for EACH dataset
  ref_date_temp <- as.Date(gsub(".*since\\s+([0-9-]+).*", "\\1", temp_data$runtime_units))
  ref_date_dewp <- as.Date(gsub(".*since\\s+([0-9-]+).*", "\\1", dewp_data$runtime_units))
  
  # Ensure we get single values
  forecast_date_temp <- ref_date_temp + days(temp_data$runtime_vals[vt_idx_temp[1]])
  forecast_date_dewp <- ref_date_dewp + days(dewp_data$runtime_vals[vt_idx_dewp[1]])
  
  # Verify dates match (use all() for safe comparison)
  if (!identical(forecast_date_temp, forecast_date_dewp)) {
    warning("Temperature and dew point data have different forecast dates: ",
            as.character(forecast_date_temp), " vs ", as.character(forecast_date_dewp))
  }
  
  # Create lead times
  lead_times_hours <- seq(0, 240, length.out = 41)
  
  # Initialize results
  results <- list()
  
  # Extract data manually for each member and step
  for (m in 1:51) {
    for (s in 1:41) {
      # Extract temperature value - use first index if multiple
      temp_val <- tryCatch({
        temp_data$data[grid_idx[1], s, m, vt_idx_temp[1]]
      }, error = function(e) {
        tryCatch({
          temp_data$data[m, s, vt_idx_temp[1], grid_idx[1]]
        }, error = function(e) {
          NA
        })
      })
      
      # Extract dew point value - use first index if multiple
      dewp_val <- tryCatch({
        dewp_data$data[grid_idx[1], s, m, vt_idx_dewp[1]]
      }, error = function(e) {
        tryCatch({
          dewp_data$data[m, s, vt_idx_dewp[1], grid_idx[1]]
        }, error = function(e) {
          NA
        })
      })
      
      # Ensure we have single values
      if (length(temp_val) > 1) temp_val <- temp_val[1]
      if (length(dewp_val) > 1) dewp_val <- dewp_val[1]
      
      # Add to results
      results[[length(results) + 1]] <- data.frame(
        Member = paste0("M", m),
        lead_time_hrs = lead_times_hours[s],
        Forecast_date = forecast_date_temp,
        Temperature = as.numeric(temp_val),
        DewPoint = as.numeric(dewp_val),
        Temperature_C = as.numeric(temp_val) - 273.15,
        DewPoint_C = as.numeric(dewp_val) - 273.15,
        Gridpoint_ID = gridpoint_id,
        stringsAsFactors = FALSE
      )
    }
  }
  
  # Combine all results
  tidy_combined <- bind_rows(results)
  return(tidy_combined)
}

#test
tidy_result_2021_08_13_G605 <- tidy_table_ultimate("2021-08-13", 605)
tidy_result_2021_08_13_G605
```

##import meta data to find locations(lon and lat) for gridpoints and their corresponding stations
```{r}
#import meta data
prediction_metadata <- read.csv(here("data", "ToSend-01-20-2025", "prediction_meta.csv"))
sta_gp_metadata <- read.csv(here("data", "ToSend-01-20-2025", "sta_gp_metadata.csv"))
sta_gp_metadata <- sta_gp_metadata %>%
  select(-X)

# all grid points appeared in our all_data data set
unique_gridpoints <- c(605, 639, 674, 676, 680, 715, 745, 747, 787, 818, 819, 821, 854, 857, 891, 896, 935, 965, 967, 969, 971, 1001, 1002, 1003, 1041, 1073, 1074, 1080, 1111, 1112, 1114, 1118, 1147, 1148, 1154, 1187, 1193, 1269)

#match them with meta

gridpoint_lookup <- data.frame(
  data_index = 1:length(unique_gridpoints),
  gridpoint = unique_gridpoints
)

# merge
gridpoint_lookup <- merge(gridpoint_lookup, prediction_metadata,
                         by = "gridpoint",
                         all.x = TRUE)%>%select(-data_index)
gridpoint_lookup <- gridpoint_lookup %>%
  left_join(sta_gp_metadata, by = c("gridpoint" = "gp"))%>%
  select(-sta_id,
         gp_lat = gp_lat.x, 
         gp_lon = gp_lon.x, 
         everything(),
         -gp_lat.y, 
         -gp_lon.y)

# one-to-many relationship when joining two datasets where one gridpoint maps to multiple stations, causing duplicate rows in the merged data 
gridpoint_station_table = gridpoint_lookup %>% 
  mutate(
    # determine primary or secondary
    station_type = ifelse(station_id == sta_id, "primary", "secondary")
  )%>%
  mutate(
    is_coast = ifelse(station_type == "secondary", NA, is_coast),
    clc_dist0 = ifelse(station_type == "secondary", NA, clc_dist0),
    dist = ifelse(station_type == "secondary", NA, dist)
  )%>%
  select(-station_id)

gridpoint_station_table

## Verify guess
## There are 38 grid point locations in the data but 46 stations so Kiri guessed that there may be more than one station per grid point - this is worth checking. We will need to follow up about the mapping from grid points to stations. 

station_count <- gridpoint_station_table %>%
  group_by(gridpoint) %>%
  summarise(
    n_stations = sum(!is.na(sta_id)),  
  ) %>%
  arrange(desc(n_stations))  

station_count
length(station_count$gridpoint)
sum(station_count$n_stations)

# only found 43 stations in 38 grid points

# In addition, for some gridpoints like 819 , it has 2 relate stations with different station_id, sta_lat and sta_lon
```
################### (: Visualization starts here :) ######################


## find stations near cities
```{r}
# lon and lat for different cities
cities <- data.frame(
  city = c("Amsterdam", "Rotterdam", "Utrecht", "The Hague", "Eindhoven", 
           "Groningen", "Tilburg", "Almere", "Breda", "Nijmegen",
           "Haarlem", "Arnhem", "Zaanstad", "Apeldoorn", "Enschede",
           "Amersfoort", "Zwolle", "Dordrecht", "Leiden", "Maastricht",
           "Delft", "Alkmaar", "Leeuwarden", "Middelburg", "Den Helder"),
  city_lat = c(52.37, 51.92, 52.09, 52.08, 51.44,
               53.22, 51.56, 52.37, 51.59, 51.84,
               52.38, 51.98, 52.44, 52.21, 52.22,
               52.16, 52.51, 51.81, 52.16, 50.85,
               52.01, 52.63, 53.20, 51.50, 52.96),
  city_lon = c(4.90, 4.48, 5.12, 4.30, 5.48,
               6.57, 5.08, 5.22, 4.78, 5.87,
               4.64, 5.90, 4.83, 5.97, 6.90,
               5.39, 6.09, 4.67, 4.49, 5.69,
               4.36, 4.75, 5.80, 3.61, 4.76),
  population_rank = c(1, 2, 4, 3, 5,    # population rank
                      6, 7, 8, 9, 10,
                      11, 12, 13, 14, 15,
                      16, 17, 18, 19, 20,
                      21, 22, 23, 24, 25),
  region = c("North Holland", "South Holland", "Utrecht", "South Holland", "North Brabant",
             "Groningen", "North Brabant", "Flevoland", "North Brabant", "Gelderland",
             "North Holland", "Gelderland", "North Holland", "Gelderland", "Overijssel",
             "Utrecht", "Overijssel", "South Holland", "South Holland", "Limburg",
             "South Holland", "North Holland", "Friesland", "Zeeland", "North Holland")
)

# Find nearest station for each city
city_connections <- cities %>%
 rowwise() %>%
 mutate(
   # Calculate distances to all stations
   distances = list(sqrt((gridpoint_station_table$sta_lat - city_lat)^2 + 
                        (gridpoint_station_table$sta_lon - city_lon)^2) * 111),
   nearest_idx = which.min(distances),
   station_lat = gridpoint_station_table$sta_lat[nearest_idx],
   station_lon = gridpoint_station_table$sta_lon[nearest_idx],
   distance_km = round(min(distances), 1)
 )

# Create simple connection map
city_station_plot = ggplot() +
  # Connection lines
  geom_segment(data = city_connections,
               aes(x = city_lon, y = city_lat, xend = station_lon, yend = station_lat),
               alpha = 0.3) +
  
  # Primary Stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "primary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "red", size = 2) +
  
  # Secondary Stations (yellow.samll size)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "gold", size = 1) +
 
 # Cities
 geom_point(data = cities,
            aes(x = city_lon, y = city_lat, size = 1/population_rank), color = "blue" ) +
 
 # Labels for major cities only
 geom_text_repel(data = cities ,
                 aes(x = city_lon, y = city_lat, label = city),
                 size = 3) +
  
 geom_text_repel(data = gridpoint_station_table ,
                 aes(x = sta_lon, y = sta_lat, label = sta_id),
                 size = 2) +
  
 labs(title = "Cities and Nearest Weather Stations",
     subtitle = "City points size is determinted by its population rank",
     x = "Longitude", y = "Latitude")+
 theme_minimal() +
 coord_fixed(1.3)+
 scale_size_continuous(guide = FALSE)

city_station_plot

ggsave(
  filename = "Cities and Nearest Weather Stations.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

```

## find stations near grid points,for some gridpoints like 819 , it has 2 relate stations but same station_id different sta_lat and sta_lon
```{r}
# Create visualization
#netherlands <- ne_countries(country = "netherlands", returnclass = "sf", scale = "medium")

gridpoint_station_map <- ggplot() +
  #geom_sf(data = netherlands, fill = NA, color = "black", size = 0.8) +
  # Connection lines
  geom_segment(data = gridpoint_station_table,
               aes(x = gp_lon, y = gp_lat, xend = sta_lon, yend = sta_lat),
               alpha = 0.3) +
  # Plot gridpoint points (using squares)
  geom_point(data = gridpoint_station_table,
             aes(x = gp_lon, y = gp_lat, shape = "Gridpoints"),
             color = "darkblue") +
  
  # Plot primary stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "primary"),
             aes(x = sta_lon, y = sta_lat, shape = "Primary Stations"),
             color = "red") +
  
  # Plot secondary stations (yellow)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat, shape = "Secondary Stations"),
             color = "gold") +
  
  # Set shapes
  scale_shape_manual(values = c("Gridpoints" = 15, 
                               "Primary Stations" = 16,
                               "Secondary Stations" = 17),
                     name = "Type") +
  
  # Add gridpoint labels
  geom_text_repel(data = gridpoint_station_table,
                  aes(x = gp_lon, y = gp_lat, label = gridpoint),
                  size = 2.5,
                  color = "darkblue",
                  box.padding = 0.3,
                  point.padding = 0.2,
                  max.overlaps = 20) +
  
  # Add primary station labels (red)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "primary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "red",
                  nudge_y = 0.02,
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  # Add secondary station labels (yellow)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "secondary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "gold",
                  nudge_y = -0.02,  #avoid overlapping
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  labs(title = "ECMWF Gridpoints and KNMI Stations in the Netherlands",
       subtitle = "Primary stations (red) vs Secondary stations (yellow)",
       x = "Longitude",
       y = "Latitude") +
  
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

gridpoint_station_map

ggsave(
  filename = "ECMWF Gridpoints and KNMI Stations in the Netherlands.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

# every station is super close to its corresponding grid points
```
```{r}
#automate plot function using gridpoint_id date and members to plot
auto_forecast_plot <- function(date, grid_point, members = 1:51, 
                              variable = "Temperature_C",
                              data_dir = here("data", "ToSend-01-20-2025")) {
  
  # Get the tidy data
  tidy_data <- tidy_table_ultimate(date, grid_point, data_dir)
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names)
  
  # Create base plot
  p <- ggplot(plot_data, aes(x = lead_time_hrs, y = .data[[variable]], group = Member))
  
  # Check number of members
  n_members <- length(members)
  
  if (n_members <= 10) {
    # Use different colors for each member
    colors <- c("red", "blue", "green", "purple", "orange", 
                "brown", "pink", "yellow", "cyan", "magenta")
    
    p <- p + geom_line(aes(color = Member), size = 1.2, alpha = 0.8) +
         scale_color_manual(values = colors[1:n_members])
  } else {
    # Use gray for all lines when more than 10 members
    p <- p + geom_line(alpha = 0.6, color = "gray")
  }
  
  # Add labels and theme
  p <- p +
    labs(
      title = paste("Forecast for", date, "at Gridpoint", grid_point),
      subtitle = paste(n_members, "ensemble members"),
      x = "Lead Time (hours)",
      y = ifelse(variable == "Temperature_C", "Temperature (°C)", 
                 ifelse(variable == "DewPoint_C", "Dew Point (°C)", variable))
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      legend.position = if(n_members <= 10) "right" else "none"
    ) +
    scale_x_continuous(breaks = seq(0, 240, 24)) +
    coord_cartesian(xlim = c(0, 240))
  
  return(p)
}

p1 <- auto_forecast_plot("2021-01-31", 605, members = 1:51)
print(p1)
```
```{r}
auto_forecast_plot_with_pdf <- function(date, grid_point, members = 1:51, 
                                       variable = "Temperature_C",
                                       pdf_times = c(24, 48, 120, 240),  # Hours to show PDFs
                                       data_dir = here("data", "ToSend-01-20-2025")) {
  
  # Get the tidy data
  tidy_data <- tidy_table_ultimate(date, grid_point, data_dir)
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names)
  
  # Check number of members
  n_members <- length(members)
  
  # Main forecast plot
  p_main <- ggplot(plot_data, aes(x = lead_time_hrs, y = .data[[variable]], group = Member))
  
  if (n_members <= 10) {
    colors <- c("red", "blue", "green", "purple", "orange", 
                "brown", "pink", "yellow", "cyan", "magenta")
    p_main <- p_main + 
      geom_line(aes(color = Member), size = 1.2, alpha = 0.8) +
      scale_color_manual(values = colors[1:n_members])
  } else {
    p_main <- p_main + 
      geom_line(alpha = 0.6, color = "gray")
  }
  
  # Add vertical lines at PDF times
  p_main <- p_main +
    geom_vline(xintercept = pdf_times, linetype = "dashed", alpha = 0.5) +
    labs(
      title = paste("Forecast for", date, "at Gridpoint", grid_point),
      subtitle = paste(n_members, "ensemble members"),
      x = "Lead Time (hours)",
      y = ifelse(variable == "Temperature_C", "Temperature (°C)", 
                 ifelse(variable == "DewPoint_C", "Dew Point (°C)", variable))
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      legend.position = if(n_members <= 10) "bottom" else "none"
    ) +
    scale_x_continuous(breaks = seq(0, 240, 24)) +
    coord_cartesian(xlim = c(0, 240))
  
  # Create PDF plots
  pdf_plots <- list()
  
  for (i in seq_along(pdf_times)) {
    time_hr <- pdf_times[i]
    
    # Get data for this specific time
    pdf_data <- plot_data %>%
      filter(abs(lead_time_hrs - time_hr) < 0.1)  # Account for floating point
    
    if (nrow(pdf_data) > 0) {
      # Create density plot
      p_pdf <- ggplot(pdf_data, aes(x = .data[[variable]])) +
        geom_density(fill = "lightblue", alpha = 0.7, color = "darkblue") +
        geom_rug(alpha = 0.5) +
        labs(
          title = paste0(time_hr, "h"),
          x = "",
          y = "Density"
        ) +
        theme_minimal() +
        theme(
          plot.title = element_text(size = 10, hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          panel.grid.major.y = element_blank(),
          panel.grid.minor.y = element_blank()
        ) +
        coord_flip()  # Rotate to vertical
      
      # Add mean line
      mean_val <- mean(pdf_data[[variable]], na.rm = TRUE)
      p_pdf <- p_pdf + 
        geom_vline(xintercept = mean_val, color = "red", linetype = "dashed")
      
      pdf_plots[[i]] <- p_pdf
    }
  }
  
  # Combine plots using patchwork
  if (length(pdf_plots) > 0) {
    # Combine PDF plots vertically
    pdf_combined <- wrap_plots(pdf_plots, ncol = 1)
    
    # Combine main plot with PDFs
    final_plot <- p_main + pdf_combined + 
      plot_layout(widths = c(3, 1))
  } else {
    final_plot <- p_main
  }
  
  return(final_plot)
}

p1 <- auto_forecast_plot_with_pdf("2021-01-31", 605, members = 1:51)
print(p1)
```



#Write code so we can visualise a forecast on a given day (think spaghetti type plot)
```{r}
library(ncdf4)
library(dplyr)
library(tidyr)
library(ggplot2)
```

#These are the files starting with "kis". It contains 10-min observations at stations between 2021 and 2024 following the link I sent you. You would have to subset it to match the time resolution of the forecasts, and combine the different years and months together.
#Source: https://dataplatform.knmi.nl/dataset/vochtigheid-en-temperatuur-1-0
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(lubridate)


readLines("data/ToSend-01-20-2025/kis_tot_202106.gz", n = 25)

kis_tot_202106 <- read_table("data/ToSend-01-20-2025/kis_tot_202106.gz", skip = 21)

head(kis_tot_202106)
tail(kis_tot_202106)

summary(kis_tot_202106)
#U_SEA_10 and x19 all NA
#some vaiables like U_10,TX_DRYB_10 miss too many records
#T_WETB_10, TX_DRYB_10, U_10 show maximums of 100, 99, or even 114.3—values outside any physical range
```






