---
title: "API test"
author: "Kevin"
date: "2025-03-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#change R language to english
Sys.setlocale("LC_TIME", "English")
rm(list = ls())

library(R.utils)
library(ggplot2)
library(patchwork)
library(lubridate)
library(here)
library(ncdf4)
library(ggrepel)
library(tidyverse)
library(plotly)
#library(sf)
#library(rnaturalearth)

# creat .gitignore file to avoid upload data(too large)
cat("# Ignore all data files
data/
*.RData
*.Rhistory
.Rproj.user/
.RDataTmp*
", file = ".gitignore")
```

## Reading in the netcdf

# Model: These are the files starting with "combined_raw_". It contains ECMWF-IFS ensemble forecasts (50+1 members) over the Netherlands at 6-h time resolution.
#check combined_raw_2d/2t_year data
#2d = dew point temperature
#2t = 2-meter temperature
#NetCDF data type

## There is an issue with how the dates are read in from the netcdf files. The order is mixed up, must look at the validtime to resolve this known issue. 

## Some varification and test for our dataset (ensemble forecasts)

```{r}
#read netcdf file
t2m_nc <- nc_open("data/ToSend-01-20-2025/combined_raw_2t_2021.nc") # temp data
td2m_nc <- nc_open("data/ToSend-01-20-2025/combined_raw_2d_2021.nc") #dew point data

#list all variables in this data set
names(t2m_nc$var) 
names(td2m_nc$var)

#get data
T2 <- ncvar_get(t2m_nc, "x2t")  # temp in Kelvin
Td <- ncvar_get(td2m_nc, "x2d") # dew point temperature

step <- ncvar_get(t2m_nc, "step") #Lead times
validTime_raw <- ncvar_get(t2m_nc, "validTime") ## ?? no idea what are those number means for date
#might be minute offsets from a reference time but dont know reference time

#close netcdfs
nc_close(t2m_nc)
nc_close(td2m_nc)

summary(T2)
summary(Td)

# dim(T2) # result: 38 41 51 730
# #str(t2m_nc)
# 
# validTime_raw
# 
# dim(t2m_nc)
# dim(T2)
# t2m_nc[[1]]
# 
# T2[1,1:41,1,1]
# 
# # From our meeting with Kiri
# names(t2m_nc$dim)
# t2m_nc$dim$runtime
# table(t2m_nc$dim$runtime$vals)
# t2m_nc$dim$step
# 
# # Making sense of meeting with Kir
str_data_reference_date = t2m_nc$dim$runtime$units
data_reference_date = as_date("2021-01-31")
# #TODO: automate this somehow
date_refs = data_reference_date + t2m_nc$dim$runtime$vals
# 
date_lookup_df = data.frame(day_i = 1:length(date_refs), date = date_refs)


# # dimension 1 is the grid cell locations (these may match more than one station) (Match these using the documentation - still need to figure this out)
# # dimension 2 is the number of lead times over the 10 days (6 hours) (In the documentation)
# # dimension 3 is the number of ensemble members (50) plus 1 high resolution run
# # dimension 4 is the number of forcasts 365 * 2 (2 forecasts per day)

#Here is basiclly what this nc data set looks like

```
#Here is basiclly what this nc data set looks like
combined_raw_2t_2021.nc (Temperature data)
combined_raw_2d_2021.nc (Dewpoint data)

Data Structure (4D array):
[location, lead_time, ensemble_member, forecasts number(two forecasts daily)]
[38,       41,        51,              730]

Visual Representation:
┌─────────────────────────────────────────────┐
│              Year 2021 Data                 │
├─────────────────────────────────────────────┤
│  Forecast Axis (730 forecasts)                        │
│  ↓                                          │
│  forecasts 1 
         ┌─────────────────────────┐         │
│        │ Loc1  Loc2 ... Loc38   │ ← 38 locations
│        ├─────────────────────────┤         │
│        │ 0h  ┌─────────────┐    │         │
│        │ 6h  │ M1 M2...M51 │    │ ← 51 ensemble members
│        │ 12h │ Temp values │    │         │
│        │ ... │   matrix    │    │         │
│        │240h └─────────────┘    │ ← 41 lead times
│        └─────────────────────────┘         │
│                                             │
│  forecasts 2 
         ┌─────────────────────────┐         │
│        │ (same structure)        │         │
│        └─────────────────────────┘         │
│  ...                                        │
│                                             │
│  forecasts 730 
           ┌───────────────────────┐         │
│          │ (same structure)      │         │
│          └───────────────────────┘         │
└─────────────────────────────────────────────┘

Example indexing:
all_data[["2021"]]$T2[1, 1, 1, 1] = Location 1, Hour 0, Member 1, Forecast 1
all_data[["2021"]]$T2[38, 41, 51, 730] = Location 38, Hour 240, Member 51, Forecast 730

Dimension meanings:
- gridpoint: [605, 639, 674, ...] (38 station IDs)
- step: [0, 6, 12, ..., 240] (41 forecast hours)
- member: 1-50 are ensemble members, 51 is control forecast
- validTime: [timestamp1, timestamp2, ..., timestamp730] (730 forecast times)


## Start visualization(test example created by Kate)
```{r}
lead_times_hours = seq(0, 240, length.out = 41)#

ggplot() + 
  geom_line(aes(x = lead_times_hours, T2[1,1:41,1,1])) + 
  geom_line(aes(x = lead_times_hours, T2[1,1:41,2,1]), col = "blue") +
  geom_line(aes(x = lead_times_hours, T2[1,1:41,3,1]), col = "red") 

raw_forecast_data = T2; loc_i = 1; day_i = 1
tidy_forecast <- function(raw_forecast_data, day_i, loc_i){
  daily_forecast = raw_forecast_data[loc_i, 1:41, 1:51, day_i] |>
    as.data.frame()
  names(daily_forecast) = paste0("M", 1:ncol(daily_forecast))
  daily_forecast = daily_forecast |>
    mutate(lead_time_hrs = seq(0, 240, length.out = 41)) |>
    pivot_longer(cols = 1:50, names_to = "Member", values_to = "Forecast_value")
  #TODO: fix this so columns aren't hard coded
  return(daily_forecast)
}

example_day = tidy_forecast(T2, 1, 1)
example_day

ggplot(example_day) + 
  geom_line(aes(x = lead_time_hrs, y = Forecast_value, group = Member), alpha = 0.6, col = "gray")


#TODO: automate this somehow
date_refs = data_reference_date + t2m_nc$dim$runtime$vals 

date_lookup_df = data.frame(day_i = 1:length(date_refs), date = date_refs)

```

##after test and some preliminary research,we start to import whole dataset
##Read all nc data after understand the data structure
```{r}
rm(list = ls())
############ import ensemble forecast data

#TODO: fix direct path references (complete,delete after check)
#TODO: put your files on github (complete,delete after check)

data_dir <- here("data", "ToSend-01-20-2025") # set file direction
nc_files <- list.files(data_dir, pattern = "\\.nc$", full.names = TRUE) # find all nc file

#divide them to temp and dewpoint data based on name
temp_files <- nc_files[grep("_2t_", nc_files)]
dewpoint_files <- nc_files[grep("_2d_", nc_files)]

#function to read netcdf file based on different year
read_year_data <- function(year, data_dir) {
  t2m_file <- file.path(data_dir, paste0("combined_raw_2t_", year, ".nc"))
  td2m_file <- file.path(data_dir, paste0("combined_raw_2d_", year, ".nc"))
  #open nc file
  t2m_nc <- nc_open(t2m_file)
  td2m_nc <- nc_open(td2m_file)
  #read data by different variable
  T2 <- ncvar_get(t2m_nc, "x2t") # get temp data
  Td <- ncvar_get(td2m_nc, "x2d") # get dew point data
  step <- ncvar_get(t2m_nc, "step")# Lead time# How long it predict?
  validTime <- ncvar_get(t2m_nc, "validTime")# target time of forecast
  gridpoint <- ncvar_get(t2m_nc, "gridpoint") # gridpoint of location
  #close nc file
  nc_close(t2m_nc)
  nc_close(td2m_nc)
  #return read data in list format 
  return(list(
    year = year,
    T2 = T2,
    Td = Td,
    step = step,
    validTime = validTime,
    gridpoint = gridpoint
  ))
}

#function to extract nc file year  
extract_years <- function(files) {
  years <- unique(gsub(".*_(\\d{4})\\.nc", "\\1", basename(files)))
  return(as.numeric(years))
}

#find all available year
available_years <- extract_years(c(temp_files, dewpoint_files))
available_years <- sort(unique(available_years))

#use for loop to import all data to list all data
all_data <- list()
for (year in available_years) {
  year_data <- read_year_data(year, data_dir)
  if (!is.null(year_data)) {
    all_data[[as.character(year)]] <- year_data
  }
}

# all_data
#   ├── "2021"
#   │   ├── year: 2021
#   │   ├── T2: [38, 41, 51, 730] temp
#   │   ├── Td: [38, 41, 51, 730] dew point
#   │   ├── step: [0, 1, 2, ..., 40]
#   │   ├── validTime: time info
#   │   └── gridpoint: [605, 639, 674, ...]
#   ├── "2022"
#   │   └── (same structure)
#   └── ...

# example: extract 2021 temp
#T2_2021 <- all_data[["2021"]]$T2

```

## create a tidy table for forecast(not completed)
```{r}
tidy_forecast <- function(raw_forecast_data, day_i, loc_i) {
  # extract data
  daily_forecast <- raw_forecast_data[loc_i, , , day_i] |>
    as.data.frame()
  
  names(daily_forecast) <- paste0("M", 1:ncol(daily_forecast))
  
  daily_forecast <- daily_forecast |>
    mutate(lead_time_hrs = seq(0, 240, length.out = nrow(daily_forecast))) |>
    pivot_longer(cols = starts_with("M"), 
                 names_to = "Member", 
                 values_to = "Forecast_value")
  
  return(daily_forecast)
}

# create tidy table for all years
create_year_tidy <- function(year_data, loc_i , day_i ) {
  # temperature
  temp_tidy <- tidy_forecast(year_data$T2, day_i, loc_i) |>
    rename(Temperature = Forecast_value)
  
  # dew points
  dewpoint_tidy <- tidy_forecast(year_data$Td, day_i, loc_i) |>
    select(lead_time_hrs, Member, Dewpoint = Forecast_value)
  
  # combine all elements
  combined <- temp_tidy |>
    left_join(dewpoint_tidy, by = c("lead_time_hrs", "Member")) |>
    mutate(
      year = year_data$year,
      grid_point_id = year_data$gridpoint[loc_i],
      valid_time_hours = year_data$validTime[day_i],
    )
  
  return(combined)
}

# test
tidy_2021_1_1 <- create_year_tidy(all_data[["2021"]],1,1)

# check results
head(tidy_2021_1_1)
tail(tidy_2021_1_1)

```

##import meta data to find locations(lon and lat) for gridpoints and their corresponding stations
```{r}
#import meta data
prediction_metadata <- read.csv(here("data", "ToSend-01-20-2025", "prediction_meta.csv"))
sta_gp_metadata <- read.csv(here("data", "ToSend-01-20-2025", "sta_gp_metadata.csv"))
sta_gp_metadata <- sta_gp_metadata %>%
  select(-X)
# find all grid points appeared in our all_data data set
all_gridpoints <- c()
for (year in names(all_data)) {
  all_gridpoints <- c(all_gridpoints, all_data[[year]]$gridpoint)
}
unique_gridpoints <- sort(unique(all_gridpoints))

#match them with meta

gridpoint_lookup <- data.frame(
  data_index = 1:length(unique_gridpoints),
  gridpoint = unique_gridpoints
)

# merge
gridpoint_lookup <- merge(gridpoint_lookup, prediction_metadata,
                         by = "gridpoint",
                         all.x = TRUE)%>%select(-data_index)
gridpoint_lookup <- gridpoint_lookup %>%
  left_join(sta_gp_metadata, by = c("gridpoint" = "gp"))%>%
  select(-sta_id,
         gp_lat = gp_lat.x, 
         gp_lon = gp_lon.x, 
         everything(),
         -gp_lat.y, 
         -gp_lon.y)

# one-to-many relationship when joining two datasets where one gridpoint maps to multiple stations, causing duplicate rows in the merged data 
gridpoint_station_table = gridpoint_lookup %>% 
  mutate(
    # determine primary or secondary
    station_type = ifelse(station_id == sta_id, "primary", "secondary")
  )%>%
  mutate(
    is_coast = ifelse(station_type == "secondary", NA, is_coast),
    clc_dist0 = ifelse(station_type == "secondary", NA, clc_dist0),
    dist = ifelse(station_type == "secondary", NA, dist)
  )%>%
  select(-station_id)

gridpoint_station_table

## Verify guess
## There are 38 grid point locations in the data but 46 stations so Kiri guessed that there may be more than one station per grid point - this is worth checking. We will need to follow up about the mapping from grid points to stations. 

station_count <- gridpoint_station_table %>%
  group_by(gridpoint) %>%
  summarise(
    n_stations = sum(!is.na(sta_id)),  
  ) %>%
  arrange(desc(n_stations))  

station_count
length(station_count$gridpoint)
sum(station_count$n_stations)

# only found 43 stations in 38 grid points

# In addition for some gridpoints like 819 , it has 2 relate stations with different station_id, sta_lat and sta_lon
```

## find stations near cities
```{r}
# lon and lat for different cities
cities <- data.frame(
  city = c("Amsterdam", "Rotterdam", "Utrecht", "The Hague", "Eindhoven", 
           "Groningen", "Tilburg", "Almere", "Breda", "Nijmegen",
           "Haarlem", "Arnhem", "Zaanstad", "Apeldoorn", "Enschede",
           "Amersfoort", "Zwolle", "Dordrecht", "Leiden", "Maastricht",
           "Delft", "Alkmaar", "Leeuwarden", "Middelburg", "Den Helder"),
  city_lat = c(52.37, 51.92, 52.09, 52.08, 51.44,
               53.22, 51.56, 52.37, 51.59, 51.84,
               52.38, 51.98, 52.44, 52.21, 52.22,
               52.16, 52.51, 51.81, 52.16, 50.85,
               52.01, 52.63, 53.20, 51.50, 52.96),
  city_lon = c(4.90, 4.48, 5.12, 4.30, 5.48,
               6.57, 5.08, 5.22, 4.78, 5.87,
               4.64, 5.90, 4.83, 5.97, 6.90,
               5.39, 6.09, 4.67, 4.49, 5.69,
               4.36, 4.75, 5.80, 3.61, 4.76),
  population_rank = c(1, 2, 4, 3, 5,    # population rank
                      6, 7, 8, 9, 10,
                      11, 12, 13, 14, 15,
                      16, 17, 18, 19, 20,
                      21, 22, 23, 24, 25),
  region = c("North Holland", "South Holland", "Utrecht", "South Holland", "North Brabant",
             "Groningen", "North Brabant", "Flevoland", "North Brabant", "Gelderland",
             "North Holland", "Gelderland", "North Holland", "Gelderland", "Overijssel",
             "Utrecht", "Overijssel", "South Holland", "South Holland", "Limburg",
             "South Holland", "North Holland", "Friesland", "Zeeland", "North Holland")
)

# Find nearest station for each city
city_connections <- cities %>%
 rowwise() %>%
 mutate(
   # Calculate distances to all stations
   distances = list(sqrt((gridpoint_station_table$sta_lat - city_lat)^2 + 
                        (gridpoint_station_table$sta_lon - city_lon)^2) * 111),
   nearest_idx = which.min(distances),
   station_lat = gridpoint_station_table$sta_lat[nearest_idx],
   station_lon = gridpoint_station_table$sta_lon[nearest_idx],
   distance_km = round(min(distances), 1)
 )

# Create simple connection map
city_station_plot = ggplot() +
  # Connection lines
  geom_segment(data = city_connections,
               aes(x = city_lon, y = city_lat, xend = station_lon, yend = station_lat),
               alpha = 0.3) +
  
  # Primary Stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "primary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "red", size = 2) +
  
  # Secondary Stations (yellow.samll size)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "gold", size = 1) +
 
 # Cities
 geom_point(data = cities,
            aes(x = city_lon, y = city_lat, size = 1/population_rank), color = "blue" ) +
 
 # Labels for major cities only
 geom_text_repel(data = cities ,
                 aes(x = city_lon, y = city_lat, label = city),
                 size = 3) +
  
 geom_text_repel(data = gridpoint_station_table ,
                 aes(x = sta_lon, y = sta_lat, label = sta_id),
                 size = 2) +
  
 labs(title = "Cities and Nearest Weather Stations",
     subtitle = "City points size is determinted by its population rank",
     x = "Longitude", y = "Latitude")+
 theme_minimal() +
 coord_fixed(1.3)+
 scale_size_continuous(guide = FALSE)

city_station_plot

ggsave(
  filename = "Cities and Nearest Weather Stations.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

```

## find stations near grid points,for some gridpoints like 819 , it has 2 relate stations but same station_id different sta_lat and sta_lon
```{r}
# Create visualization
netherlands <- ne_countries(country = "netherlands", returnclass = "sf", scale = "medium")

gridpoint_station_map <- ggplot() +
  #geom_sf(data = netherlands, fill = NA, color = "black", size = 0.8) +
  # Connection lines
  geom_segment(data = gridpoint_station_table,
               aes(x = gp_lon, y = gp_lat, xend = sta_lon, yend = sta_lat),
               alpha = 0.3) +
  # Plot gridpoint points (using squares)
  geom_point(data = gridpoint_station_table,
             aes(x = gp_lon, y = gp_lat, shape = "Gridpoints"),
             color = "darkblue") +
  
  # Plot primary stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "primary"),
             aes(x = sta_lon, y = sta_lat, shape = "Primary Stations"),
             color = "red") +
  
  # Plot secondary stations (yellow)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat, shape = "Secondary Stations"),
             color = "gold") +
  
  # Set shapes
  scale_shape_manual(values = c("Gridpoints" = 15, 
                               "Primary Stations" = 16,
                               "Secondary Stations" = 17),
                     name = "Type") +
  
  # Add gridpoint labels
  geom_text_repel(data = gridpoint_station_table,
                  aes(x = gp_lon, y = gp_lat, label = gridpoint),
                  size = 2.5,
                  color = "darkblue",
                  box.padding = 0.3,
                  point.padding = 0.2,
                  max.overlaps = 20) +
  
  # Add primary station labels (red)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "primary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "red",
                  nudge_y = 0.02,
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  # Add secondary station labels (yellow)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "secondary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "gold",
                  nudge_y = -0.02,  #avoid overlapping
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  labs(title = "ECMWF Gridpoints and KNMI Stations in the Netherlands",
       subtitle = "Primary stations (red) vs Secondary stations (yellow)",
       x = "Longitude",
       y = "Latitude") +
  
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

gridpoint_station_map

ggsave(
  filename = "ECMWF Gridpoints and KNMI Stations in the Netherlands.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

# every station is super close to its corresponding grid points
```



#Write code so we can visualise a forecast on a given day (think spaghetti type plot)
```{r}
library(ncdf4)
library(dplyr)
library(tidyr)
library(ggplot2)
```

#These are the files starting with "kis". It contains 10-min observations at stations between 2021 and 2024 following the link I sent you. You would have to subset it to match the time resolution of the forecasts, and combine the different years and months together.
#Source: https://dataplatform.knmi.nl/dataset/vochtigheid-en-temperatuur-1-0
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(lubridate)


readLines("data/ToSend-01-20-2025/kis_tot_202106.gz", n = 25)

kis_tot_202106 <- read_table("data/ToSend-01-20-2025/kis_tot_202106.gz", skip = 21)

head(kis_tot_202106)
tail(kis_tot_202106)

summary(kis_tot_202106)
#U_SEA_10 and x19 all NA
#some vaiables like U_10,TX_DRYB_10 miss too many records
#T_WETB_10, TX_DRYB_10, U_10 show maximums of 100, 99, or even 114.3—values outside any physical range
```






