---
title: "Forecast data import and visualisation"
author: "Wenkai Zhong"
date: "2025-07-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#change R language to english
Sys.setlocale("LC_TIME", "English")


library(R.utils)
library(ggplot2)
library(patchwork)
library(lubridate)
library(here)
library(ncdf4)
library(ggrepel)
library(tidyverse)
library(plotly)
#library(sf)
#library(rnaturalearth)

# creat .gitignore file to avoid upload data(too large)
cat("# Ignore all data files
data/
*.RData
*.Rhistory
.Rproj.user/
.RDataTmp*
", file = ".gitignore")
```

## Reading in the netcdf

# Model: These are the files starting with "combined_raw_". It contains ECMWF-IFS ensemble forecasts (50+1 members) over the Netherlands at 6-h time resolution.
#check combined_raw_2d/2t_year data
#2d = dew point temperature
#2t = 2-meter temperature
#NetCDF data type

#Here is basiclly what this nc data set looks like
combined_raw_2t_2021.nc (Temperature data)
combined_raw_2d_2021.nc (Dewpoint data)

Data Structure (4D array):
[location, lead_time, ensemble_member, forecasts number(two forecasts daily)]
[38,       41,        51,              730]

Visual Representation:
┌─────────────────────────────────────────────┐
│              Year 2021 Data                 │
├─────────────────────────────────────────────┤
│  Forecast Axis (730 forecasts)                        │
│  ↓                                          │
│  forecasts 1 
         ┌─────────────────────────┐         │
│        │ Loc1  Loc2 ... Loc38   │ ← 38 locations
│        ├─────────────────────────┤         │
│        │ 0h  ┌─────────────┐    │         │
│        │ 6h  │ M1 M2...M51 │    │ ← 51 ensemble members
│        │ 12h │ Temp values │    │         │
│        │ ... │   matrix    │    │         │
│        │240h └─────────────┘    │ ← 41 lead times
│        └─────────────────────────┘         │
│                                            │
│  forecasts 2 
         ┌─────────────────────────┐         │
│        │ (same structure)        │         │
│        └─────────────────────────┘         │
│  ...                                        │
│                                             │
│  forecasts 730 
           ┌───────────────────────┐         │
│          │ (same structure)      │         │
│          └───────────────────────┘         │
└─────────────────────────────────────────────┘

Example indexing:
all_data[["2021"]]$T2[1, 1, 1, 1] = Location 1, Hour 0, Member 1, Forecast 1
all_data[["2021"]]$T2[38, 41, 51, 730] = Location 38, Hour 240, Member 51, Forecast 730

Dimension meanings:
- gridpoint: [605, 639, 674, ...] (38 station IDs)
- step: [0, 6, 12, ..., 240] (41 forecast hours)
- member: 1-50 are ensemble members, 51 is control forecast
- validTime: [timestamp1, timestamp2, ..., timestamp730] (730 forecast times)

##after test and some preliminary research,we start to import whole dataset
##functions that help us to extract data from nc files
```{r}
#rm(list = ls())
#use example: temp_2021 <- read_data(2021, "2t")
read_data <- function(year, var_type, data_dir = here("data", "ToSend-01-20-2025")) {
  # Build filename
  filename <- file.path(data_dir, paste0("combined_raw_", var_type, "_", year, ".nc"))
  
  # Open file
  nc <- nc_open(filename)
  
  # Read main variable
  var_name <- paste0("x", var_type)  # x2t or x2d
  data <- ncvar_get(nc, var_name)
  
  # Read other information
  step <- ncvar_get(nc, "step")
  validTime <- ncvar_get(nc, "validTime")
  gridpoint <- ncvar_get(nc, "gridpoint")
  member <- if("member" %in% names(nc$dim)) ncvar_get(nc, "member") else NULL
  
  runtime_info <- nc$dim$runtime
  
  # Close file
  nc_close(nc)
  
  # Return
  return(list(
    data = data,
    step = step,
    validTime = validTime,
    gridpoint = gridpoint,
    member = member,
    runtime_units = runtime_info$units,
    runtime_vals = runtime_info$vals
  ))
}

# Test
temp_2023 <- read_data(2023, "2t")  # Read combined_raw_2t_2021.nc
dewp_2021 <- read_data(2021, "2d")  # Read combined_raw_2d_2021.nc
temp_2023_start_time <- temp_2023$runtime_units
temp_2023_start_time
dewp_2021_start_time <- dewp_2021$runtime_units
dewp_2021_start_time
```

###function that help us to convert readed data to tidy format
```{r}
#example：example_day <- tidy_formation(temp_2021, gridpoint_idx = 1, validtime_idx = 100)
tidy_formation <- function(data, gridpoint_idx, validtime_idx) {
  # Extract reference datetime from runtime_units (e.g., "days since 2021-01-31 00:00:00")
  ref_datetime_str <- gsub(".*since\\s+([0-9-]+\\s+[0-9:]+).*", "\\1", data$runtime_units)
  ref_datetime <- ymd_hms(ref_datetime_str)
  
  # validTime[1, validtime_idx] gives hours from reference time for this forecast initialization
  init_hours_from_ref <- data$validTime[1, validtime_idx]
  forecast_init_datetime <- ref_datetime + (init_hours_from_ref * 3600)
  
  print(paste("Forecast initialization time:", forecast_init_datetime))
  
  # Extract data slice for [gridpoint, step, member, validtime]
  data_slice <- data$data[gridpoint_idx, , , validtime_idx]
  df <- as.data.frame(t(data_slice))
  names(df) <- paste0("Step_", 0:40)
  df$Member <- paste0("M", seq_len(nrow(df)))
  
  # Create lead time hours vector (0 to 240 hours in 41 steps)
  lead_times_hours <- seq(0, 240, length.out = 41)
  
  # Pivot to long format and add metadata
  tidy_df <- df %>%
    pivot_longer(
      cols = starts_with("Step_"),
      names_to = "Step_idx",
      values_to = "Forecast_value"
    ) %>%
    mutate(
      Step_idx = as.numeric(gsub("Step_", "", Step_idx)),
      lead_time_hrs = lead_times_hours[Step_idx + 1],  # +1 because R is 1-indexed
      Gridpoint_idx = gridpoint_idx,
      ValidTime_idx = validtime_idx,
      Gridpoint = data$gridpoint[gridpoint_idx],
      Forecast_init_datetime = forecast_init_datetime,
      # Valid time = initialization time + lead time
      Valid_datetime = forecast_init_datetime + (lead_time_hrs * 3600),
    )
  
  return(tidy_df)
}

# Example usage and verification
# # Convert specific validtime to tidy format
temp_example_day <- tidy_formation(temp_2023, gridpoint_idx = 1, validtime_idx = 1)
temp_example_day

dewp_example_day <- tidy_formation(dewp_2021, gridpoint_idx = 1, validtime_idx = 1)
dewp_example_day
```

##function that we only input forecats_time and gridpoint to generate tidy forecast table
```{r}
# Helper function to find runtime index for a given date

# Helper functions
find_runtime_index <- function(data, target_datetime) {
  # Check if input includes time or just date
  has_time <- grepl("\\d{2}:\\d{2}", target_datetime)
  
  # Parse reference datetime
  ref_datetime_str <- gsub(".*since\\s+([0-9-]+\\s+[0-9:]+).*", "\\1", data$runtime_units)
  ref_datetime <- as.POSIXct(ref_datetime_str, tz = "UTC")
  
  if (has_time) {
    # If time is specified, find exact forecast
    target_dt <- as.POSIXct(target_datetime, tz = "UTC")
    
    # Calculate hours since reference
    hours_since_ref <- as.numeric(difftime(target_dt, ref_datetime, units = "hours"))
    
    # Find matching index in validTime[1,]
    idx <- which(abs(data$validTime[1,] - hours_since_ref) < 0.1)
    
    if (length(idx) == 0) {
      # No exact match, find closest
      idx <- which.min(abs(data$validTime[1,] - hours_since_ref))
      warning(paste("No exact match for", target_datetime, 
                    ". Returning closest forecast at index", idx))
    } else if (length(idx) > 1) {
      # Multiple matches (shouldn't happen), take first
      idx <- idx[1]
      warning(paste("Multiple matches found for", target_datetime, 
                    ". Returning first match at index", idx))
    }
    
    return(idx)
    
  } else {
    # If only date is specified, return all forecasts for that day
    target_date <- as.Date(target_datetime)
    days_since_ref <- as.numeric(target_date - as.Date(ref_datetime))
    
    # Calculate hours for 00:00 and 12:00 UTC
    hours_00 <- days_since_ref * 24
    hours_12 <- days_since_ref * 24 + 12
    
    # Find indices
    indices_00 <- which(abs(data$validTime[1,] - hours_00) < 0.1)
    indices_12 <- which(abs(data$validTime[1,] - hours_12) < 0.1)
    
    all_indices <- c(indices_00, indices_12)
    
    # Sort by initialization time
    all_indices <- all_indices[order(data$validTime[1, all_indices])]
    
    # Print info about found forecasts
    for (i in seq_along(all_indices)) {
      init_hours <- data$validTime[1, all_indices[i]]
      init_time <- ref_datetime + (init_hours * 3600)
    }
    
    return(all_indices)
  }
}

# Test examples
# Test 1: Find specific forecast with time
test1 <- find_runtime_index(temp_2023, "2023-01-21 00:00:00")
test2 <- find_runtime_index(temp_2023, "2023-01-21 12:00:00")
test3 <- find_runtime_index(dewp_2021, "2021-05-17 00:00:00")
test4 <- find_runtime_index(dewp_2021, "2021-01-31 00:00:00")
test1 
test2 
test3 
test4 

find_gridpoint_index <- function(data, gridpoint_id) {
  idx <- which(data$gridpoint == gridpoint_id)
  if (length(idx) == 0) {
    stop("Gridpoint ID ", gridpoint_id, " not found")
  }
  return(idx)
}

test_grid_1 = find_gridpoint_index(temp_2023, 605)
test_grid_1
test_grid_2 = find_gridpoint_index(dewp_2021, 605)
test_grid_2

```

#check forecasts that be made in a specific date
```{r}

# Main function
tidy_table_ultimate <- function(forecast_datetime, gridpoint_id) {
  # Find relative data set
  year <- lubridate::year(as.POSIXct(forecast_datetime))
  
  temp_data <- read_data(year, "2t")
  dewp_data <- read_data(year, "2t")
  
  # Step 1: Find the runtime index for temperature and dewpoint
  runtime_temp_idx <- find_runtime_index(temp_data, forecast_datetime)
  runtime_dewp_idx <- find_runtime_index(dewp_data, forecast_datetime)
  
  # Check if unique runtime index was found
  if (length(runtime_temp_idx) != 1 || length(runtime_dewp_idx) != 1) {
    stop(paste("Could not uniquely identify forecast time", forecast_datetime, 
               "in one or both datasets. Please check time format and data."))
  }
  
  # Step 2: Find the gridpoint index
  grid_idx_temp <- find_gridpoint_index(temp_data, gridpoint_id)
  grid_idx_dewp <- find_gridpoint_index(dewp_data, gridpoint_id)
  
  # Step 3: Extract tidy data
  temp_tidy <- tidy_formation(temp_data, grid_idx_temp, runtime_temp_idx)
  dewp_tidy <- tidy_formation(dewp_data, grid_idx_dewp, runtime_dewp_idx)
  
  # Step 4: Combine and format
  tidy_combined <- temp_tidy %>%
    rename(Temperature_K = Forecast_value) %>%
    mutate(
      DewPoint_K = dewp_tidy$Forecast_value,
      # Convert to Celsius
      Temperature_C = Temperature_K - 273.15,
      DewPoint_C = DewPoint_K - 273.15,
      # Add time information
      Forecast_init_date = as.Date(Forecast_init_datetime),
      Forecast_init_time = format(Forecast_init_datetime, "%H:%M:%S"),
      Valid_date = as.Date(Valid_datetime),
      Valid_time = format(Valid_datetime, "%H:%M:%S"),
      # Gridpoint ID
      Gridpoint_ID = gridpoint_id
    ) %>%
    select(
      Member, 
      lead_time_hrs,
      Forecast_init_datetime,
      Forecast_init_date,
      Forecast_init_time,
      Valid_datetime,
      Valid_date,
      Valid_time,
      Temperature_K,
      Temperature_C,
      DewPoint_K,
      DewPoint_C,
      Gridpoint_ID,
      everything()
    )
  
  return(tidy_combined)
}


# Test the function
tidy_result_2021_01_31_00_G605 <- tidy_table_ultimate("2021-05-17 00:00:00", 605)
tidy_result_2021_01_31_00_G605
# View the first few rows
head(tidy_result_2021_01_31_00_G605)

# Check structure
str(tidy_result_2021_01_31_00_G605)

# Test with different dates and times
tidy_result_2021_01_31_12_G605 <- tidy_table_ultimate("2021-01-31 12:00:00", 605)
tidy_result_2021_08_13_00_G605 <- tidy_table_ultimate("2023-01-21 00:00:00", 605)
tidy_result_2021_08_13_00_G605
```


##import meta data to find locations(lon and lat) for gridpoints and their corresponding stations
```{r}
#import meta data
prediction_metadata <- read.csv(here("data", "ToSend-01-20-2025", "prediction_meta.csv"))
sta_gp_metadata <- read.csv(here("data", "ToSend-01-20-2025", "sta_gp_metadata.csv"))
sta_gp_metadata <- sta_gp_metadata %>%
  select(-X)

# all grid points appeared in our all_data data set
unique_gridpoints <- c(605, 639, 674, 676, 680, 715, 745, 747, 787, 818, 819, 821, 854, 857, 891, 896, 935, 965, 967, 969, 971, 1001, 1002, 1003, 1041, 1073, 1074, 1080, 1111, 1112, 1114, 1118, 1147, 1148, 1154, 1187, 1193, 1269)

#match them with meta

gridpoint_lookup <- data.frame(
  data_index = 1:length(unique_gridpoints),
  gridpoint = unique_gridpoints
)

# merge
gridpoint_lookup <- merge(gridpoint_lookup, prediction_metadata,
                         by = "gridpoint",
                         all.x = TRUE)%>%select(-data_index)
gridpoint_lookup <- gridpoint_lookup %>%
  left_join(sta_gp_metadata, by = c("gridpoint" = "gp"))%>%
  select(-sta_id,
         gp_lat = gp_lat.x, 
         gp_lon = gp_lon.x, 
         everything(),
         -gp_lat.y, 
         -gp_lon.y)

# one-to-many relationship when joining two datasets where one gridpoint maps to multiple stations, causing duplicate rows in the merged data 
gridpoint_station_table = gridpoint_lookup %>% 
  mutate(
    # determine primary or secondary
    station_type = ifelse(station_id == sta_id, "primary", "secondary")
  )%>%
  mutate(
    is_coast = ifelse(station_type == "secondary", NA, is_coast),
    clc_dist0 = ifelse(station_type == "secondary", NA, clc_dist0),
    dist = ifelse(station_type == "secondary", NA, dist)
  )%>%
  select(-station_id)

gridpoint_station_table

## Verify guess
## There are 38 grid point locations in the data but 46 stations so Kiri guessed that there may be more than one station per grid point - this is worth checking. We will need to follow up about the mapping from grid points to stations. 

station_count <- gridpoint_station_table %>%
  group_by(gridpoint) %>%
  summarise(
    n_stations = sum(!is.na(sta_id)),  
  ) %>%
  arrange(desc(n_stations))  

station_count
length(station_count$gridpoint)
sum(station_count$n_stations)

# only found 43 stations in 38 grid points

# In addition, for some grid points like 819 , it has 2 relate stations with different station_id, sta_lat and sta_lon
```

```{r}
tidy_forecast_with_station_grid_location <- function(target_datetime, gridpoint_id, 
                                                    temp_data = NULL, 
                                                    dewp_data = NULL,
                                                    station_table = NULL) {
  
  # Use default data if not provided
  if (is.null(temp_data)) temp_data <- temp_2021
  if (is.null(dewp_data)) dewp_data <- dewp_2021
  if (is.null(station_table)) station_table <- gridpoint_station_table
  
  # Get forecast data using tidy_table_ultimate
  forecast_data <- tidy_table_ultimate(
    forecast_datetime = target_datetime, 
    gridpoint_id = gridpoint_id,
    temp_data = temp_data,
    dewp_data = dewp_data
  )
  
  # Add station information
  forecast_with_station <- forecast_data %>%
    left_join(
      station_table %>%
        select(gridpoint, sta_id, sta_lat, sta_lon, dist, is_coast, 
               gp_lat, gp_lon, clc_dist0),
      by = c("Gridpoint_ID" = "gridpoint")
    ) %>%
    # Rename columns for clarity
    rename(
      station_id = sta_id,
      station_lat = sta_lat,
      station_lon = sta_lon,
      gridpoint_to_station_dist = dist,
      gridpoint_lat = gp_lat,
      gridpoint_lon = gp_lon,
      coastal_distance = clc_dist0
    ) %>%
    # Reorder columns for better readability
    select(
      # Forecast timing info
      Member, lead_time_hrs,
      Forecast_init_datetime, 
      Valid_datetime, 
      # Weather values
      Temperature_K, Temperature_C, DewPoint_K, DewPoint_C,
      # Location info
      Gridpoint_ID, station_id, 
      station_lat, station_lon,
      gridpoint_lat, gridpoint_lon,
      gridpoint_to_station_dist,
      is_coast, coastal_distance,
    )
  
  return(forecast_with_station)
}

# Test with specific datetime
tidy_result_2021_08_13_12_G605 <- tidy_forecast_with_station_grid_location(
  "2021-05-17 00:00:00", 
  605
)

tidy_result_2021_08_13_12_G605
```

#function that input the time be forecasted and return relative tidy table
```{r}
get_forecasts_for_valid_time <- function(target_valid_datetime, 
                                       gridpoint_id,
                                       max_days_back = 10,
                                       temp_data = NULL,
                                       dewp_data = NULL,
                                       station_table = NULL) {
  
  # Use default data if not provided
  if (is.null(temp_data)) temp_data <- temp_2021
  if (is.null(dewp_data)) dewp_data <- dewp_2021
  if (is.null(station_table)) station_table <- gridpoint_station_table
  
  # Ensure target time is in POSIXct format
  target_time <- as.POSIXct(target_valid_datetime, tz = "UTC")
  
  # Initialize results list
  all_forecasts <- list()
  
  # Loop through previous N days to find forecasts that can reach this valid time
  for (days_back in 0:max_days_back) {
    # For each day, check both 00:00 and 12:00 forecasts
    for (hour in c(0, 12)) {
      # Calculate potential forecast initialization time
      forecast_init_time <- target_time - (days_back * 24 + hour) * 3600
      forecast_datetime_str <- format(forecast_init_time, "%Y-%m-%d %H:%M:%S")
      
      # Skip if forecast time is in the future
      if (forecast_init_time > Sys.time()) next
      
      # Calculate lead time needed
      lead_time_hours <- as.numeric(difftime(target_time, forecast_init_time, units = "hours"))
      
      # Skip if lead time is beyond 240 hours (10 days)
      if (lead_time_hours > 240 || lead_time_hours < 0) next
      
      tryCatch({
        # Get forecast data
        forecast_table <- tidy_forecast_with_station_grid_location(
          forecast_datetime_str, 
          gridpoint_id,
          temp_data = temp_data,
          dewp_data = dewp_data,
          station_table = station_table
        )
        
        # Filter rows where Valid_datetime matches target time
        matched_rows <- forecast_table %>%
          filter(abs(difftime(Valid_datetime, target_time, units = "secs")) < 1)
        
        # If matching rows found, add to results
        if (nrow(matched_rows) > 0) {
          matched_rows <- matched_rows %>%
            mutate(
              forecast_age_hours = lead_time_hours,
              forecast_age_days = round(lead_time_hours / 24, 1),
              forecast_origin = forecast_datetime_str
            )
          
          all_forecasts[[forecast_datetime_str]] <- matched_rows
          message(paste("✓ Found", nrow(matched_rows)/51, 
                       "forecast(s) from", forecast_datetime_str,
                       "(", round(lead_time_hours), "hours ahead)"))
        }
        
      }, error = function(e) {
        # Only show error for debugging if needed
        # message(paste("  No data for", forecast_datetime_str))
      })
    }
  }
  
  # Combine all results
  if (length(all_forecasts) > 0) {
    result <- bind_rows(all_forecasts) %>%
      arrange(desc(Forecast_init_datetime)) %>%
      # Add ranking by forecast recency
      mutate(
        forecast_rank = dense_rank(desc(Forecast_init_datetime))
      )
    
    return(result)
  } else {
    warning(paste("No forecasts found for valid time:", target_valid_datetime))
    return(NULL)
  }
}

# Test the function
# Find all forecasts predicting temperature for 2021-08-15 12:00:00
forecasts_for_target <- get_forecasts_for_valid_time(
  "2021-08-15 12:00:00", 
  gridpoint_id = 605,
  max_days_back = 10
)

forecasts_for_target
```

################### ( Visualization starts here :) ######################


## find stations near cities
```{r}
# lon and lat for different cities
cities <- data.frame(
  city = c("Amsterdam", "Rotterdam", "Utrecht", "The Hague", "Eindhoven", 
           "Groningen", "Tilburg", "Almere", "Breda", "Nijmegen",
           "Haarlem", "Arnhem", "Zaanstad", "Apeldoorn", "Enschede",
           "Amersfoort", "Zwolle", "Dordrecht", "Leiden", "Maastricht",
           "Delft", "Alkmaar", "Leeuwarden", "Middelburg", "Den Helder"),
  city_lat = c(52.37, 51.92, 52.09, 52.08, 51.44,
               53.22, 51.56, 52.37, 51.59, 51.84,
               52.38, 51.98, 52.44, 52.21, 52.22,
               52.16, 52.51, 51.81, 52.16, 50.85,
               52.01, 52.63, 53.20, 51.50, 52.96),
  city_lon = c(4.90, 4.48, 5.12, 4.30, 5.48,
               6.57, 5.08, 5.22, 4.78, 5.87,
               4.64, 5.90, 4.83, 5.97, 6.90,
               5.39, 6.09, 4.67, 4.49, 5.69,
               4.36, 4.75, 5.80, 3.61, 4.76),
  population_rank = c(1, 2, 4, 3, 5,    # population rank
                      6, 7, 8, 9, 10,
                      11, 12, 13, 14, 15,
                      16, 17, 18, 19, 20,
                      21, 22, 23, 24, 25),
  region = c("North Holland", "South Holland", "Utrecht", "South Holland", "North Brabant",
             "Groningen", "North Brabant", "Flevoland", "North Brabant", "Gelderland",
             "North Holland", "Gelderland", "North Holland", "Gelderland", "Overijssel",
             "Utrecht", "Overijssel", "South Holland", "South Holland", "Limburg",
             "South Holland", "North Holland", "Friesland", "Zeeland", "North Holland")
)

# Find nearest station for each city
city_connections <- cities %>%
 rowwise() %>%
 mutate(
   # Calculate distances to all stations
   distances = list(sqrt((gridpoint_station_table$sta_lat - city_lat)^2 + 
                        (gridpoint_station_table$sta_lon - city_lon)^2) * 111),
   nearest_idx = which.min(distances),
   station_lat = gridpoint_station_table$sta_lat[nearest_idx],
   station_lon = gridpoint_station_table$sta_lon[nearest_idx],
   distance_km = round(min(distances), 1)
 )

# Create simple connection map
city_station_plot = ggplot() +
  # Connection lines
  geom_segment(data = city_connections,
               aes(x = city_lon, y = city_lat, xend = station_lon, yend = station_lat),
               alpha = 0.3) +
  
  # Primary Stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "primary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "red", size = 2) +
  
  # Secondary Stations (yellow.samll size)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "gold", size = 1) +
 
 # Cities
 geom_point(data = cities,
            aes(x = city_lon, y = city_lat, size = 1/population_rank), color = "blue" ) +
 
 # Labels for major cities only
 geom_text_repel(data = cities ,
                 aes(x = city_lon, y = city_lat, label = city),
                 size = 3) +
  
 geom_text_repel(data = gridpoint_station_table ,
                 aes(x = sta_lon, y = sta_lat, label = sta_id),
                 size = 2) +
  
 labs(title = "Cities and Nearest Weather Stations",
     subtitle = "City points size is determinted by its population rank",
     x = "Longitude", y = "Latitude")+
 theme_minimal() +
 coord_fixed(1.3)+
 scale_size_continuous(guide = FALSE)

city_station_plot

ggsave(
  filename = "Cities and Nearest Weather Stations.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

```

## find stations near grid points,for some gridpoints like 819 , it has 2 relate stations but same station_id different sta_lat and sta_lon
```{r}
# Create visualization
#netherlands <- ne_countries(country = "netherlands", returnclass = "sf", scale = "medium")

gridpoint_station_map <- ggplot() +
  #geom_sf(data = netherlands, fill = NA, color = "black", size = 0.8) +
  # Connection lines
  geom_segment(data = gridpoint_station_table,
               aes(x = gp_lon, y = gp_lat, xend = sta_lon, yend = sta_lat),
               alpha = 0.3) +
  # Plot gridpoint points (using squares)
  geom_point(data = gridpoint_station_table,
             aes(x = gp_lon, y = gp_lat, shape = "Gridpoints"),
             color = "darkblue") +
  
  # Plot primary stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "primary"),
             aes(x = sta_lon, y = sta_lat, shape = "Primary Stations"),
             color = "red") +
  
  # Plot secondary stations (yellow)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat, shape = "Secondary Stations"),
             color = "gold") +
  
  # Set shapes
  scale_shape_manual(values = c("Gridpoints" = 15, 
                               "Primary Stations" = 16,
                               "Secondary Stations" = 17),
                     name = "Type") +
  
  # Add gridpoint labels
  geom_text_repel(data = gridpoint_station_table,
                  aes(x = gp_lon, y = gp_lat, label = gridpoint),
                  size = 2.5,
                  color = "darkblue",
                  box.padding = 0.3,
                  point.padding = 0.2,
                  max.overlaps = 20) +
  
  # Add primary station labels (red)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "primary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "red",
                  nudge_y = 0.02,
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  # Add secondary station labels (yellow)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "secondary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "gold",
                  nudge_y = -0.02,  #avoid overlapping
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  labs(title = "ECMWF Gridpoints and KNMI Stations in the Netherlands",
       subtitle = "Primary stations (red) vs Secondary stations (yellow)",
       x = "Longitude",
       y = "Latitude") +
  
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

gridpoint_station_map

ggsave(
  filename = "ECMWF Gridpoints and KNMI Stations in the Netherlands.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

# every station is super close to its corresponding grid points
```
```{r}
#automate plot function using gridpoint_id date and members to plot temperature
auto_forecast_plot_faceted <- function(forecast_datetime, 
                                     gridpoint_id, 
                                     members,
                                     variable = "Temperature_C",
                                     temp_data = NULL,
                                     dewp_data = NULL,
                                     station_table = NULL) {
  
  # Use default data if not provided
  if (is.null(temp_data)) temp_data <- temp_2021
  if (is.null(dewp_data)) dewp_data <- dewp_2021
  
  # Get the tidy data with station info
  tidy_data <- tidy_forecast_with_station_grid_location(
    target_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id,
    temp_data = temp_data,
    dewp_data = dewp_data,
    station_table = station_table
  )
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names)
  
  # Extract station info for subtitle
  station_info <- unique(plot_data$station_id)[1]
  is_coastal <- unique(plot_data$is_coast)[1]
  
  # Create base plot
  p <- ggplot(plot_data, aes(x = lead_time_hrs, y = .data[[variable]], group = Member))
  
  # Check number of members
  n_members <- length(members)
  
  
  # Use gray lines for many members - THIS IS YOUR CASE WITH 51 MEMBERS
  p <- p + 
    geom_line(size = 0.3, alpha = 0.4, color = "gray50") +
    # Add ensemble mean as a thicker line
    stat_summary(fun = mean, geom = "line", color = "gray", size = 0.3, alpha = 0.6)
  
  
  # Add labels and theme
  p <- p +
    labs(
      title = paste("Forecast initialized at", format(unique(plot_data$Forecast_init_datetime)[1], "%Y-%m-%d %H:%M UTC")),
      subtitle = paste("Gridpoint", gridpoint_id, "| Station:", station_info, 
                      "| Coastal:", ifelse(is_coastal, "Yes", "No"),
                      "| Members:", n_members),
      x = "Lead Time (hours)",
      y = ifelse(variable == "Temperature_C", "Temperature (°C)", 
                ifelse(variable == "DewPoint_C", "Dew Point (°C)", 
                       ifelse(variable == "Temperature_K", "Temperature (K)",
                              ifelse(variable == "DewPoint_K", "Dew Point (K)", variable)))),
      color = if(n_members <= 25) "Member" else NULL
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 11, color = "gray40"),
      legend.position = if(n_members <= 10) "right" else if(n_members <= 25) "bottom" else "none",
      panel.grid.minor = element_blank(),
      panel.border = element_rect(fill = NA, color = "gray80")
    ) +
    scale_x_continuous(
      breaks = seq(0, 240, 24),
      minor_breaks = seq(0, 240, 12),
      labels = function(x) paste0(x, "h\n", format(unique(plot_data$Forecast_init_datetime)[1] + x*3600, "%m/%d"))
    ) +
    coord_cartesian(xlim = c(0, 240))
  
  # Add reference lines for days
  p <- p +
    geom_vline(xintercept = seq(24, 240, 24), alpha = 0.2, linetype = "dashed")
  
  return(p)
}

# Usage:
p_faceted <- auto_forecast_plot_faceted("2021-01-31 00:00:00", 605, members = 1:51)
p_faceted

```

# plot with pdf to be more clear to view the distribution
```{r}
library(patchwork)
auto_forecast_plot_with_pdf_separate <- function(forecast_datetime, 
                                                gridpoint_id, 
                                                members = 1:51, 
                                                variable = "Temperature_C",
                                                pdf_times = c(24, 48, 120, 240),
                                                temp_data = NULL,
                                                dewp_data = NULL) {
  
  # Use default data if not provided
  if (is.null(temp_data)) temp_data <- temp_2021
  if (is.null(dewp_data)) dewp_data <- dewp_2021
  
  # Get tidy data using the new function
  tidy_data <- tidy_table_ultimate(
    forecast_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id,
    temp_data = temp_data,
    dewp_data = dewp_data
  )
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names)
  
  n_members <- length(members)
  
  # Main plot - exactly like your original
  p_main <- ggplot(plot_data, aes(x = lead_time_hrs, y = .data[[variable]], group = Member)) +
    geom_line(alpha = 0.6, color = if(n_members <= 10) "auto" else "gray") +
    geom_vline(xintercept = pdf_times, linetype = "dashed", alpha = 0.5) +
    labs(title = paste("Forecast:", format(unique(plot_data$Forecast_init_datetime)[1], "%Y-%m-%d %H:%M UTC")), 
         x = "Lead Time (hours)", 
         y = variable) +
    theme_minimal() +
    scale_x_continuous(breaks = seq(0, 240, 24))
  
  if (n_members <= 10) p_main <- p_main + aes(color = Member)
  
  # Create a 2x2 grid of PDF plots - exactly like your original
  pdf_plots <- lapply(pdf_times, function(t) {
    pdf_data <- filter(plot_data, abs(lead_time_hrs - t) < 0.1)
    
    ggplot(pdf_data, aes(x = .data[[variable]])) +
      geom_histogram(aes(y = ..density..), bins = 20, fill = "lightblue", 
                    color = "darkblue", alpha = 0.7) +
      geom_density(color = "darkblue", size = 1.2) +
      geom_vline(xintercept = mean(pdf_data[[variable]]), 
                color = "red", linetype = "dashed", size = 1) +
      labs(title = paste0(t, " hours ahead"), 
           x = variable, 
           y = "Density") +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 10),
        plot.margin = margin(10, 10, 10, 10)
      )
  })
  
  # Load patchwork
  library(patchwork)
  
  # Arrange PDFs in a grid below the main plot
  pdf_grid <- wrap_plots(pdf_plots, ncol = 2, nrow = 2)
  
  # Stack main plot and PDF grid
  combined <- p_main / pdf_grid + plot_layout(heights = c(2, 3))
  
  return(combined)
}

# Usage:
# Single time with grid PDFs below
p_pdf = auto_forecast_plot_with_pdf_separate (
  forecast_datetime = "2021-01-31 00:00:00",
  gridpoint_id = 605
)

p_pdf 
```

