---
title: "Forecast data import and visualisation"
author: "Wenkai Zhong"
date: "2025-07-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#change R language to english
Sys.setlocale("LC_TIME", "English")


library(R.utils)
library(ggplot2)
library(patchwork)
library(lubridate)
library(here)
library(ncdf4)
library(ggrepel)
library(tidyverse)
library(plotly)
#library(sf)
#library(rnaturalearth)

# creat .gitignore file to avoid upload data(too large)
cat("# Ignore all data files
data/
*.RData
*.Rhistory
.Rproj.user/
.RDataTmp*
", file = ".gitignore")
```

## Reading in the netcdf

# Model: These are the files starting with "combined_raw_". It contains ECMWF-IFS ensemble forecasts (50+1 members) over the Netherlands at 6-h time resolution.
#check combined_raw_2d/2t_year data
#2d = dew point temperature
#2t = 2-meter temperature
#NetCDF data type

#Here is basiclly what this nc data set looks like
combined_raw_2t_2021.nc (Temperature data)
combined_raw_2d_2021.nc (Dewpoint data)

Data Structure (4D array):
[location, lead_time, ensemble_member, forecasts number(two forecasts daily)]
[38,       41,        51,              730]

Visual Representation:
┌─────────────────────────────────────────────┐
│              Year 2021 Data                 │
├─────────────────────────────────────────────┤
│  Forecast Axis (730 forecasts)                        │
│  ↓                                          │
│  forecasts 1 
         ┌─────────────────────────┐         │
│        │ Loc1  Loc2 ... Loc38   │ ← 38 locations
│        ├─────────────────────────┤         │
│        │ 0h  ┌─────────────┐    │         │
│        │ 6h  │ M1 M2...M51 │    │ ← 51 ensemble members
│        │ 12h │ Temp values │    │         │
│        │ ... │   matrix    │    │         │
│        │240h └─────────────┘    │ ← 41 lead times
│        └─────────────────────────┘         │
│                                            │
│  forecasts 2 
         ┌─────────────────────────┐         │
│        │ (same structure)        │         │
│        └─────────────────────────┘         │
│  ...                                        │
│                                             │
│  forecasts 730 
           ┌───────────────────────┐         │
│          │ (same structure)      │         │
│          └───────────────────────┘         │
└─────────────────────────────────────────────┘

Example indexing:
all_data[["2021"]]$T2[1, 1, 1, 1] = Location 1, Hour 0, Member 1, Forecast 1
all_data[["2021"]]$T2[38, 41, 51, 730] = Location 38, Hour 240, Member 51, Forecast 730

Dimension meanings:
- gridpoint: [605, 639, 674, ...] (38 station IDs)
- step: [0, 6, 12, ..., 240] (41 forecast hours)
- member: 1-50 are ensemble members, 51 is control forecast
- validTime: [timestamp1, timestamp2, ..., timestamp730] (730 forecast times)

##after test and some preliminary research,we start to import whole dataset
##functions that help us to extract data from nc files
```{r}
rm(list = ls())
#use example: temp_2021 <- read_data(2021, "2t")
read_data <- function(year, var_type, data_dir = here("data", "ToSend-01-20-2025")) {
  # Build filename
  filename <- file.path(data_dir, paste0("combined_raw_", var_type, "_", year, ".nc"))
  
  # Open file
  nc <- nc_open(filename)
  
  # Read main variable
  var_name <- paste0("x", var_type)  # x2t or x2d
  data <- ncvar_get(nc, var_name)
  
  # Read other information
  step <- ncvar_get(nc, "step")
  validTime <- ncvar_get(nc, "validTime")
  gridpoint <- ncvar_get(nc, "gridpoint")
  member <- if("member" %in% names(nc$dim)) ncvar_get(nc, "member") else NULL
  
  runtime_info <- nc$dim$runtime
  
  # Close file
  nc_close(nc)
  
  # Return
  return(list(
    data = data,
    step = step,
    validTime = validTime,
    gridpoint = gridpoint,
    member = member,
    runtime_units = runtime_info$units,
    runtime_vals = runtime_info$vals
  ))
}

# Test
# temp_2021 <- read_data(2021, "2t")  # Read combined_raw_2t_2021.nc
#dewp_2021 <- read_data(2021, "2d")  # Read combined_raw_2d_2021.nc
# temp_2021_start_time <- temp_2021$runtime_units
# temp_2021_start_time
# dewp_2021_start_time <- dewp_2021$runtime_units
# dewp_2021_start_time
```

###function that help us to convert readed data to tidy format
```{r}
#example：example_day <- tidy_formation(temp_2021, gridpoint_idx = 1, validtime_idx = 100)
tidy_formation <- function(data, gridpoint_idx, validtime_idx) {
  # Parse reference date from runtime_units (e.g., "days since 2021-01-31 00:00:00")
  ref_date <- as.Date(gsub(".*since\\s+([0-9-]+).*", "\\1", data$runtime_units))
  
  # validtime_idx is the same as day_i in your original code
  # It directly indexes into runtime_vals
  forecast_date <- ref_date + days(data$runtime_vals[validtime_idx])
  
  # Get the data slice [gridpoint, step, member, validtime]
  # This is equivalent to T2[loc_i, 1:41, 1:51, day_i] in your original code
  data_slice <- data$data[gridpoint_idx, , , validtime_idx]
  
  # Transpose to get members as rows, steps as columns
  df <- as.data.frame(t(data_slice))
  
  # Name columns by step index
  names(df) <- paste0("Step_", 0:40)
  
  # Add member column
  df$Member <- paste0("M", seq_len(nrow(df)))
  
  # Create lead time hours vector (0 to 240 hours in 41 steps)
  lead_times_hours <- seq(0, 240, length.out = 41)
  
  # Pivot to long format and add all necessary columns
  tidy_df <- df %>%
    pivot_longer(
      cols = starts_with("Step_"),
      names_to = "Step_idx",
      values_to = "Forecast_value"
    ) %>%
    mutate(
      Step_idx = as.numeric(gsub("Step_", "", Step_idx)),
      lead_time_hrs = lead_times_hours[Step_idx + 1],  # +1 because R is 1-indexed
      Gridpoint_idx = gridpoint_idx,
      ValidTime_idx = validtime_idx,
      Gridpoint = data$gridpoint[gridpoint_idx],
      Forecast_date = forecast_date  # This is the date from date_lookup_df
    ) %>%
    select(Member, lead_time_hrs, Forecast_date, Forecast_value, 
           Gridpoint, everything())
  
  return(tidy_df)
}


# Example usage and verification
# # Convert specific validtime to tidy format
#dewp_example_day <- tidy_formation(dewp_2021, gridpoint_idx = 1, validtime_idx = 100)
#dewp_example_day
```

##function that we only input forecats_time and gridpoint to generate tidy forecast table
```{r}
# Example: tidy_result_2021_01_31_G605 <- tidy_table_ultimate("2021-01-31", 605)
# Helper function to find runtime index for a given date

# Helper functions
find_runtime_index <- function(data, target_datetime) {
  target_date <- as.Date(target_datetime)
  ref_date <- as.Date(gsub(".*since\\s+([0-9-]+).*", "\\1", data$runtime_units))
  days_since_ref <- as.numeric(target_date - ref_date)
  
  # Find all indices for this date
  date_matches <- which(abs(data$runtime_vals - days_since_ref) < 0.1)
  
  if (length(date_matches) == 0) {
    idx <- which.min(abs(data$runtime_vals - days_since_ref))
    return(idx)
  }
  
  return(date_matches)
}

find_gridpoint_index <- function(data, gridpoint_id) {
  idx <- which(data$gridpoint == gridpoint_id)
  if (length(idx) == 0) {
    stop("Gridpoint ID ", gridpoint_id, " not found")
  }
  return(idx)
}

# New function: Calculate actual forecast time from validTime
calculate_forecast_time_from_validtime <- function(data, runtime_idx) {
  # validTime might be hours since some reference time
  # Need to find the validTime reference point
  ref_datetime <- as.POSIXct(gsub(".*since\\s+([0-9-]+\\s+[0-9:]+).*", "\\1", 
                                  data$runtime_units), tz = "UTC")
  
  # Get runtime value and validTime value for this index
  runtime_days <- data$runtime_vals[runtime_idx]
  validtime_value <- data$validTime[runtime_idx]
  
  # Calculate base date (from runtime_vals)
  base_date <- ref_datetime + (runtime_days * 86400)
  
  # validTime is usually hours since some reference time
  # If validTime is negative or very large, might need different interpretation
  # Here we assume validTime is hours since 1900-01-01 (common meteorological convention)
  validtime_ref <- as.POSIXct("1900-01-01 00:00:00", tz = "UTC")
  actual_time <- validtime_ref + (validtime_value * 3600)
  
  # If calculated time seems unreasonable, try different interpretation
  if (year(actual_time) != year(base_date)) {
    # validTime might be relative to a different reference point
    # Let's check the difference between two validTimes
    return(list(base_date = base_date, validtime = validtime_value, idx = runtime_idx))
  }
  
  return(list(forecast_time = actual_time, idx = runtime_idx))
}
```

#check forecasts that be made in a specific date
```{r}
# Main function!
# Example: tidy_result_2021_08_13_G605 <- tidy_table_ultimate("2021-08-13", 605)
tidy_table_ultimate <- function(forecast_init_time, gridpoint_id, data_dir = here("data", "ToSend-01-20-2025")) {
  
  # Step 1: Extract year
  year <- year(as.Date(forecast_init_time))
  
  # Step 2: Read both datasets
  temp_data <- read_data(year, "2t", data_dir)
  dewp_data <- read_data(year, "2d", data_dir)
  
  # Step 3: Find runtime indices
  runtime_idx_temp <- find_runtime_index(temp_data, forecast_init_time)
  runtime_idx_dewp <- find_runtime_index(dewp_data, forecast_init_time)
  
  # Step 4: Find gridpoint index
  grid_idx <- find_gridpoint_index(temp_data, gridpoint_id)
  
  # Step 5: Process each forecast for this date
  ref_datetime <- as.POSIXct(gsub(".*since\\s+([0-9-]+\\s+[0-9:]+).*", "\\1", 
                                  temp_data$runtime_units), tz = "UTC")
  
  all_day_results <- list()
  
  # Analyze validTime differences to determine forecast times
  if (length(runtime_idx_temp) > 1) {
    validtime_diff <- diff(sort(temp_data$validTime[runtime_idx_temp]))
    
    # Sort by validTime - typically smaller validTime corresponds to 00:00, larger to 12:00
    sorted_idx <- runtime_idx_temp[order(temp_data$validTime[runtime_idx_temp])]
    
    forecast_hours <- c(0, 12)  # Assume 00:00 and 12:00 forecasts
  } else {
    sorted_idx <- runtime_idx_temp
    forecast_hours <- 0
  }
  
  # Process each forecast time
  for (i in 1:length(sorted_idx)) {
    temp_idx <- sorted_idx[i]
    
    # Calculate forecast initialization time
    forecast_init_datetime <- ref_datetime + (temp_data$runtime_vals[temp_idx] * 86400) + 
                             (forecast_hours[i] * 3600)
    
    # Find corresponding dewpoint index
    dewp_idx <- runtime_idx_dewp[i]  # Simplified assumption: sequential correspondence
    
    # Create lead times
    lead_times_hours <- seq(0, 240, length.out = 41)
    
    # Initialize results for this forecast
    results <- list()
    
    # Extract data for each member and step
    for (m in 1:51) {
      for (s in 1:41) {
        # Extract values
        temp_val <- tryCatch({
          temp_data$data[grid_idx[1], s, m, temp_idx]
        }, error = function(e) { NA })
        
        dewp_val <- tryCatch({
          dewp_data$data[grid_idx[1], s, m, dewp_idx]
        }, error = function(e) { NA })
        
        if (length(temp_val) > 1) temp_val <- temp_val[1]
        if (length(dewp_val) > 1) dewp_val <- dewp_val[1]
        
        valid_datetime <- forecast_init_datetime + (lead_times_hours[s] * 3600)
        
        results[[length(results) + 1]] <- data.frame(
          Member = paste0("M", m),
          lead_time_hrs = lead_times_hours[s],
          Forecast_init_datetime = format(forecast_init_datetime, "%Y-%m-%d %H:%M:%S"),
          Valid_datetime = format(valid_datetime, "%Y-%m-%d %H:%M:%S"),
          Forecast_init_date = as.Date(forecast_init_datetime),
          Valid_date = as.Date(valid_datetime),
          Temperature_K = as.numeric(temp_val),
          DewPoint_K = as.numeric(dewp_val),
          Temperature_C = as.numeric(temp_val) - 273.15,
          DewPoint_C = as.numeric(dewp_val) - 273.15,
          Gridpoint_ID = gridpoint_id,
          Runtime_index = temp_idx,
          ValidTime_value = temp_data$validTime[temp_idx],
          stringsAsFactors = FALSE
        )
      }
    }
    
    all_day_results[[length(all_day_results) + 1]] <- bind_rows(results)
  }
  
  # Combine all results
  tidy_combined <- bind_rows(all_day_results)
  
  return(tidy_combined)
}

# Test
tidy_result_2021_08_13_G605 <- tidy_table_ultimate("2021-08-13", 605)
tidy_result_2021_08_13_G605
# Check the results one day two forecast
#unique(tidy_result_2021_08_13_G605[, c("Forecast_init_datetime", "Runtime_index", "ValidTime_value")])
```


##import meta data to find locations(lon and lat) for gridpoints and their corresponding stations
```{r}
#import meta data
prediction_metadata <- read.csv(here("data", "ToSend-01-20-2025", "prediction_meta.csv"))
sta_gp_metadata <- read.csv(here("data", "ToSend-01-20-2025", "sta_gp_metadata.csv"))
sta_gp_metadata <- sta_gp_metadata %>%
  select(-X)

# all grid points appeared in our all_data data set
unique_gridpoints <- c(605, 639, 674, 676, 680, 715, 745, 747, 787, 818, 819, 821, 854, 857, 891, 896, 935, 965, 967, 969, 971, 1001, 1002, 1003, 1041, 1073, 1074, 1080, 1111, 1112, 1114, 1118, 1147, 1148, 1154, 1187, 1193, 1269)

#match them with meta

gridpoint_lookup <- data.frame(
  data_index = 1:length(unique_gridpoints),
  gridpoint = unique_gridpoints
)

# merge
gridpoint_lookup <- merge(gridpoint_lookup, prediction_metadata,
                         by = "gridpoint",
                         all.x = TRUE)%>%select(-data_index)
gridpoint_lookup <- gridpoint_lookup %>%
  left_join(sta_gp_metadata, by = c("gridpoint" = "gp"))%>%
  select(-sta_id,
         gp_lat = gp_lat.x, 
         gp_lon = gp_lon.x, 
         everything(),
         -gp_lat.y, 
         -gp_lon.y)

# one-to-many relationship when joining two datasets where one gridpoint maps to multiple stations, causing duplicate rows in the merged data 
gridpoint_station_table = gridpoint_lookup %>% 
  mutate(
    # determine primary or secondary
    station_type = ifelse(station_id == sta_id, "primary", "secondary")
  )%>%
  mutate(
    is_coast = ifelse(station_type == "secondary", NA, is_coast),
    clc_dist0 = ifelse(station_type == "secondary", NA, clc_dist0),
    dist = ifelse(station_type == "secondary", NA, dist)
  )%>%
  select(-station_id)

gridpoint_station_table

## Verify guess
## There are 38 grid point locations in the data but 46 stations so Kiri guessed that there may be more than one station per grid point - this is worth checking. We will need to follow up about the mapping from grid points to stations. 

station_count <- gridpoint_station_table %>%
  group_by(gridpoint) %>%
  summarise(
    n_stations = sum(!is.na(sta_id)),  
  ) %>%
  arrange(desc(n_stations))  

station_count
length(station_count$gridpoint)
sum(station_count$n_stations)

# only found 43 stations in 38 grid points

# In addition, for some gridpoints like 819 , it has 2 relate stations with different station_id, sta_lat and sta_lon
```

```{r}
tidy_forecast_with_station_grid_location <- function(target_date, gridpoint_id, 
                                      data_dir = here("data", "ToSend-01-20-2025")) {
  # Get forecast data
  forecast_data <- tidy_table_ultimate(target_date, gridpoint_id, data_dir)
  
  # Add station information
  forecast_with_station <- forecast_data %>%
    left_join(
      gridpoint_station_table %>%
        select(gridpoint, sta_id, sta_lat, sta_lon, dist, is_coast, 
               gp_lat, gp_lon, clc_dist0),
      by = c("Gridpoint_ID" = "gridpoint")
    ) %>%
    # Optionally rename columns for clarity
    rename(
      station_id = sta_id,
      station_lat = sta_lat,
      station_lon = sta_lon,
      gridpoint_to_station_dist = dist,
      gridpoint_lat = gp_lat,
      gridpoint_lon = gp_lon
    )
  
  return(forecast_with_station)
}

tidy_result_2021_08_13_G605 <- tidy_forecast_with_station_grid_location("2021-08-13", 605)
tidy_result_2021_08_13_G605
```

```{r}

```



################### ( Visualization starts here :) ######################


## find stations near cities
```{r}
# lon and lat for different cities
cities <- data.frame(
  city = c("Amsterdam", "Rotterdam", "Utrecht", "The Hague", "Eindhoven", 
           "Groningen", "Tilburg", "Almere", "Breda", "Nijmegen",
           "Haarlem", "Arnhem", "Zaanstad", "Apeldoorn", "Enschede",
           "Amersfoort", "Zwolle", "Dordrecht", "Leiden", "Maastricht",
           "Delft", "Alkmaar", "Leeuwarden", "Middelburg", "Den Helder"),
  city_lat = c(52.37, 51.92, 52.09, 52.08, 51.44,
               53.22, 51.56, 52.37, 51.59, 51.84,
               52.38, 51.98, 52.44, 52.21, 52.22,
               52.16, 52.51, 51.81, 52.16, 50.85,
               52.01, 52.63, 53.20, 51.50, 52.96),
  city_lon = c(4.90, 4.48, 5.12, 4.30, 5.48,
               6.57, 5.08, 5.22, 4.78, 5.87,
               4.64, 5.90, 4.83, 5.97, 6.90,
               5.39, 6.09, 4.67, 4.49, 5.69,
               4.36, 4.75, 5.80, 3.61, 4.76),
  population_rank = c(1, 2, 4, 3, 5,    # population rank
                      6, 7, 8, 9, 10,
                      11, 12, 13, 14, 15,
                      16, 17, 18, 19, 20,
                      21, 22, 23, 24, 25),
  region = c("North Holland", "South Holland", "Utrecht", "South Holland", "North Brabant",
             "Groningen", "North Brabant", "Flevoland", "North Brabant", "Gelderland",
             "North Holland", "Gelderland", "North Holland", "Gelderland", "Overijssel",
             "Utrecht", "Overijssel", "South Holland", "South Holland", "Limburg",
             "South Holland", "North Holland", "Friesland", "Zeeland", "North Holland")
)

# Find nearest station for each city
city_connections <- cities %>%
 rowwise() %>%
 mutate(
   # Calculate distances to all stations
   distances = list(sqrt((gridpoint_station_table$sta_lat - city_lat)^2 + 
                        (gridpoint_station_table$sta_lon - city_lon)^2) * 111),
   nearest_idx = which.min(distances),
   station_lat = gridpoint_station_table$sta_lat[nearest_idx],
   station_lon = gridpoint_station_table$sta_lon[nearest_idx],
   distance_km = round(min(distances), 1)
 )

# Create simple connection map
city_station_plot = ggplot() +
  # Connection lines
  geom_segment(data = city_connections,
               aes(x = city_lon, y = city_lat, xend = station_lon, yend = station_lat),
               alpha = 0.3) +
  
  # Primary Stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "primary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "red", size = 2) +
  
  # Secondary Stations (yellow.samll size)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "gold", size = 1) +
 
 # Cities
 geom_point(data = cities,
            aes(x = city_lon, y = city_lat, size = 1/population_rank), color = "blue" ) +
 
 # Labels for major cities only
 geom_text_repel(data = cities ,
                 aes(x = city_lon, y = city_lat, label = city),
                 size = 3) +
  
 geom_text_repel(data = gridpoint_station_table ,
                 aes(x = sta_lon, y = sta_lat, label = sta_id),
                 size = 2) +
  
 labs(title = "Cities and Nearest Weather Stations",
     subtitle = "City points size is determinted by its population rank",
     x = "Longitude", y = "Latitude")+
 theme_minimal() +
 coord_fixed(1.3)+
 scale_size_continuous(guide = FALSE)

city_station_plot

ggsave(
  filename = "Cities and Nearest Weather Stations.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

```

## find stations near grid points,for some gridpoints like 819 , it has 2 relate stations but same station_id different sta_lat and sta_lon
```{r}
# Create visualization
#netherlands <- ne_countries(country = "netherlands", returnclass = "sf", scale = "medium")

gridpoint_station_map <- ggplot() +
  #geom_sf(data = netherlands, fill = NA, color = "black", size = 0.8) +
  # Connection lines
  geom_segment(data = gridpoint_station_table,
               aes(x = gp_lon, y = gp_lat, xend = sta_lon, yend = sta_lat),
               alpha = 0.3) +
  # Plot gridpoint points (using squares)
  geom_point(data = gridpoint_station_table,
             aes(x = gp_lon, y = gp_lat, shape = "Gridpoints"),
             color = "darkblue") +
  
  # Plot primary stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "primary"),
             aes(x = sta_lon, y = sta_lat, shape = "Primary Stations"),
             color = "red") +
  
  # Plot secondary stations (yellow)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat, shape = "Secondary Stations"),
             color = "gold") +
  
  # Set shapes
  scale_shape_manual(values = c("Gridpoints" = 15, 
                               "Primary Stations" = 16,
                               "Secondary Stations" = 17),
                     name = "Type") +
  
  # Add gridpoint labels
  geom_text_repel(data = gridpoint_station_table,
                  aes(x = gp_lon, y = gp_lat, label = gridpoint),
                  size = 2.5,
                  color = "darkblue",
                  box.padding = 0.3,
                  point.padding = 0.2,
                  max.overlaps = 20) +
  
  # Add primary station labels (red)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "primary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "red",
                  nudge_y = 0.02,
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  # Add secondary station labels (yellow)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "secondary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "gold",
                  nudge_y = -0.02,  #avoid overlapping
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  labs(title = "ECMWF Gridpoints and KNMI Stations in the Netherlands",
       subtitle = "Primary stations (red) vs Secondary stations (yellow)",
       x = "Longitude",
       y = "Latitude") +
  
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

gridpoint_station_map

ggsave(
  filename = "ECMWF Gridpoints and KNMI Stations in the Netherlands.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

# every station is super close to its corresponding grid points
```
```{r}
#automate plot function using gridpoint_id date and members to plot temperature
auto_forecast_plot_faceted <- function(date, grid_point, members, 
                                      variable = "Temperature_C",
                                      data_dir = here("data", "ToSend-01-20-2025")) {
  
  # Get the tidy data
  tidy_data <- tidy_table_ultimate(date, grid_point, data_dir)
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names) %>%
    mutate(Forecast_time = format(as.POSIXct(Forecast_init_datetime), "%H:%M"))
  
  # Create base plot
  p <- ggplot(plot_data, aes(x = lead_time_hrs, y = .data[[variable]], group = Member))
  
  # Check number of members
  n_members <- length(members)
  
  if (n_members <= 10) {
    p <- p + geom_line(aes(color = Member), size = 1.2, alpha = 0.8) +
         scale_color_manual(values = c("red", "blue", "green", "purple", "orange", 
                                      "brown", "pink", "yellow", "cyan", "magenta")[1:n_members])
  } else {
    p <- p + geom_line(alpha = 0.6, color = "gray")
  }
  
  # Add faceting
  p <- p +
    facet_wrap(~ Forecast_time, ncol = 1) +
    labs(
      title = paste("Forecast for", date, "at Gridpoint", grid_point),
      subtitle = paste(n_members, "ensemble members"),
      x = "Lead Time (hours)",
      y = ifelse(variable == "Temperature_C", "Temperature (°C)", 
                 ifelse(variable == "DewPoint_C", "Dew Point (°C)", variable))
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      legend.position = if(n_members <= 10) "right" else "none"
    ) +
    scale_x_continuous(breaks = seq(0, 240, 24)) +
    coord_cartesian(xlim = c(0, 240))
  
  return(p)
}

# Usage:
p_faceted <- auto_forecast_plot_faceted("2021-01-31", 605, members = 1:51)
p_faceted

```

# plot with pdf to be more clear to view the distribution
```{r}
auto_forecast_plot_with_pdf_separate <- function(date, grid_point, members = 1:51, 
                                                variable = "Temperature_C",
                                                pdf_times = c(24, 48, 120, 240),
                                                forecast_hour = 0,  # 0 or 12
                                                data_dir = here("data", "ToSend-01-20-2025")) {
  
  tidy_data <- tidy_table_ultimate(date, grid_point, data_dir) %>%
    filter(Member %in% paste0("M", members),
           Forecast_init_datetime == paste0(date, " ", sprintf("%02d:00:00", forecast_hour)))
  
  n_members <- length(members)
  
  # Main plot
  p_main <- ggplot(tidy_data, aes(x = lead_time_hrs, y = .data[[variable]], group = Member)) +
    geom_line(alpha = 0.6, color = if(n_members <= 10) "auto" else "gray") +
    geom_vline(xintercept = pdf_times, linetype = "dashed", alpha = 0.5) +
    labs(title = paste("Forecast:", date, forecast_hour, ":00 UTC"), 
         x = "Lead Time (hours)", 
         y = variable) +
    theme_minimal() +
    scale_x_continuous(breaks = seq(0, 240, 24))
  
  if (n_members <= 10) p_main <- p_main + aes(color = Member)
  
  # Create a 2x2 grid of PDF plots
  pdf_plots <- lapply(pdf_times, function(t) {
    pdf_data <- filter(tidy_data, abs(lead_time_hrs - t) < 0.1)
    
    ggplot(pdf_data, aes(x = .data[[variable]])) +
      geom_histogram(aes(y = ..density..), bins = 20, fill = "lightblue", 
                    color = "darkblue", alpha = 0.7) +
      geom_density(color = "darkblue", size = 1.2) +
      geom_vline(xintercept = mean(pdf_data[[variable]]), 
                color = "red", linetype = "dashed", size = 1) +
      labs(title = paste0(t, " hours ahead"), 
           x = variable, 
           y = "Density") +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 12, face = "bold"),
        axis.title = element_text(size = 10),
        plot.margin = margin(10, 10, 10, 10)
      )
  })
  
  # Arrange PDFs in a grid below the main plot
  pdf_grid <- wrap_plots(pdf_plots, ncol = 2, nrow = 2)
  
  # Stack main plot and PDF grid
  p_main / pdf_grid + plot_layout(heights = c(2, 3))
}

# Usage:
# Single time with grid PDFs below
p2 <- auto_forecast_plot_with_pdf_separate("2021-01-31", 605, members = 1:50, forecast_hour = 12)#12 OR 0

p2
```

