
```{r}
#install.packages("here")
library(here)
#install.packages("ggplot2")
library(ggplot2)
#install.packages("reshape2")
library(reshape2)
#install.packages("viridis")
library(viridis)
#install.packages("dplyr")
library(dplyr)
#install.packages("purrr")
library(purrr)
#install.packages("tidyr")
library(tidyr)
#install.packages("compiler")
library(compiler)
#install.packages("quantreg")
library(quantreg)
#install.packages("randomForest")
library(randomForest)
#install.packages("lubridate")
library(lubridate) 
#install.packages("rnaturalearth")
library(rnaturalearth)
#install.packages("rnaturalearthdata")
library(rnaturalearthdata)
#install.packages("pROC")
library(pROC)
#install.packages("isodistrreg")
library(isodistrreg)
#install.packages("kableExtra")
library(kableExtra)
```

#load_data for further research
```{r}
# Set file path
# data_path <- here("data_clean")
# 
# # Get all RDS files in the directory
# files <- list.files(data_path, pattern = "\\.rds$", full.names = TRUE)
# print(paste("Found", length(files), "files"))
# 
# # Read files separately for each gridpoint
# files_G891 <- files[grepl("G891", files)]
# files_G1002 <- files[grepl("G1002", files)]
# 
# safe_read_combine <- function(file_list, grid_id, city_name) {
#   data_list <- list()
# 
#   # Track which files have which columns
#   file_column_summary <- list()
# 
#   # First pass: read all files and identify all unique columns
#   all_columns <- c()
# 
#   for(i in seq_along(file_list)) {
#     file <- file_list[i]
#     filename <- tools::file_path_sans_ext(basename(file))
# 
#     tryCatch({
#       data <- readRDS(file)
#       all_columns <- unique(c(all_columns, names(data)))
# 
#       # Track which columns this file has
#       file_column_summary[[filename]] <- names(data)
# 
#       print(paste("File", filename, "has", ncol(data), "columns"))
#     }, error = function(e) {
#       print(paste("Error reading", file, ":", e$message))
#     })
#   }
# 
#   print(paste("Total unique columns across all files:", length(all_columns)))
# 
#   # Check specifically for WOW columns across files
#   wow_cols <- c("wow_temp_max", "wow_wbgt_max", "wow_temp_mean", "wow_wbgt_mean")
#   print("\n=== WOW Column Availability by File ===")
#   for(filename in names(file_column_summary)) {
#     file_cols <- file_column_summary[[filename]]
#     has_wow <- wow_cols[wow_cols %in% file_cols]
#     missing_wow <- wow_cols[!wow_cols %in% file_cols]
#     if(length(missing_wow) > 0) {
#       print(sprintf("%s: MISSING %s", filename, paste(missing_wow, collapse=", ")))
#     }
#   }
# 
#   # Second pass: read and standardize all files
#   for(i in seq_along(file_list)) {
#     file <- file_list[i]
#     filename <- tools::file_path_sans_ext(basename(file))
#     parts <- strsplit(filename, "_")[[1]]
# 
#     tryCatch({
#       data <- readRDS(file)
# 
#       # Before adding missing columns, check current state
#       orig_ncol <- ncol(data)
# 
#       # Add missing columns with NA
#       missing_cols <- setdiff(all_columns, names(data))
#       if(length(missing_cols) > 0) {
#         print(paste("Adding", length(missing_cols), "missing columns to", filename))
#         for(col in missing_cols) {
#           data[[col]] <- NA
#         }
#       }
# 
#       # Verify columns were added
#       if(ncol(data) != length(all_columns)) {
#         print(sprintf("WARNING: Column mismatch for %s. Expected %d, got %d",
#                      filename, length(all_columns), ncol(data)))
#       }
# 
#       # Convert station ID columns to character
#       col_names <- names(data)
#       station_id_cols <- col_names[grepl("station.*id|ExternalSiteId", col_names, ignore.case = TRUE)]
#       for(col in station_id_cols) {
#         if(col %in% names(data)) {
#           data[[col]] <- as.character(data[[col]])
#         }
#       }
# 
#       # Add metadata
#       data$season <- parts[1]
#       data$year <- as.numeric(parts[2])
#       data$gridpoint <- grid_id
#       data$city <- city_name
#       data$leadtime <- paste(parts[4:length(parts)], collapse = "_")
# 
#       # Store with all columns present
#       data_list[[i]] <- data
# 
#       print(sprintf("Loaded %s: %d -> %d columns", filename, orig_ncol, ncol(data)))
# 
#     }, error = function(e) {
#       print(paste("Error reading", file, ":", e$message))
#     })
#   }
# 
#   # Before combining, check what we have
#   print("\n=== Pre-combination check ===")
#   for(i in seq_along(data_list)) {
#     if(!is.null(data_list[[i]])) {
#       wow_present <- wow_cols[wow_cols %in% names(data_list[[i]])]
#       print(sprintf("Data frame %d has %d columns, %d WOW columns",
#                    i, ncol(data_list[[i]]), length(wow_present)))
#     }
#   }
# 
#   # Combine all data
#   if(length(data_list) > 0) {
#     # Remove NULL entries
#     data_list <- data_list[!sapply(data_list, is.null)]
# 
#     combined <- bind_rows(data_list)
# 
#     print(sprintf("\n=== After combination: %d rows, %d columns ===",
#                  nrow(combined), ncol(combined)))
# 
#     # Check WOW columns in combined data
#     wow_in_combined <- wow_cols[wow_cols %in% names(combined)]
#     print(sprintf("WOW columns in combined data: %s",
#                  paste(wow_in_combined, collapse=", ")))
# 
#     # Summary of missing data
#     for(col in wow_cols) {
#       if(col %in% names(combined)) {
#         na_count <- sum(is.na(combined[[col]]))
#         total <- nrow(combined)
#         non_na <- total - na_count
#         print(sprintf("%s: %d non-NA values (%.1f%% missing)",
#                      col, non_na, 100*na_count/total))
#       } else {
#         print(sprintf("%s: COLUMN NOT FOUND IN COMBINED DATA!", col))
#       }
#     }
# 
#     return(combined)
#   } else {
#     return(NULL)
#   }
# }
# 
# # Run with detailed diagnostics
# data_amsterdam <- safe_read_combine(files_G891, "G891", "Amsterdam")
# 
# # Final check
# print("\n=== FINAL CHECK ===")
# print(sprintf("Amsterdam data: %d rows, %d columns",
#              nrow(data_amsterdam), ncol(data_amsterdam)))
# wow_cols_final <- names(data_amsterdam)[grepl("wow", names(data_amsterdam), ignore.case = TRUE)]
# print(sprintf("WOW columns in final data: %s", paste(wow_cols_final, collapse=", ")))
# 
# # Apply the function
# data_amsterdam <- safe_read_combine(files_G891, "G891", "Amsterdam")
# data_rotterdam <- safe_read_combine(files_G1002, "G1002", "Rotterdam")
# 
# # Check what columns we have
# print("Amsterdam columns with WOW:")
# print(names(data_amsterdam)[grepl("wow", names(data_amsterdam), ignore.case = TRUE)])
# 
# print("Rotterdam columns with WOW:")
# print(names(data_rotterdam)[grepl("wow", names(data_rotterdam), ignore.case = TRUE)])
# 
# 
# # Fixed version that preserves all columns
# process_knmi_observations <- function(data) {
#   print(paste("Processing KNMI observations for", unique(data$city), "..."))
#   print(paste("Original data rows:", nrow(data)))
#   print(paste("Original columns:", ncol(data)))
# 
#   # Check unique LOCATION values
#   unique_locations <- unique(data$LOCATION)
#   print(paste("Found", length(unique_locations), "unique LOCATION values:",
#               paste(unique_locations, collapse = ", ")))
# 
#   # Group by Member and lead_time_hrs, then take maximum of KNMI observations
#   data_processed <- data %>%
#     group_by(Member, lead_time_hrs, Valid_datetime, Forecast_init_datetime) %>%
#     mutate(
#       # Take maximum values for all KNMI observation columns
#       T_DRYB_10 = mean(T_DRYB_10, na.rm = TRUE),
#       T_DEWP_10 = mean(T_DEWP_10, na.rm = TRUE),
#       T_WETB_10 = mean(T_WETB_10, na.rm = TRUE),
#       TX_DRYB_10 = mean(TX_DRYB_10, na.rm = TRUE),
#       RH_10 = mean(RH_10, na.rm = TRUE),
#       WBGT_obs_10 = mean(WBGT_obs_10, na.rm = TRUE),
#       U_10 = mean(U_10, na.rm = TRUE),
# 
#       # Count how many sensor locations contributed to this maximum
#       n_locations = n_distinct(LOCATION, na.rm = TRUE),
#       locations_included = paste(unique(LOCATION), collapse = "; ")
#     ) %>%
#     ungroup() %>%
#     # Remove duplicate rows but KEEP ALL COLUMNS using .keep_all = TRUE
#     distinct(Member, lead_time_hrs, Valid_datetime, .keep_all = TRUE)
# 
#   # Replace -Inf with NA (in case all values were NA for max())
#   knmi_cols <- c("T_DRYB_10", "T_DEWP_10", "T_WETB_10", "TX_DRYB_10",
#                  "RH_10", "WBGT_obs_10", "U_10")
# 
#   for(col in knmi_cols) {
#     if(col %in% names(data_processed)) {
#       inf_count <- sum(is.infinite(data_processed[[col]]), na.rm = TRUE)
#       if(inf_count > 0) {
#         print(paste("Warning:", inf_count, "infinite values found in", col))
#         data_processed[[col]][is.infinite(data_processed[[col]])] <- NA
#       }
#     }
#   }
# 
#   print(paste("Processed data rows:", nrow(data_processed)))
#   print(paste("Processed data columns:", ncol(data_processed)))
#   print(paste("Data reduction:",
#               sprintf("%.1f%%", (1 - nrow(data_processed)/nrow(data)) * 100)))
# 
#   # Verify all WOW columns are preserved
#   original_wow_cols <- names(data)[grepl("^wow_", names(data))]
#   processed_wow_cols <- names(data_processed)[grepl("^wow_", names(data_processed))]
# 
#   if(length(original_wow_cols) != length(processed_wow_cols)) {
#     print("\nWarning: Some WOW columns may have been lost!")
#     print(paste("Original WOW columns:", length(original_wow_cols)))
#     print(paste("Processed WOW columns:", length(processed_wow_cols)))
#     lost_wow <- setdiff(original_wow_cols, processed_wow_cols)
#     if(length(lost_wow) > 0) {
#       print("Lost WOW columns:")
#       print(lost_wow)
#     }
#   } else {
#     print(paste("\nAll", length(original_wow_cols), "WOW columns preserved successfully!"))
#   }
# 
#   # Summary statistics for verification
#   print("\n=== KNMI Maximum Values Summary ===")
#   print(paste("Temperature (T_DRYB_10) range:",
#               sprintf("%.1f to %.1f°C",
#                       min(data_processed$T_DRYB_10, na.rm = TRUE),
#                       max(data_processed$T_DRYB_10, na.rm = TRUE))))
#   print(paste("WBGT (WBGT_obs_10) range:",
#               sprintf("%.1f to %.1f°C",
#                       min(data_processed$WBGT_obs_10, na.rm = TRUE),
#                       max(data_processed$WBGT_obs_10, na.rm = TRUE))))
#   print(paste("Average locations per observation:",
#               sprintf("%.1f", mean(data_processed$n_locations, na.rm = TRUE))))
# 
#   return(data_processed)
# }
# 
# # Apply the corrected processing
# data_amsterdam <- process_knmi_observations(data_amsterdam)
# data_rotterdam <- process_knmi_observations(data_rotterdam)
# 
# 
# 
# # === SAVE PROCESSED DATA ===
# #
# # Save Amsterdam data
# amsterdam_file <- file.path(data_path, "data_amsterdam_processed.rds")
# saveRDS(data_amsterdam, amsterdam_file)
# print(paste("Saved Amsterdam data to:", amsterdam_file))
# print(paste("File size:", round(file.size(amsterdam_file) / 1024^2, 1), "MB"))
# 
# # Save Rotterdam data
# rotterdam_file <- file.path(data_path, "data_rotterdam_processed.rds")
# saveRDS(data_rotterdam, rotterdam_file)
# print(paste("Saved Rotterdam data to:", rotterdam_file))
# print(paste("File size:", round(file.size(rotterdam_file) / 1024^2, 1), "MB"))

# Load data
data_amsterdam <- readRDS(here("data_clean", "data_amsterdam_processed.rds"))
print(paste("Loaded Amsterdam data:", nrow(data_amsterdam), "rows,", ncol(data_amsterdam), "columns"))

data_rotterdam <- readRDS(here("data_clean", "data_rotterdam_processed.rds"))
print(paste("Loaded Rotterdam data:", nrow(data_rotterdam), "rows,", ncol(data_rotterdam), "columns"))

```
# Data Quality Distribution Analysis


```{r}
# Enhanced Data Quality Distribution Analysis with multiple variables
analyze_wow_knmi_agreement_enhanced <- function(data_amsterdam, data_rotterdam) {
  
  # 1. Combine data and prepare for analysis
  agreement_analysis <- bind_rows(
    data_amsterdam %>% mutate(city = "Amsterdam"),
    data_rotterdam %>% mutate(city = "Rotterdam")
  ) %>%
    filter(!is.na(wow_temp_mean) & !is.na(T_DRYB_10) & 
           !is.na(wow_dewpoint_mean) & !is.na(T_DEWP_10) &
           !is.na(wow_wbgt_mean) & !is.na(WBGT_obs_10)) %>%
    mutate(
      # Temperature bias
      temp_bias = wow_temp_mean - T_DRYB_10,
      temp_abs_dev = abs(temp_bias),
      
      # Dewpoint bias
      dewpoint_bias = wow_dewpoint_mean - T_DEWP_10,
      dewpoint_abs_dev = abs(dewpoint_bias),
      
      # WBGT bias
      wbgt_bias = wow_wbgt_mean - WBGT_obs_10,
      wbgt_abs_dev = abs(wbgt_bias),
      
      # Categorize deviations for temperature
      temp_category = case_when(
        temp_abs_dev < 1 ~ "Excellent (<1°C)",
        temp_abs_dev < 2 ~ "Good (1-2°C)",
        temp_abs_dev < 3 ~ "Acceptable (2-3°C)",
        temp_abs_dev < 5 ~ "Poor (3-5°C)",
        TRUE ~ "Very Poor (>5°C)"
      )
    )
  
  # 2. Summary statistics for all variables
  summary_stats <- agreement_analysis %>%
    group_by(city, season, leadtime) %>%
    summarise(
      n = n(),
      # Temperature
      temp_mean_bias = mean(temp_bias, na.rm = TRUE),
      temp_sd_bias = sd(temp_bias, na.rm = TRUE),
      temp_rmse = sqrt(mean(temp_bias^2, na.rm = TRUE)),
      temp_mae = mean(temp_abs_dev, na.rm = TRUE),
      temp_corr = cor(wow_temp_mean, T_DRYB_10, use = "complete.obs"),
      
      # Dewpoint
      dewpoint_mean_bias = mean(dewpoint_bias, na.rm = TRUE),
      dewpoint_rmse = sqrt(mean(dewpoint_bias^2, na.rm = TRUE)),
      dewpoint_mae = mean(dewpoint_abs_dev, na.rm = TRUE),
      dewpoint_corr = cor(wow_dewpoint_mean, T_DEWP_10, use = "complete.obs"),
      
      # WBGT
      wbgt_mean_bias = mean(wbgt_bias, na.rm = TRUE),
      wbgt_rmse = sqrt(mean(wbgt_bias^2, na.rm = TRUE)),
      wbgt_mae = mean(wbgt_abs_dev, na.rm = TRUE),
      wbgt_corr = cor(wow_wbgt_mean, WBGT_obs_10, use = "complete.obs"),
      
      .groups = 'drop'
    )
  
  # 3. Multi-panel bias distribution plot
  bias_long <- agreement_analysis %>%
    select(city, season, temp_bias, dewpoint_bias, wbgt_bias) %>%
    pivot_longer(cols = c(temp_bias, dewpoint_bias, wbgt_bias),
                 names_to = "variable",
                 values_to = "bias") %>%
    mutate(variable = case_when(
      variable == "temp_bias" ~ "Temperature",
      variable == "dewpoint_bias" ~ "Dew Point",
      variable == "wbgt_bias" ~ "WBGT"
    ))
  
  p1 <- ggplot(bias_long, aes(x = bias, fill = season)) +
    geom_histogram(bins = 50, alpha = 0.6, position = "identity") +
    facet_grid(variable ~ city, scales = "free_y") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
    xlim(-10, 5) +  # 设置x轴范围
    labs(title = "WOW-KNMI Bias Distribution: Temperature, Dew Point, and WBGT",
         x = "Bias (WOW - KNMI) [°C]",
         y = "Count") +
    theme_minimal() +
    theme(strip.text = element_text(size = 10, face = "bold"))
  
  # 4. FIXED Correlation plot - removed coord_equal() due to free scales
  p2 <- agreement_analysis %>%
    ggplot(aes(x = T_DRYB_10, y = wow_temp_mean)) +
    geom_hex(bins = 30) +
    geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
    facet_grid(city ~ season) +
    scale_fill_gradient(low = "lightblue", high = "darkblue", trans = "log10") +
    labs(title = "WOW vs KNMI: Temperature Correlation",
         x = "KNMI Temperature [°C]",
         y = "WOW Temperature [°C]") +
    theme_minimal()
  
  # Additional correlation plots for dewpoint and WBGT
  p2_dewpoint <- agreement_analysis %>%
    ggplot(aes(x = T_DEWP_10, y = wow_dewpoint_mean)) +
    geom_hex(bins = 30) +
    geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
    facet_grid(city ~ season) +
    scale_fill_gradient(low = "lightgreen", high = "darkgreen", trans = "log10") +
    labs(title = "WOW vs KNMI: Dew Point Correlation",
         x = "KNMI Dew Point [°C]",
         y = "WOW Dew Point [°C]") +
    theme_minimal()
  
  p2_wbgt <- agreement_analysis %>%
    ggplot(aes(x = WBGT_obs_10, y = wow_wbgt_mean)) +
    geom_hex(bins = 30) +
    geom_abline(intercept = 0, slope = 1, color = "red", linetype = "dashed") +
    facet_grid(city ~ season) +
    scale_fill_gradient(low = "lightyellow", high = "darkorange", trans = "log10") +
    labs(title = "WOW vs KNMI: WBGT Correlation",
         x = "KNMI WBGT [°C]",
         y = "WOW WBGT [°C]") +
    theme_minimal()
  
  # 5. Seasonal summary - fixed the names_sep issue
  seasonal_summary <- summary_stats %>%
    group_by(city, season) %>%
    summarise(
      temp_bias = mean(temp_mean_bias, na.rm = TRUE),
      temp_mae = mean(temp_mae, na.rm = TRUE),
      temp_corr = mean(temp_corr, na.rm = TRUE),
      dewpoint_bias = mean(dewpoint_mean_bias, na.rm = TRUE),
      dewpoint_mae = mean(dewpoint_mae, na.rm = TRUE),
      dewpoint_corr = mean(dewpoint_corr, na.rm = TRUE),
      wbgt_bias = mean(wbgt_mean_bias, na.rm = TRUE),
      wbgt_mae = mean(wbgt_mae, na.rm = TRUE),
      wbgt_corr = mean(wbgt_corr, na.rm = TRUE),
      .groups = 'drop'
    )
  
  # 6. Box plot comparison
  p3 <- bias_long %>%
    ggplot(aes(x = season, y = bias, fill = variable)) +
    geom_boxplot(alpha = 0.7) +
    facet_wrap(~city) +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
    labs(title = "Seasonal Bias Comparison",
         x = "Season",
         y = "Bias [°C]",
         fill = "Variable") +
    theme_minimal() +
    scale_fill_brewer(palette = "Set2")
  
  return(list(
    summary = summary_stats,
    seasonal = seasonal_summary,
    plots = list(
      bias_hist = p1, 
      temp_corr = p2,
      dewpoint_corr = p2_dewpoint,
      wbgt_corr = p2_wbgt,
      box_plot = p3
    ),
    detailed = agreement_analysis
  ))
}

# Run enhanced analysis
enhanced_analysis <- analyze_wow_knmi_agreement_enhanced(data_amsterdam, data_rotterdam)

# Print comprehensive summary
print("Overall Summary Statistics:")
print(enhanced_analysis$summary)

print("\nSeasonal Comparison:")
print(enhanced_analysis$seasonal)

# Display plots
print(enhanced_analysis$plots$bias_hist)
print(enhanced_analysis$plots$temp_corr)
print(enhanced_analysis$plots$dewpoint_corr)
print(enhanced_analysis$plots$wbgt_corr)
print(enhanced_analysis$plots$box_plot)

# Create a summary table for the paper
summary_for_paper <- enhanced_analysis$seasonal %>%
  mutate(
    Temperature = sprintf("%.2f (%.3f)", temp_bias, temp_corr),
    `Dew Point` = sprintf("%.2f (%.3f)", dewpoint_bias, dewpoint_corr),
    WBGT = sprintf("%.2f (%.3f)", wbgt_bias, wbgt_corr)
  ) %>%
  select(city, season, Temperature, `Dew Point`, WBGT)

print("\nFormatted for Paper (Bias in °C, Correlation in parentheses):")
print(summary_for_paper)
```

########## test WOW and obs temp, humidity and wetbulb

#CRPS score isodistrreg and Brier score

```{r}
# Function to compare CRPS between cities using different observation sources
# Evaluates ensemble forecast performance for Temperature and WBGT
compare_cities_crps <- function(data_list,      # List of dataframes for each city
                                city_names,      # Vector of city names
                                lead_time = 24,  # Forecast lead time in hours
                                n_times = Inf,   # Maximum number of time points to process
                                thresholds = c(27)) {  # WBGT thresholds for Brier Score
  
  # Load required libraries
  library(isodistrreg)  # For CRPS and Brier Score calculations
  library(dplyr)        # Data manipulation
  library(ggplot2)      # Plotting
  library(tidyr)        # Data reshaping
  library(patchwork)    # Combining plots
  library(knitr)        # Table formatting
  library(kableExtra)   # Enhanced tables
  
  # Initialize storage lists for results
  all_crps_results <- list()
  all_brier_results <- list()
  
  # Process each city separately
  for(city_idx in 1:length(data_list)) {
    data <- data_list[[city_idx]]
    city_name <- city_names[city_idx]
    
    # Filter data for specified lead time
    data_lt <- data %>%
      filter(lead_time_hrs == lead_time)
    
    # Get unique forecast valid times
    unique_times <- unique(data_lt$Valid_datetime)
    n_calc <- min(n_times, length(unique_times))
    
    cat(sprintf("\nProcessing %s: %d time points...\n", city_name, n_calc))
    
    # Initialize city-specific storage
    crps_results_list <- list()
    brier_results_list <- list()
    valid_count <- 0
    
    # Loop through each time point
    for(i in 1:n_calc) {
      vtime <- unique_times[i]
      
      # Get ensemble data for this time
      time_data <- data_lt %>%
        filter(Valid_datetime == vtime)
      
      # Skip if insufficient ensemble members
      if(nrow(time_data) < 10) next
      
      # Create ensemble matrices (members as columns)
      ens_temp_df <- data.frame(t(time_data$Temperature_C))
      colnames(ens_temp_df) <- paste0("M", 1:ncol(ens_temp_df))
      
      ens_wbgt_df <- data.frame(t(time_data$WBGT_C))
      colnames(ens_wbgt_df) <- paste0("M", 1:ncol(ens_wbgt_df))
      
      # Extract observations - CORRECTED to use WOW max values
      # KNMI: 10-minute averages from official stations
      obs_temp_knmi <- time_data$T_DRYB_10[!is.na(time_data$T_DRYB_10)][1]
      obs_wbgt_knmi <- time_data$WBGT_obs_10[!is.na(time_data$WBGT_obs_10)][1]
      
      # WOW: Hourly maximum values from crowd-sourced stations
      obs_temp_wow_max <- time_data$wow_temp_max[!is.na(time_data$wow_temp_max)][1]
      obs_wbgt_wow_max <- time_data$wow_wbgt_max[!is.na(time_data$wow_wbgt_max)][1]
      
      # Check if any observations are available
      has_any_obs <- !is.na(obs_temp_knmi) || !is.na(obs_temp_wow_max) || 
                     !is.na(obs_wbgt_knmi) || !is.na(obs_wbgt_wow_max)
      
      if(!has_any_obs) next
      
      valid_count <- valid_count + 1
      
      # Initialize CRPS results dataframe
      crps_results <- data.frame(
        city = city_name,
        time = vtime,
        season = time_data$season[1]
      )
      
      # Calculate Temperature CRPS for KNMI observations
      if(!is.na(obs_temp_knmi)) {
        crps_results$crps_temp_knmi <- as.numeric(
          isodistrreg::crps(predictions = ens_temp_df, y = obs_temp_knmi)
        )
      } else {
        crps_results$crps_temp_knmi <- NA
      }
      
      # Calculate Temperature CRPS for WOW max observations
      if(!is.na(obs_temp_wow_max)) {
        crps_results$crps_temp_wow_max <- as.numeric(
          isodistrreg::crps(predictions = ens_temp_df, y = obs_temp_wow_max)
        )
      } else {
        crps_results$crps_temp_wow_max <- NA
      }
      
      # Calculate WBGT CRPS for KNMI observations
      if(!is.na(obs_wbgt_knmi)) {
        crps_results$crps_wbgt_knmi <- as.numeric(
          isodistrreg::crps(predictions = ens_wbgt_df, y = obs_wbgt_knmi)
        )
      } else {
        crps_results$crps_wbgt_knmi <- NA
      }
      
      # Calculate WBGT CRPS for WOW max observations
      if(!is.na(obs_wbgt_wow_max)) {
        crps_results$crps_wbgt_wow_max <- as.numeric(
          isodistrreg::crps(predictions = ens_wbgt_df, y = obs_wbgt_wow_max)
        )
      } else {
        crps_results$crps_wbgt_wow_max <- NA
      }
      
      # Store results
      crps_results_list[[valid_count]] <- crps_results
      
      # Calculate Brier Scores for WBGT thresholds
      for(thresh in thresholds) {
        brier_result <- data.frame(
          city = city_name,
          time = vtime,
          season = time_data$season[1],
          threshold = thresh
        )
        
        # Brier Score for KNMI WBGT observations
        if(!is.na(obs_wbgt_knmi)) {
          brier_result$bs_wbgt_knmi <- as.numeric(
            isodistrreg::bscore(predictions = ens_wbgt_df, 
                               thresholds = thresh, 
                               y = obs_wbgt_knmi)
          )
        } else {
          brier_result$bs_wbgt_knmi <- NA
        }
        
        # Brier Score for WOW max WBGT observations
        if(!is.na(obs_wbgt_wow_max)) {
          brier_result$bs_wbgt_wow_max <- as.numeric(
            isodistrreg::bscore(predictions = ens_wbgt_df, 
                               thresholds = thresh, 
                               y = obs_wbgt_wow_max)
          )
        } else {
          brier_result$bs_wbgt_wow_max <- NA
        }
        
        brier_results_list[[paste(valid_count, thresh, sep="_")]] <- brier_result
      }
    }
    
    # Combine city results if any valid data exists
    if(length(crps_results_list) > 0) {
      all_crps_results[[city_idx]] <- bind_rows(crps_results_list)
      all_brier_results[[city_idx]] <- bind_rows(brier_results_list)
    }
  }
  
  # Combine results from all cities
  combined_crps <- bind_rows(all_crps_results)
  combined_brier <- bind_rows(all_brier_results)
  
  # Create seasonal comparison table
  comparison_table <- combined_crps %>%
    group_by(city, season) %>%
    summarise(
      n_obs = n(),
      # Temperature CRPS statistics
      temp_knmi_mean = mean(crps_temp_knmi, na.rm = TRUE),
      temp_knmi_median = median(crps_temp_knmi, na.rm = TRUE),
      temp_wow_max_mean = mean(crps_temp_wow_max, na.rm = TRUE),
      temp_wow_max_median = median(crps_temp_wow_max, na.rm = TRUE),
      # WBGT CRPS statistics
      wbgt_knmi_mean = mean(crps_wbgt_knmi, na.rm = TRUE),
      wbgt_knmi_median = median(crps_wbgt_knmi, na.rm = TRUE),
      wbgt_wow_max_mean = mean(crps_wbgt_wow_max, na.rm = TRUE),
      wbgt_wow_max_median = median(crps_wbgt_wow_max, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    mutate(across(where(is.numeric), ~round(., 3)))
  
  # Create overall statistics table
  overall_table <- combined_crps %>%
    group_by(city) %>%
    summarise(
      n_total = n(),
      n_temp_knmi = sum(!is.na(crps_temp_knmi)),
      n_temp_wow = sum(!is.na(crps_temp_wow_max)),
      n_wbgt_knmi = sum(!is.na(crps_wbgt_knmi)),
      n_wbgt_wow = sum(!is.na(crps_wbgt_wow_max)),
      temp_knmi_mean = mean(crps_temp_knmi, na.rm = TRUE),
      temp_wow_max_mean = mean(crps_temp_wow_max, na.rm = TRUE),
      wbgt_knmi_mean = mean(crps_wbgt_knmi, na.rm = TRUE),
      wbgt_wow_max_mean = mean(crps_wbgt_wow_max, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    mutate(across(where(is.numeric) & !c(n_total, n_temp_knmi, n_temp_wow, 
                                          n_wbgt_knmi, n_wbgt_wow), ~round(., 3)))
  
  # Summarize Brier scores if available
  if(nrow(combined_brier) > 0) {
    brier_table <- combined_brier %>%
      group_by(city, threshold) %>%
      summarise(
        n_obs = n(),
        bs_wbgt_knmi_mean = mean(bs_wbgt_knmi, na.rm = TRUE),
        bs_wbgt_wow_max_mean = mean(bs_wbgt_wow_max, na.rm = TRUE),
        .groups = 'drop'
      ) %>%
      mutate(across(where(is.numeric) & !n_obs, ~round(., 4)))
  }
  
  # Create Temperature CRPS visualization
  plot_temp <- combined_crps %>%
    select(city, season, starts_with("crps_temp")) %>%
    pivot_longer(cols = starts_with("crps_temp"),
                 names_to = "Type",
                 values_to = "CRPS") %>%
    filter(!is.na(CRPS)) %>%
    mutate(Type = case_when(
      Type == "crps_temp_knmi" ~ "KNMI (avg)",
      Type == "crps_temp_wow_max" ~ "WOW (max)",
      TRUE ~ Type
    )) %>%
    ggplot(aes(x = season, y = CRPS, fill = Type)) +
    geom_violin(position = position_dodge(width = 0.9), 
                alpha = 0.6, trim = FALSE) +
    geom_boxplot(position = position_dodge(width = 0.9),
                 width = 0.2, alpha = 0.8,
                 outlier.size = 0.5) +
    facet_wrap(~city, ncol = 2) +
    scale_fill_manual(values = c("KNMI (avg)" = "#2166AC", 
                                  "WOW (max)" = "#92C5DE")) +
    coord_cartesian(ylim = c(0, 6)) +  # Limit y-axis for better visibility
    theme_minimal(base_size = 11) +
    labs(x = "Season", y = "CRPS (°C)", fill = "Data Source") +
    theme(legend.position = "right",
          legend.direction = "vertical",
          strip.text = element_text(face = "bold", size = 12))
  
  # Create WBGT CRPS visualization
  plot_wbgt <- combined_crps %>%
    select(city, season, starts_with("crps_wbgt")) %>%
    pivot_longer(cols = starts_with("crps_wbgt"),
                 names_to = "Type",
                 values_to = "CRPS") %>%
    filter(!is.na(CRPS)) %>%
    mutate(Type = case_when(
      Type == "crps_wbgt_knmi" ~ "KNMI (avg)",
      Type == "crps_wbgt_wow_max" ~ "WOW (max)",
      TRUE ~ Type
    )) %>%
    ggplot(aes(x = season, y = CRPS, fill = Type)) +
    geom_violin(position = position_dodge(width = 0.9), 
                alpha = 0.6, trim = FALSE) +
    geom_boxplot(position = position_dodge(width = 0.9),
                 width = 0.2, alpha = 0.8,
                 outlier.size = 0.5) +
    facet_wrap(~city, ncol = 2) +
    scale_fill_manual(values = c("KNMI (avg)" = "#D6604D", 
                                  "WOW (max)" = "#FDDBC7")) +
    coord_cartesian(ylim = c(0, 12)) +  # Adjusted for WBGT range
    theme_minimal(base_size = 11) +
    labs(x = "Season", y = "CRPS (°C)", fill = "Data Source") +
    theme(legend.position = "right",
          legend.direction = "vertical",
          strip.text = element_text(face = "bold", size = 12))
  
  # Combine plots with patchwork
  combined_plot <- plot_temp / plot_wbgt +
    plot_annotation(
      title = sprintf("CRPS Comparison (Lead time = %d hrs)", lead_time),
      subtitle = "Temperature (top) and WBGT (bottom)",
      theme = theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
                    plot.subtitle = element_text(size = 12, hjust = 0.5))
    )
  
  # Print summary statistics to console
  cat("\n========================================\n")
  cat("CRPS COMPARISON - Overall Statistics\n")
  cat("========================================\n")
  print(overall_table)
  
  cat("\n========================================\n")
  cat("CRPS COMPARISON - By Season\n")
  cat("========================================\n")
  print(comparison_table)
  
  if(exists("brier_table")) {
    cat("\n========================================\n")
    cat(sprintf("BRIER SCORE COMPARISON - Threshold: %s°C\n", 
                paste(thresholds, collapse=", ")))
    cat("========================================\n")
    print(brier_table)
  }
  
  # Display combined plot
  print(combined_plot)
  
  # Return all results as a list
  return(list(
    crps_data = combined_crps,        # Raw CRPS data
    brier_data = combined_brier,      # Raw Brier Score data
    overall_stats = overall_table,    # Overall statistics by city
    seasonal_stats = comparison_table,# Seasonal statistics
    brier_stats = if(exists("brier_table")) brier_table else NULL,
    plot = combined_plot              # Combined visualization
  ))
}

# Execute the analysis for Amsterdam and Rotterdam
results_comparison <- compare_cities_crps(
  data_list = list(data_amsterdam, data_rotterdam),
  city_names = c("Amsterdam", "Rotterdam"),
  lead_time = 24,     # 24-hour ahead forecasts
  n_times = Inf,      # Process all available time points
  thresholds = c(27)  # 27°C WBGT threshold for heat stress
)

# Access individual components
# results_comparison$overall_stats    # Overall statistics
# results_comparison$seasonal_stats   # Seasonal breakdown
#results_comparison$plot             # Visualization
```
#Station Mapping
```{r}
# Function 1: Basic Station Map with Temperature/WBGT Distribution
plot_station_temperature_map <- function(data, 
                                        city_name = NULL,
                                        time_point = NULL, 
                                        variable = "temperature",
                                        include_wow = TRUE) {
  
  # Select time point
  if(is.null(time_point)) {
    plot_data <- data %>%
      filter(!is.na(WBGT_C)) %>%
      slice(1)
  } else {
    plot_data <- data %>%
      filter(Valid_datetime == time_point)
  }
  
  if(nrow(plot_data) == 0) {
    stop("No data available for the specified time point")
  }
  
  # Auto-detect city name if not provided
  if(is.null(city_name)) {
    city_name <- plot_data$nearest_city[1]
  }
  
  # Get Netherlands map
  netherlands <- ne_countries(scale = "large", country = "Netherlands", returnclass = "sf")
  
  # Initialize stations dataframe
  stations_df <- data.frame()
  
  # Select which variable to plot
  if(variable == "temperature") {
    knmi_value <- plot_data$T_DRYB_10[1]
    grid_value <- plot_data$Temperature_C[1]
    color_label <- "Temperature (°C)"
    midpoint_val <- 15
  } else {
    knmi_value <- plot_data$WBGT_obs_10[1]
    grid_value <- plot_data$WBGT_C[1]
    color_label <- "WBGT (°C)"
    midpoint_val <- 20
  }
  
  # Debug: Print KNMI value
  if(is.na(knmi_value)) {
    cat("Note: KNMI", ifelse(variable == "temperature", "temperature", "WBGT"), 
        "value is NA for station", plot_data$station_id[1], "\n")
  }
  
  # Add city center
  stations_df <- rbind(stations_df, data.frame(
    lon = plot_data$nearest_city_lon[1],
    lat = plot_data$nearest_city_lat[1],
    type = "City Center",
    name = city_name,
    value = NA,
    distance_km = 0,
    data_source = "Reference"
  ))
  
  # Add KNMI station
  if(!is.na(knmi_value)) {
    stations_df <- rbind(stations_df, data.frame(
      lon = plot_data$station_lon[1],
      lat = plot_data$station_lat[1],
      type = "KNMI Station",
      name = paste("KNMI", plot_data$station_id[1]),
      value = knmi_value,
      distance_km = plot_data$nearest_city_distance_km[1],
      data_source = "Official"
    ))
  } else {
    stations_df <- rbind(stations_df, data.frame(
      lon = plot_data$station_lon[1],
      lat = plot_data$station_lat[1],
      type = "KNMI Station",
      name = paste("KNMI", plot_data$station_id[1]),
      value = NA,
      distance_km = plot_data$nearest_city_distance_km[1],
      data_source = "Official"
    ))
  }
  
  # Add gridpoint
  stations_df <- rbind(stations_df, data.frame(
    lon = plot_data$gridpoint_lon[1],
    lat = plot_data$gridpoint_lat[1],
    type = "Model Gridpoint",
    name = paste("Grid", plot_data$Gridpoint_ID[1]),
    value = grid_value,
    distance_km = plot_data$gridpoint_to_station_dist[1],
    data_source = "Model"
  ))
  
  # Add WOW stations if requested and available
  if(include_wow && !is.na(plot_data$wow_data_available[1]) && plot_data$wow_data_available[1] == TRUE) {
    for(i in 1:5) {
      wow_id_col <- paste0("wow_station_", i, "_ExternalSiteId")
      wow_lat_col <- paste0("wow_station_", i, "_Latitude")
      wow_lon_col <- paste0("wow_station_", i, "_Longitude")
      wow_val_col <- if(variable == "temperature") {
        paste0("wow_station_", i, "_station_temp")
      } else {
        paste0("wow_station_", i, "_station_wbgt")
      }
      
      if(wow_id_col %in% names(plot_data) && 
         !is.na(plot_data[[wow_id_col]][1]) && 
         !is.na(plot_data[[wow_val_col]][1])) {
        stations_df <- rbind(stations_df, data.frame(
          lon = plot_data[[wow_lon_col]][1],
          lat = plot_data[[wow_lat_col]][1],
          type = "WOW Station",
          name = paste0("WOW", i),
          value = plot_data[[wow_val_col]][1],
          distance_km = NA,
          data_source = "Citizen"
        ))
      }
    }
  }
  
  # Calculate map bounds
  lon_range <- range(stations_df$lon, na.rm = TRUE)
  lat_range <- range(stations_df$lat, na.rm = TRUE)
  
  # Add buffer
  lon_buffer <- diff(lon_range) * 0.3
  lat_buffer <- diff(lat_range) * 0.3
  
  # Get city center coordinates for connections
  city_center <- stations_df[stations_df$type == "City Center", ]
  
  # Create the plot
  p <- ggplot() +
    # Netherlands background
    geom_sf(data = netherlands, fill = "lightgray", color = "darkgray", alpha = 0.5) +
    coord_sf(xlim = lon_range + c(-lon_buffer, lon_buffer),
             ylim = lat_range + c(-lat_buffer, lat_buffer)) +
    
    # Add connections to city center
    geom_segment(data = stations_df[stations_df$type != "City Center",],
                 aes(x = city_center$lon[1],
                     y = city_center$lat[1],
                     xend = lon, yend = lat),
                 color = "gray70", linetype = "dashed", alpha = 0.3) +
    
    # Add stations
    geom_point(data = stations_df,
               aes(x = lon, y = lat, 
                   color = value, 
                   shape = type, 
                   size = type),
               stroke = 1.5) +
    
    # Add value labels with ggrepel
    ggrepel::geom_text_repel(
      data = stations_df[!is.na(stations_df$value),],
      aes(x = lon, y = lat, 
          label = sprintf("%.1f°C", value)),
      size = 3, 
      fontface = "bold",
      box.padding = 0.5,
      point.padding = 0.3,
      segment.color = 'grey50',
      segment.size = 0.2,
      max.overlaps = Inf,
      seed = 42,  # For reproducible positioning
      nudge_y = 0.01
    ) +
    
    # Add station names with ggrepel
    ggrepel::geom_label_repel(
      data = stations_df,
      aes(x = lon, y = lat, label = name),
      size = 2.5, 
      alpha = 0.9,
      box.padding = 0.35,
      point.padding = 0.3,
      label.padding = 0.15,
      segment.color = 'grey70',
      segment.size = 0.2,
      max.overlaps = Inf,
      seed = 42,
      nudge_y = -0.015,
      fill = "white"
    ) +
    
    # Color scale
    scale_color_gradient2(
      low = "blue", mid = "yellow", high = "red",
      midpoint = midpoint_val,
      name = color_label,
      na.value = "gray50",
      limits = c(min(stations_df$value, na.rm = TRUE) - 2,
                 max(stations_df$value, na.rm = TRUE) + 2)
    ) +
    
    # Shape and size scales
    scale_shape_manual(
      values = c("City Center" = 15, 
                 "KNMI Station" = 17, 
                 "Model Gridpoint" = 16,
                 "WOW Station" = 19),
      name = "Station Type"
    ) +
    scale_size_manual(
      values = c("City Center" = 6, 
                 "KNMI Station" = 5, 
                 "Model Gridpoint" = 4,
                 "WOW Station" = 3.5),
      guide = "none"
    ) +
    
    # Labels and theme
    labs(
      title = sprintf("%s Distribution across %s Weather Stations", 
                     ifelse(variable == "temperature", "Temperature", "WBGT"), 
                     city_name),
      subtitle = sprintf("Time: %s | WOW Coverage: %.0f%% | Quality: %s",
                        format(plot_data$Valid_datetime[1], "%Y-%m-%d %H:%M"),
                        ifelse(is.na(plot_data$wow_coverage[1]), 0, plot_data$wow_coverage[1] * 100),
                        ifelse(is.na(plot_data$wow_data_quality[1]), "N/A", plot_data$wow_data_quality[1])),
      x = "Longitude",
      y = "Latitude",
      caption = "Data sources: KNMI official stations, ECMWF model gridpoints, WOW citizen stations"
    ) +
    theme_minimal() +
    theme(
      legend.position = "right",
      panel.grid.major = element_line(color = "gray90", linewidth = 0.3),
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(size = 10)
    )
  
  return(p)
}

# Function 2: Simple Heat Map without interpolation
plot_temperature_heatmap_simple <- function(data, 
                                           city_name = NULL,
                                           time_point = NULL,
                                           variable = "wbgt") {
  
  # Select time point
  if(is.null(time_point)) {
    plot_data <- data %>%
      filter(!is.na(wow_data_available) & wow_data_available == TRUE) %>%
      slice(1)
  } else {
    plot_data <- data %>%
      filter(Valid_datetime == time_point)
  }
  
  if(nrow(plot_data) == 0) {
    warning("No data with WOW stations available for the specified time point")
    return(NULL)
  }
  
  # Auto-detect city name
  if(is.null(city_name)) {
    city_name <- plot_data$nearest_city[1]
  }
  
  # Collect all station data
  stations_df <- data.frame()
  
  # Select variable
  if(variable == "temperature") {
    knmi_val <- plot_data$T_DRYB_10[1]
    grid_val <- plot_data$Temperature_C[1]
    var_label <- "Temperature (°C)"
  } else {
    knmi_val <- plot_data$WBGT_obs_10[1]
    grid_val <- plot_data$WBGT_C[1]
    var_label <- "WBGT (°C)"
  }
  
  # Add city center
  stations_df <- rbind(stations_df, data.frame(
    lon = plot_data$nearest_city_lon[1],
    lat = plot_data$nearest_city_lat[1],
    value = NA,
    type = "City Center",
    label = city_name
  ))
  
  # Add KNMI station
  stations_df <- rbind(stations_df, data.frame(
    lon = plot_data$station_lon[1],
    lat = plot_data$station_lat[1],
    value = knmi_val,
    type = "KNMI",
    label = plot_data$station_id[1]
  ))
  
  # Add gridpoint
  stations_df <- rbind(stations_df, data.frame(
    lon = plot_data$gridpoint_lon[1],
    lat = plot_data$gridpoint_lat[1],
    value = grid_val,
    type = "Model",
    label = paste("Grid", plot_data$Gridpoint_ID[1])
  ))
  
  # Add WOW stations
  for(i in 1:5) {
    wow_lon <- plot_data[[paste0("wow_station_", i, "_Longitude")]][1]
    wow_lat <- plot_data[[paste0("wow_station_", i, "_Latitude")]][1]
    wow_val <- if(variable == "temperature") {
      plot_data[[paste0("wow_station_", i, "_station_temp")]][1]
    } else {
      plot_data[[paste0("wow_station_", i, "_station_wbgt")]][1]
    }
    
    if(!is.na(wow_lon) && !is.na(wow_lat) && !is.na(wow_val)) {
      stations_df <- rbind(stations_df, data.frame(
        lon = wow_lon,
        lat = wow_lat,
        value = wow_val,
        type = "WOW",
        label = paste0("WOW", i)
      ))
    }
  }
  
  # Calculate bounds
  lon_range <- range(stations_df$lon, na.rm = TRUE)
  lat_range <- range(stations_df$lat, na.rm = TRUE)
  lon_buffer <- diff(lon_range) * 0.2
  lat_buffer <- diff(lat_range) * 0.2
  
  # Create plot with better text positioning
  p <- ggplot(stations_df) +
    # Add points with size proportional to value
    geom_point(data = stations_df[!is.na(stations_df$value),],
               aes(x = lon, y = lat, 
                   color = value, 
                   size = value),
               alpha = 0.7) +
    
    # Add city center
    geom_point(data = stations_df[stations_df$type == "City Center",],
               aes(x = lon, y = lat),
               color = "red", shape = 18, size = 5) +
    
    # Use ggrepel for station labels
    ggrepel::geom_label_repel(
      data = stations_df,
      aes(x = lon, y = lat, label = label),
      size = 2.5,
      box.padding = 0.35,
      point.padding = 0.3,
      segment.color = 'grey50',
      segment.size = 0.2,
      max.overlaps = Inf,
      alpha = 0.9,
      seed = 42,
      fill = "white"
    ) +
    
    # Use ggrepel for value labels
    ggrepel::geom_text_repel(
      data = stations_df[!is.na(stations_df$value),],
      aes(x = lon, y = lat, 
          label = sprintf("%.1f°C", value)),
      size = 3, 
      fontface = "bold",
      box.padding = 0.25,
      point.padding = 0.25,
      segment.color = 'grey30',
      segment.size = 0.2,
      max.overlaps = Inf,
      seed = 42
    ) +
    
    # Color scale
    scale_color_gradient2(
      low = "blue", mid = "yellow", high = "red",
      midpoint = ifelse(variable == "temperature", 15, 20),
      name = var_label
    ) +
    
    scale_size_continuous(
      range = c(5, 15),
      guide = "none"
    ) +
    
    # Labels and theme
    labs(
      title = sprintf("%s Distribution - %s", var_label, city_name),
      subtitle = sprintf("Time: %s | %d stations reporting",
                        format(plot_data$Valid_datetime[1], "%Y-%m-%d %H:%M"),
                        sum(!is.na(stations_df$value))),
      x = "Longitude",
      y = "Latitude",
      caption = "Red diamond: city center | Circle size: value magnitude"
    ) +
    coord_fixed(ratio = 1.3) +
    xlim(lon_range[1] - lon_buffer, lon_range[2] + lon_buffer) +
    ylim(lat_range[1] - lat_buffer, lat_range[2] + lat_buffer) +
    theme_minimal() +
    theme(
      panel.grid.major = element_line(color = "gray90"),
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold", size = 14)
    )
  
  return(p)
}

# Function 3: Time Series Comparison Plot (保持不变)
plot_station_timeseries <- function(data, 
                                   city_name = NULL,
                                   hours_to_plot = 24) {
  
  # Auto-detect city name
  if(is.null(city_name)) {
    city_name <- unique(data$nearest_city)[1]
  }
  
  # Filter to recent hours
  latest_time <- max(data$Valid_datetime, na.rm = TRUE)
  start_time <- latest_time - (hours_to_plot * 3600)
  
  plot_data <- data %>%
    filter(Valid_datetime >= start_time & Valid_datetime <= latest_time)
  
  # Prepare long format data for plotting
  time_series_data <- plot_data %>%
    select(Valid_datetime, 
           KNMI = WBGT_obs_10,
           Model = WBGT_C,
           WOW_Mean = wow_wbgt_mean,
           WOW_Max = wow_wbgt_max) %>%
    pivot_longer(cols = -Valid_datetime,
                names_to = "Source",
                values_to = "WBGT")
  
  # Create time series plot
  p <- ggplot(time_series_data, aes(x = Valid_datetime, y = WBGT)) +
    geom_line(aes(color = Source), linewidth = 1.2, na.rm = TRUE) +
    geom_point(aes(color = Source, shape = Source), size = 2, na.rm = TRUE) +
    
    scale_color_manual(values = c("KNMI" = "darkgreen",
                                  "Model" = "blue",
                                  "WOW_Mean" = "purple",
                                  "WOW_Max" = "red")) +
    
    labs(title = sprintf("WBGT Time Series Comparison - %s", city_name),
         subtitle = sprintf("Last %d hours | Mean WOW stations: %.1f",
                           hours_to_plot,
                           mean(plot_data$wow_n_stations, na.rm = TRUE)),
         x = "Time",
         y = "WBGT (°C)",
         color = "Data Source",
         shape = "Data Source") +
    
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = 1))
  
  # Add uncertainty band if data is available
  if(all(c("wow_wbgt_min", "wow_wbgt_max") %in% names(plot_data))) {
    ribbon_data <- plot_data %>%
      filter(!is.na(wow_wbgt_min) & !is.na(wow_wbgt_max))
    
    if(nrow(ribbon_data) > 0) {
      p <- p + geom_ribbon(data = ribbon_data,
                          aes(x = Valid_datetime,
                              ymin = wow_wbgt_min,
                              ymax = wow_wbgt_max),
                          alpha = 0.2, fill = "purple",
                          inherit.aes = FALSE)
    }
  }
  
  return(p)
}

# Function 4: Comparison plot between two cities (保持不变)
plot_cities_comparison <- function(data1, data2, 
                                  city1_name = NULL, 
                                  city2_name = NULL,
                                  variable = "wbgt") {
  
  # Auto-detect city names
  if(is.null(city1_name)) city1_name <- unique(data1$nearest_city)[1]
  if(is.null(city2_name)) city2_name <- unique(data2$nearest_city)[1]
  
  # Select variable
  var_col <- ifelse(variable == "temperature", "T_DRYB_10", "WBGT_obs_10")
  var_label <- ifelse(variable == "temperature", "Temperature (°C)", "WBGT (°C)")
  
  # Prepare data
  data1_subset <- data1 %>%
    select(Valid_datetime, value = !!sym(var_col)) %>%
    mutate(City = city1_name)
  
  data2_subset <- data2 %>%
    select(Valid_datetime, value = !!sym(var_col)) %>%
    mutate(City = city2_name)
  
  combined_data <- rbind(data1_subset, data2_subset)
  
  # Create comparison plot
  p <- ggplot(combined_data, aes(x = Valid_datetime, y = value, color = City)) +
    geom_line(linewidth = 1.2, na.rm = TRUE) +
    geom_point(size = 1.5, alpha = 0.6, na.rm = TRUE) +
    
    scale_color_manual(values = c("blue", "red")) +
    
    labs(title = sprintf("%s Comparison: %s vs %s", 
                        var_label, city1_name, city2_name),
         x = "Time",
         y = var_label) +
    
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = 1))
  
  return(p)
}

# Wrapper function to create all maps for a city
create_city_analysis_maps <- function(data, city_name = NULL, time_point = NULL) {
  
  # Create a list to store all plots
  plots <- list()
  
  # Temperature map
  plots$temp_map <- plot_station_temperature_map(
    data, 
    city_name = city_name,
    time_point = time_point,
    variable = "temperature",
    include_wow = TRUE
  )
  
  # WBGT map
  plots$wbgt_map <- plot_station_temperature_map(
    data, 
    city_name = city_name,
    time_point = time_point,
    variable = "wbgt",
    include_wow = TRUE
  )
  
  # Simple heat map
  plots$heatmap <- plot_temperature_heatmap_simple(
    data,
    city_name = city_name,
    time_point = time_point,
    variable = "wbgt"
  )
  
  # Time series
  plots$timeseries <- plot_station_timeseries(
    data,
    city_name = city_name,
    hours_to_plot = 24
  )
  
  return(plots)
}

# 使用示例
time_point <- as.POSIXct("2023-07-09 12:00:00", tz = "UTC")

# 创建地图
rotterdam_maps <- create_city_analysis_maps(
  data_rotterdam,
  city_name = "Rotterdam", 
  time_point = time_point
)

amsterdam_maps <- create_city_analysis_maps(
  data_amsterdam,
  city_name = "Amsterdam",
  time_point = time_point
)

# shows map
print(amsterdam_maps$temp_map)
print(amsterdam_maps$wbgt_map)
print(amsterdam_maps$heatmap)
#print(amsterdam_maps$timeseries)
```


#post processing
#splite test and train
```{r}
# Define train/test split
training_period <- 30  # days for rolling window training
validation_start <- "2021-07-01"  # Start of validation period
test_start <- "2021-08-01"  # Start of test period

# Split data function
split_data <- function(data, lead_time = 24) {
  data_filtered <- data %>%
    filter(lead_time_hrs == lead_time) %>%
    arrange(Valid_datetime)
  
  # Define periods
  data_split <- data_filtered %>%
    mutate(
      period = case_when(
        Valid_datetime < as.POSIXct(validation_start) ~ "train",
        Valid_datetime >= as.POSIXct(validation_start) & 
          Valid_datetime < as.POSIXct(test_start) ~ "validation",
        TRUE ~ "test"
      )
    )
  
  return(data_split)
}
```

#Core crps
```{r}
# CRPS for normal distribution
# Core CRPS functions
# Core CRPS functions
crps.norm <- function(obs, mu, sd) {
  if(sd <= 0) sd <- 1e-6
  sd * ((obs - mu) / sd * (2 * pnorm((obs - mu) / sd) - 1) + 
        2 * dnorm((obs - mu) / sd) - 1 / sqrt(pi))
}

# Vectorized version for multiple inputs
crps.norm.vec <- function(obs, mu, sd) {
  sd <- pmax(sd, 1e-6)  # Ensure all sd values are positive
  sd * ((obs - mu) / sd * (2 * pnorm((obs - mu) / sd) - 1) + 
        2 * dnorm((obs - mu) / sd) - 1 / sqrt(pi))
}

crps.ensemble <- function(obs, fcst) {
  fcst <- sort(fcst)
  fun.ecdf <- ecdf(fcst)
  diff <- diff(sort(c(fcst, obs)))
  cdfs <- fun.ecdf(sort(c(fcst, obs)))[1:length(fcst)]
  crps <- sum((cdfs - (fcst > obs))^2 * diff)
  return(crps)
}

# CRPS for optimization (EMOS)
crps.normal <- function(param, t.obs, t.ens, t.var, K) {
  param[-1] <- param[-1]^2
  
  if(is.matrix(t.ens)) {
    MEAN <- as.vector(t.ens %*% param[1:K])
  } else {
    MEAN <- param[1] + param[2] * t.ens
  }
  
  VAR <- param[K + 1] + param[K + 2] * t.var
  VAR[VAR <= 0] <- 1e-6
  SIGMA <- sqrt(VAR)
  
  obs.stdz <- (t.obs - MEAN) / SIGMA
  crps.obs <- SIGMA * (obs.stdz * (2 * pnorm(obs.stdz, 0, 1) - 1) + 
                       2 * dnorm(obs.stdz, 0, 1) - 1 / sqrt(pi))
  
  return(sum(crps.obs, na.rm = TRUE))
}
crps.normal <- cmpfun(crps.normal)

calculate_rmse <- function(obs, pred) {
  sqrt(mean((obs - pred)^2, na.rm = TRUE))
}
```

# AUC ROC
```{r}
# Compare CRPS distributions across methods
plot_crps_distributions <- function(results) {
  
  library(ggplot2)
  library(dplyr)
  
  # Create violin plot for CRPS distributions
  p1 <- ggplot(results, aes(x = method, y = crps, fill = method)) +
    geom_violin(alpha = 0.7) +
    geom_boxplot(width = 0.2, alpha = 0.9) +
    facet_grid(obs_type ~ city) +
    scale_fill_manual(values = c("EMOS" = "#2ca02c",
                                "QR" = "#ff7f0e",
                                "RF" = "#1f77b4")) +
    labs(title = "CRPS Distribution by Post-Processing Method",
         subtitle = "Lower values indicate better performance",
         x = "Method", 
         y = "CRPS") +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  print(p1)
}
```

#Method 1: Quantile Regression (QR)
```{r}
# Quantile Regression
run_quantile_regression <- function(data, obs_column = "WBGT_obs_10", 
                                   lead_time = 24, training_days = 30,
                                   quantiles = seq(0.05, 0.95, 0.05)) {
  
  data <- data %>% filter(lead_time_hrs == lead_time)
  
  data_agg <- data %>%
    group_by(Valid_datetime, season) %>%
    reframe(
      ens_mean = mean(WBGT_C, na.rm = TRUE),
      ens_spread = sd(WBGT_C, na.rm = TRUE),
      obs = first(!!sym(obs_column))
    ) %>%
    distinct() %>%
    filter(!is.na(obs), !is.na(ens_mean)) %>%
    arrange(Valid_datetime)
  
  n_points <- nrow(data_agg)
  results_list <- list()
  
  for(i in (training_days + 1):n_points) {
    train_idx <- max(1, i - training_days):(i - 1)
    train_data <- data_agg[train_idx, ]
    test_point <- data_agg[i, ]
    
    if(nrow(train_data) < 10) next
    
    pred_quantiles <- numeric(length(quantiles))
    
    for(q_idx in seq_along(quantiles)) {
      q <- quantiles[q_idx]
      
      qr_fit <- tryCatch({
        rq(obs ~ ens_mean + ens_spread, data = train_data, tau = q)
      }, error = function(e) NULL)
      
      if(!is.null(qr_fit)) {
        pred_quantiles[q_idx] <- predict(qr_fit, newdata = test_point)
      } else {
        pred_quantiles[q_idx] <- quantile(train_data$obs, q)
      }
    }
    
    pred_mean <- mean(pred_quantiles, na.rm = TRUE)
    pred_sd <- sd(pred_quantiles, na.rm = TRUE)
    if(is.na(pred_sd) || pred_sd < 0.1) pred_sd <- sd(train_data$obs, na.rm = TRUE)
    
    results_list[[length(results_list) + 1]] <- data.frame(
      time = test_point$Valid_datetime,
      obs = test_point$obs,
      pred_mean = pred_mean,
      pred_sd = pred_sd,
      pred_quantiles = I(list(pred_quantiles)),
      method = "QR",
      stringsAsFactors = FALSE
    )
  }
  
  if(length(results_list) > 0) {
    return(bind_rows(results_list))
  } else {
    return(NULL)
  }
}
```

#Method 2: Random Forest (RF)
```{r}
run_random_forest <- function(data, obs_column = "WBGT_obs_10", 
                             lead_time = 24, training_days = 30,
                             n_trees = 100) {
  
  data <- data %>% filter(lead_time_hrs == lead_time)
  
  data_features <- data %>%
    group_by(Valid_datetime, season) %>%
    reframe(
      ens_mean = mean(WBGT_C, na.rm = TRUE),
      ens_median = median(WBGT_C, na.rm = TRUE),
      ens_sd = sd(WBGT_C, na.rm = TRUE),
      ens_min = min(WBGT_C, na.rm = TRUE),
      ens_max = max(WBGT_C, na.rm = TRUE),
      ens_q25 = quantile(WBGT_C, 0.25, na.rm = TRUE),
      ens_q75 = quantile(WBGT_C, 0.75, na.rm = TRUE),
      obs = first(!!sym(obs_column)),
      hour = lubridate::hour(first(Valid_datetime)),
      month = lubridate::month(first(Valid_datetime))
    ) %>%
    distinct() %>%
    filter(!is.na(obs), !is.na(ens_mean)) %>%
    arrange(Valid_datetime)
  
  n_points <- nrow(data_features)
  results_list <- list()
  
  for(i in (training_days + 1):n_points) {
    train_idx <- max(1, i - training_days):(i - 1)
    train_data <- data_features[train_idx, ]
    test_point <- data_features[i, ]
    
    if(nrow(train_data) < 20) next
    
    n_unique <- length(unique(train_data$obs))
    
    if(n_unique >= 10) {
      features <- c("ens_mean", "ens_sd", "ens_min", "ens_max", "hour", "month")
      
      rf_model <- tryCatch({
        suppressWarnings(
          randomForest(
            formula = as.formula(paste("obs ~", paste(features, collapse = "+"))),
            data = train_data,
            ntree = n_trees,
            mtry = 3
          )
        )
      }, error = function(e) NULL)
      
      if(!is.null(rf_model)) {
        pred_mean <- predict(rf_model, newdata = test_point)
        pred_sd <- sqrt(mean(rf_model$mse))
      } else {
        lm_model <- lm(obs ~ ens_mean + ens_sd, data = train_data)
        pred_mean <- predict(lm_model, newdata = test_point)
        pred_sd <- sigma(lm_model)
      }
    } else {
      lm_model <- lm(obs ~ ens_mean, data = train_data)
      pred_mean <- predict(lm_model, newdata = test_point)
      pred_sd <- sigma(lm_model)
    }
    
    results_list[[length(results_list) + 1]] <- data.frame(
      time = test_point$Valid_datetime,
      obs = test_point$obs,
      pred_mean = as.numeric(pred_mean),
      pred_sd = pred_sd,
      method = "RF",
      stringsAsFactors = FALSE
    )
  }
  
  if(length(results_list) > 0) {
    return(bind_rows(results_list))
  } else {
    return(NULL)
  }
}
```

#Method 3: EMOS (Ensemble Model Output Statistics)
```{r}
run_emos <- function(data, obs_column = "WBGT_obs_10", 
                    lead_time = 24, training_days = 30) {
  
  data <- data %>% filter(lead_time_hrs == lead_time)
  
  data_agg <- data %>%
    group_by(Valid_datetime, season) %>%
    reframe(
      ens_mean = mean(WBGT_C, na.rm = TRUE),
      ens_var = var(WBGT_C, na.rm = TRUE),
      obs = first(!!sym(obs_column)),
      ens_values = list(WBGT_C)
    ) %>%
    distinct() %>%
    filter(!is.na(obs), !is.na(ens_mean)) %>%
    arrange(Valid_datetime)
  
  n_times <- nrow(data_agg)
  results_list <- list()
  
  for(i in (training_days + 1):n_times) {
    train_idx <- max(1, i - training_days):(i - 1)
    train_data <- data_agg[train_idx, ]
    valid_data <- data_agg[i, ]
    
    if(nrow(train_data) < 10) next
    
    lm_fit <- lm(obs ~ ens_mean, data = train_data)
    
    a_init <- coef(lm_fit)[1]
    if(is.na(a_init)) a_init <- 0
    b_init <- coef(lm_fit)[2]
    if(is.na(b_init) || b_init < 0.1) b_init <- 1
    
    c_init <- var(residuals(lm_fit))
    if(is.na(c_init) || c_init < 0.1) c_init <- 1
    d_init <- 0.5
    
    params_init <- c(a_init, sqrt(b_init), sqrt(c_init), sqrt(d_init))
    
    t_obs <- train_data$obs
    t_ens <- as.matrix(cbind(1, train_data$ens_mean))
    t_var <- train_data$ens_var
    
    opt_result <- tryCatch({
      optim(params_init, crps.normal,
            t.obs = t_obs,
            t.ens = t_ens,
            t.var = t_var,
            K = 2,
            method = "BFGS",
            control = list(maxit = 500))
    }, error = function(e) NULL)
    
    if(is.null(opt_result)) {
      pred_mean <- a_init + b_init * valid_data$ens_mean
      pred_sd <- sqrt(c_init)
    } else {
      params <- opt_result$par
      params[-1] <- params[-1]^2
      
      pred_mean <- params[1] + params[2] * valid_data$ens_mean
      pred_var <- params[3] + params[4] * valid_data$ens_var
      pred_sd <- sqrt(max(pred_var, 0.1))
    }
    
    results_list[[length(results_list) + 1]] <- data.frame(
      time = valid_data$Valid_datetime,
      obs = valid_data$obs,
      pred_mean = pred_mean,
      pred_sd = pred_sd,
      method = "EMOS",
      stringsAsFactors = FALSE
    )
  }
  
  if(length(results_list) > 0) {
    return(bind_rows(results_list))
  } else {
    return(NULL)
  }
}
```

#Main Analysis Function with WOW Comparison
```{r}
# Main analysis comparing all methods to WOW max
analyze_vs_wow <- function(data_amsterdam, data_rotterdam, 
                          lead_time = 24, training_days = 30) {
  
  cat("\n================================================\n")
  cat("   WBGT Analysis: Post-Processing vs WOW Max    \n")
  cat("================================================\n\n")
  
  all_results <- list()
  
  for(city in c("Amsterdam", "Rotterdam")) {
    
    data <- if(city == "Amsterdam") data_amsterdam else data_rotterdam
    data_filtered <- data %>% filter(lead_time_hrs == lead_time)
    
    cat(sprintf("\n===== %s =====\n", city))
    
    # Get WOW max as benchmark
    wow_benchmark <- data_filtered %>%
      group_by(Valid_datetime) %>%
      summarise(
        wow_max = first(wow_wbgt_max),
        .groups = 'drop'
      ) %>%
      filter(!is.na(wow_max))
    
    cat(sprintf("WOW benchmark points: %d\n", nrow(wow_benchmark)))
    
    # Run post-processing on official observations
    #obs_column <- "WBGT_obs_10"
    # Run post-processing on WOW observations
    obs_column <- "wow_wbgt_max"
    
    # Check data availability
    n_obs <- sum(!is.na(data_filtered[[obs_column]]))
    cat(sprintf("Official observations available: %d\n", n_obs))
    
    if(n_obs < 100) {
      cat("Skipping: insufficient observations\n")
      next
    }
    
    # Run three methods
    cat("\nRunning post-processing methods:\n")
    
    # EMOS
    cat("  EMOS... ")
    results_emos <- tryCatch({
      run_emos(data, obs_column, lead_time, training_days)
    }, error = function(e) {
      cat(sprintf("Failed: %s\n", e$message))
      NULL
    })
    
    if(!is.null(results_emos)) {
      results_emos$city <- city
      cat(sprintf("Done (%d predictions)\n", nrow(results_emos)))
    }
    
    # QR
    cat("  Quantile Regression... ")
    results_qr <- tryCatch({
      run_quantile_regression(data, obs_column, lead_time, training_days)
    }, error = function(e) {
      cat(sprintf("Failed: %s\n", e$message))
      NULL
    })
    
    if(!is.null(results_qr)) {
      results_qr$city <- city
      cat(sprintf("Done (%d predictions)\n", nrow(results_qr)))
    }
    
    # RF
    cat("  Random Forest... ")
    results_rf <- tryCatch({
      suppressWarnings(
        run_random_forest(data, obs_column, lead_time, training_days)
      )
    }, error = function(e) {
      cat(sprintf("Failed: %s\n", e$message))
      NULL
    })
    
    if(!is.null(results_rf)) {
      results_rf$city <- city
      cat(sprintf("Done (%d predictions)\n", nrow(results_rf)))
    }
    
    # Combine and merge with WOW benchmark
    city_results <- bind_rows(results_emos, results_qr, results_rf)
    
    if(!is.null(city_results)) {
      # Merge with WOW benchmark
      city_results <- city_results %>%
        left_join(wow_benchmark, by = c("time" = "Valid_datetime")) %>%
        filter(!is.na(wow_max))
      
      # Calculate CRPS against WOW max (not observations)
      # Using vectorized version for efficiency
      city_results <- city_results %>%
        mutate(
          crps_vs_wow = crps.norm.vec(wow_max, pred_mean, pred_sd),
          error_vs_wow = pred_mean - wow_max,
          abs_error_vs_wow = abs(error_vs_wow)
        )
      
      all_results[[city]] <- city_results
    }
  }
  
  # Combine all results
  final_results <- bind_rows(all_results)
  
  # Add raw ensemble for comparison
  raw_results <- list()
  
  for(city in c("Amsterdam", "Rotterdam")) {
    data <- if(city == "Amsterdam") data_amsterdam else data_rotterdam
    data_filtered <- data %>% filter(lead_time_hrs == lead_time)
    
    raw_data <- data_filtered %>%
      group_by(Valid_datetime) %>%
      summarise(
        ens_mean = mean(WBGT_C, na.rm = TRUE),
        ens_sd = sd(WBGT_C, na.rm = TRUE),
        ens_values = list(WBGT_C),
        wow_max = first(wow_wbgt_max),
        .groups = 'drop'
      ) %>%
      filter(!is.na(wow_max)) %>%
      rowwise() %>%
      mutate(
        crps_vs_wow = crps.ensemble(wow_max, unlist(ens_values)),
        error_vs_wow = ens_mean - wow_max,
        abs_error_vs_wow = abs(error_vs_wow)
      ) %>%
      ungroup() %>%
      mutate(
        city = city,
        method = "RAW",
        pred_mean = ens_mean,
        pred_sd = ens_sd,
        time = Valid_datetime
      ) %>%
      select(time, city, method, pred_mean, pred_sd, wow_max, 
             crps_vs_wow, error_vs_wow, abs_error_vs_wow)
    
    raw_results[[city]] <- raw_data
  }
  
  raw_combined <- bind_rows(raw_results)
  
  # Combine with post-processed results
  all_results_with_raw <- bind_rows(final_results, raw_combined)
  
  return(all_results_with_raw)
}


```
#ROC-AUC Analysis for Extreme Events
```{r}
# ROC-AUC analysis for extreme WBGT events
calculate_roc_auc <- function(results, threshold = 25) {
  
  cat(sprintf("\n=== ROC-AUC Analysis (WBGT > %d°C) ===\n", threshold))
  
  roc_results <- list()
  
  for(city in unique(results$city)) {
    for(method in unique(results$method)) {
      
      subset_data <- results %>%
        filter(city == !!city, method == !!method) %>%
        filter(!is.na(wow_max))
      
      if(nrow(subset_data) < 50) next
      
      # Calculate probabilities for exceeding threshold
      # Assuming normal distribution for predictions
      subset_data <- subset_data %>%
        mutate(
          obs_exceed = wow_max > threshold,
          pred_prob = pnorm(threshold, mean = pred_mean, sd = pred_sd, 
                           lower.tail = FALSE)
        )
      
      # Calculate ROC
      if(sum(subset_data$obs_exceed) > 5 && sum(!subset_data$obs_exceed) > 5) {
        roc_obj <- roc(subset_data$obs_exceed, subset_data$pred_prob, 
                       quiet = TRUE)
        
        auc_value <- auc(roc_obj)
        
        roc_results[[paste(city, method, sep="_")]] <- data.frame(
          city = city,
          method = method,
          threshold = threshold,
          auc = as.numeric(auc_value),
          n_events = sum(subset_data$obs_exceed),
          n_total = nrow(subset_data),
          stringsAsFactors = FALSE
        )
        
        # Store ROC curve data for plotting
        roc_curve <- data.frame(
          city = city,
          method = method,
          sensitivity = roc_obj$sensitivities,
          specificity = roc_obj$specificities,
          stringsAsFactors = FALSE
        )
        
        attr(roc_results[[paste(city, method, sep="_")]], "roc_curve") <- roc_curve
      }
    }
  }
  
  auc_summary <- bind_rows(roc_results)
  
  # Print summary
  print(auc_summary %>% 
        arrange(city, desc(auc)) %>%
        mutate(auc = round(auc, 3)))
  
  return(list(
    auc_summary = auc_summary,
    roc_data = roc_results
  ))
}

# Plot ROC curves
plot_roc_curves <- function(roc_analysis) {
  
  # Extract ROC curve data
  all_curves <- list()
  
  for(name in names(roc_analysis$roc_data)) {
    curve_data <- attr(roc_analysis$roc_data[[name]], "roc_curve")
    if(!is.null(curve_data)) {
      all_curves[[name]] <- curve_data
    }
  }
  
  roc_curves <- bind_rows(all_curves)
  
  # Create plot
  p <- ggplot(roc_curves, aes(x = 1 - specificity, y = sensitivity, 
                              color = method)) +
    geom_line(size = 1.2) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", alpha = 0.5) +
    facet_wrap(~city) +
    scale_color_manual(values = c("RAW" = "gray60",
                                 "EMOS" = "#2ca02c",
                                 "QR" = "#ff7f0e",
                                 "RF" = "#1f77b4")) +
    labs(title = "ROC Curves for Extreme WBGT Events (>25°C)",
         subtitle = "Comparing against WOW max observations",
         x = "False Positive Rate (1 - Specificity)",
         y = "True Positive Rate (Sensitivity)") +
    theme_minimal() +
    coord_fixed() +
    theme(legend.position = "bottom")
  
  # Add AUC values to legend
  auc_text <- roc_analysis$auc_summary %>%
    group_by(method) %>%
    summarise(avg_auc = mean(auc), .groups = 'drop') %>%
    mutate(label = sprintf("%s (AUC: %.3f)", method, avg_auc))
  
  print(p)
  
  return(p)
}
```

#Comprehensive Comparison Analysis
```{r}
# Create comprehensive comparison table
create_wow_comparison_table <- function(results) {
  
  comparison <- results %>%
    group_by(city, method) %>%
    summarise(
      n = n(),
      RMSE_vs_WOW = sqrt(mean(error_vs_wow^2, na.rm = TRUE)),
      MAE_vs_WOW = mean(abs_error_vs_wow, na.rm = TRUE),
      Bias_vs_WOW = mean(error_vs_wow, na.rm = TRUE),
      CRPS_vs_WOW = mean(crps_vs_wow, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    mutate(across(where(is.numeric), ~round(., 3)))
  
  # Calculate improvements over raw ensemble
  improvements <- comparison %>%
    group_by(city) %>%
    mutate(
      raw_crps = CRPS_vs_WOW[method == "RAW"],
      raw_rmse = RMSE_vs_WOW[method == "RAW"],
      CRPS_improvement = raw_crps - CRPS_vs_WOW,
      RMSE_improvement = raw_rmse - RMSE_vs_WOW,
      CRPS_improvement_pct = (CRPS_improvement / raw_crps) * 100,
      RMSE_improvement_pct = (RMSE_improvement / raw_rmse) * 100
    ) %>%
    ungroup() %>%
    select(-raw_crps, -raw_rmse)
  
  return(improvements)
}

# Visualization: CRPS comparison against WOW
plot_crps_vs_wow <- function(comparison_table) {
  
  # Prepare data for plotting
  plot_data <- comparison_table %>%
    mutate(method = factor(method, levels = c("RAW", "EMOS", "QR", "RF")))
  
  # Plot 1: Absolute CRPS values
  p1 <- ggplot(plot_data, aes(x = method, y = CRPS_vs_WOW, fill = method)) +
    geom_bar(stat = "identity", width = 0.7) +
    geom_text(aes(label = sprintf("%.3f", CRPS_vs_WOW)), 
              vjust = -0.5, size = 3) +
    facet_wrap(~city) +
    scale_fill_manual(values = c("RAW" = "gray60",
                                "EMOS" = "#2ca02c",
                                "QR" = "#ff7f0e",
                                "RF" = "#1f77b4")) +
    labs(title = "CRPS Comparison: All Methods vs WOW Max",
         subtitle = "Lower values indicate better agreement with crowd-sourced maximum WBGT",
         x = "Method",
         y = "Mean CRPS (vs WOW max)") +
    theme_minimal() +
    theme(legend.position = "none")
  
  # Plot 2: Improvement percentages
  p2 <- plot_data %>%
    filter(method != "RAW") %>%
    ggplot(aes(x = method, y = CRPS_improvement_pct, fill = method)) +
    geom_bar(stat = "identity", width = 0.7) +
    geom_text(aes(label = sprintf("%.1f%%", CRPS_improvement_pct)), 
              vjust = -0.5, size = 3) +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
    facet_wrap(~city) +
    scale_fill_manual(values = c("EMOS" = "#2ca02c",
                                "QR" = "#ff7f0e",
                                "RF" = "#1f77b4")) +
    labs(title = "CRPS Improvement over Raw Ensemble",
         subtitle = "When comparing to WOW max observations",
         x = "Post-Processing Method",
         y = "Improvement (%)") +
    theme_minimal() +
    theme(legend.position = "none")
  
  library(gridExtra)
  grid.arrange(p1, p2, ncol = 1)
}
```

#main execution
```{r}
# Execute complete analysis
cat("Starting WBGT Post-Processing Analysis with WOW Benchmark\n")
cat("=========================================================\n\n")

# 1. Run main analysis
results_vs_wow <- analyze_vs_wow(
  data_amsterdam, 
  data_rotterdam,
  lead_time = 24,
  training_days = 30
)

cat(sprintf("\nTotal results generated: %d\n", nrow(results_vs_wow)))

# 2. Create comparison table
comparison_wow <- create_wow_comparison_table(results_vs_wow)

cat("\n=== COMPARISON TABLE (vs WOW Max) ===\n")
print(comparison_wow)

# 3. ROC-AUC Analysis for extreme events
roc_analysis <- calculate_roc_auc(results_vs_wow, threshold = 25)

# 4. Generate visualizations
cat("\n=== Generating Plots ===\n")

# CRPS comparison plot
plot_crps_vs_wow(comparison_wow)

# ROC curves
plot_roc_curves(roc_analysis)

# 5. Summary statistics
cat("\n=== SUMMARY STATISTICS ===\n")

# Best performers
best_methods <- comparison_wow %>%
  filter(method != "RAW") %>%
  group_by(city) %>%
  slice_min(CRPS_vs_WOW, n = 1) %>%
  select(city, Best_Method = method, CRPS_vs_WOW, CRPS_improvement_pct)

cat("\nBest performing methods (lowest CRPS vs WOW max):\n")
print(best_methods)

# Overall improvements
overall_improvements <- comparison_wow %>%
  filter(method != "RAW") %>%
  group_by(method) %>%
  summarise(
    Avg_CRPS_Improvement = mean(CRPS_improvement_pct, na.rm = TRUE),
    Avg_RMSE_Improvement = mean(RMSE_improvement_pct, na.rm = TRUE),
    Avg_AUC = mean(roc_analysis$auc_summary$auc[
      roc_analysis$auc_summary$method == method], na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  arrange(desc(Avg_CRPS_Improvement))

cat("\nOverall method performance:\n")
print(overall_improvements)

# 6. Save results
output_dir <- here("results", "wow_comparison_results")
if(!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)

write.csv(results_vs_wow,
         file.path(output_dir, "all_results_vs_wow.csv"),
         row.names = FALSE)

write.csv(comparison_wow,
         file.path(output_dir, "comparison_table_vs_wow.csv"),
         row.names = FALSE)

write.csv(roc_analysis$auc_summary,
         file.path(output_dir, "roc_auc_summary.csv"),
         row.names = FALSE)

cat(sprintf("\n✓ Results saved to %s\n", output_dir))

# 7. Key insights
cat("\n=== KEY INSIGHTS ===\n")
cat("1. All CRPS values are calculated against WOW max observations\n")
cat("2. This shows how well post-processing captures local extreme conditions\n")
cat("3. Improvements demonstrate the value of local post-processing\n")
cat("4. ROC-AUC shows skill in predicting extreme events (WBGT > 25°C)\n")


```

#seasonal analysis
```{r}
# ============================================
# SEASONAL ANALYSIS - FIXED VERSION
# ============================================

# First, we need to add season information to the results
add_season_to_results <- function(results, data_amsterdam, data_rotterdam) {
  
  # Extract season information from original data
  get_season_mapping <- function(data) {
    data %>%
      select(Valid_datetime, season) %>%
      distinct() %>%
      rename(time = Valid_datetime)
  }
  
  # Get season mappings from both cities
  amsterdam_seasons <- get_season_mapping(data_amsterdam)
  rotterdam_seasons <- get_season_mapping(data_rotterdam)
  
  # Combine (they should be the same for same dates)
  all_seasons <- bind_rows(amsterdam_seasons, rotterdam_seasons) %>%
    distinct()
  
  # Join season information to results
  results_with_season <- results %>%
    left_join(all_seasons, by = "time")
  
  # Check if join was successful
  if(sum(is.na(results_with_season$season)) > 0) {
    cat(sprintf("Warning: %d rows have missing season information\n", 
                sum(is.na(results_with_season$season))))
  }
  
  return(results_with_season)
}

analyze_seasonal_performance <- function(results, data_amsterdam, data_rotterdam, 
                                        lead_time = 24) {
  
  cat("\n================================================\n")
  cat("   SEASONAL PERFORMANCE ANALYSIS                \n")
  cat("================================================\n\n")
  
  # Add season information to results
  results_with_season <- add_season_to_results(results, data_amsterdam, data_rotterdam)
  
  # Check available seasons
  cat("Available seasons in data:\n")
  print(table(results_with_season$season))
  cat("\n")
  
  # 1. Calculate seasonal CRPS for post-processed methods
  seasonal_results <- results_with_season %>%
    filter(!is.na(season)) %>%
    group_by(city, season, method) %>%
    summarise(
      n = n(),
      mean_crps = mean(crps_vs_wow, na.rm = TRUE),
      median_crps = median(crps_vs_wow, na.rm = TRUE),
      sd_crps = sd(crps_vs_wow, na.rm = TRUE),
      mean_rmse = sqrt(mean(error_vs_wow^2, na.rm = TRUE)),
      mean_mae = mean(abs_error_vs_wow, na.rm = TRUE),
      mean_bias = mean(error_vs_wow, na.rm = TRUE),
      .groups = 'drop'
    )
  
  # 2. Calculate raw ensemble seasonal CRPS
  calculate_raw_seasonal_crps <- function(data, city_name, lead_time = 6) {
    
    data_filtered <- data %>%
      filter(lead_time_hrs == lead_time)
    
    raw_seasonal <- data_filtered %>%
      group_by(Valid_datetime, season) %>%
      summarise(
        wow_max = first(wow_wbgt_max),
        ens_mean = mean(WBGT_C, na.rm = TRUE),
        ens_values = list(WBGT_C),
        .groups = 'drop'
      ) %>%
      filter(!is.na(wow_max)) %>%
      rowwise() %>%
      mutate(
        crps_raw = crps.ensemble(wow_max, unlist(ens_values))
      ) %>%
      ungroup() %>%
      group_by(season) %>%
      summarise(
        n_raw = n(),
        mean_crps_raw = mean(crps_raw, na.rm = TRUE),
        median_crps_raw = median(crps_raw, na.rm = TRUE),
        sd_crps_raw = sd(crps_raw, na.rm = TRUE),
        .groups = 'drop'
      ) %>%
      mutate(city = city_name)
    
    return(raw_seasonal)
  }
  
  # Calculate for both cities
  raw_amsterdam_seasonal <- calculate_raw_seasonal_crps(data_amsterdam, "Amsterdam", lead_time)
  raw_rotterdam_seasonal <- calculate_raw_seasonal_crps(data_rotterdam, "Rotterdam", lead_time)
  raw_seasonal_all <- bind_rows(raw_amsterdam_seasonal, raw_rotterdam_seasonal)
  
  # 3. Combine and calculate improvements
  seasonal_comparison <- seasonal_results %>%
    left_join(raw_seasonal_all %>% 
              select(city, season, mean_crps_raw, n_raw),
              by = c("city", "season")) %>%
    mutate(
      crps_improvement = mean_crps_raw - mean_crps,
      crps_improvement_pct = (crps_improvement / mean_crps_raw) * 100
    ) %>%
    arrange(city, season, method)
  
  # 4. Create seasonal_comparison_full by adding RAW results
  raw_for_table <- raw_seasonal_all %>%
    mutate(
      method = "RAW",
      n = n_raw,
      mean_crps = mean_crps_raw,
      median_crps = median_crps_raw,
      sd_crps = sd_crps_raw,
      crps_improvement = 0,
      crps_improvement_pct = 0
    ) %>%
    select(city, season, method, n, mean_crps, median_crps, sd_crps, crps_improvement_pct)
  
  seasonal_comparison_full <- bind_rows(
    raw_for_table,
    seasonal_comparison %>% 
      select(city, season, method, n, mean_crps, median_crps, sd_crps, crps_improvement_pct)
  ) %>%
    arrange(city, season, method)
  
  # 5. Print formatted results
  cat("\n=== SEASONAL CRPS PERFORMANCE ===\n\n")
  
  for(city_name in unique(seasonal_comparison_full$city)) {
    cat(sprintf("\n%s:\n", city_name))
    cat(sprintf("%s\n", paste(rep("-", 70), collapse = "")))
    
    city_seasonal <- seasonal_comparison_full %>%
      filter(city == city_name) %>%
      mutate(
        mean_crps = round(mean_crps, 3),
        crps_improvement_pct = round(crps_improvement_pct, 1)
      )
    
    # Create wide format for display
    city_wide <- city_seasonal %>%
      select(season, method, mean_crps, crps_improvement_pct) %>%
      pivot_wider(
        names_from = method,
        values_from = c(mean_crps, crps_improvement_pct),
        names_sep = "_"
      )
    
    print(city_wide, n = Inf)
  }
  
  # 6. Best performing season analysis
  cat("\n\n=== BEST PERFORMING SEASONS ===\n")
  
  best_seasons <- seasonal_comparison %>%
    group_by(city, method) %>%
    slice_max(crps_improvement_pct, n = 1) %>%
    select(city, method, best_season = season, 
           max_improvement = crps_improvement_pct) %>%
    mutate(max_improvement = round(max_improvement, 1))
  
  print(best_seasons, n = Inf)
  
  # 7. Worst performing season analysis
  cat("\n\n=== MOST CHALLENGING SEASONS ===\n")
  
  worst_seasons <- seasonal_comparison %>%
    group_by(city, method) %>%
    slice_min(crps_improvement_pct, n = 1) %>%
    select(city, method, worst_season = season, 
           min_improvement = crps_improvement_pct) %>%
    mutate(min_improvement = round(min_improvement, 1))
  
  print(worst_seasons, n = Inf)
  
  # 8. Overall seasonal patterns
  cat("\n\n=== AVERAGE IMPROVEMENT BY SEASON (All Methods) ===\n")
  
  seasonal_avg <- seasonal_comparison %>%
    group_by(season) %>%
    summarise(
      n_total = sum(n),
      avg_improvement = mean(crps_improvement_pct, na.rm = TRUE),
      sd_improvement = sd(crps_improvement_pct, na.rm = TRUE),
      min_improvement = min(crps_improvement_pct, na.rm = TRUE),
      max_improvement = max(crps_improvement_pct, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    arrange(desc(avg_improvement)) %>%
    mutate(across(where(is.numeric) & !n_total, round, 1))
  
  print(seasonal_avg)
  
  # Return all results
  return(list(
    seasonal_comparison = seasonal_comparison,
    seasonal_comparison_full = seasonal_comparison_full,
    seasonal_avg = seasonal_avg,
    best_seasons = best_seasons,
    worst_seasons = worst_seasons
  ))
}

# Plotting function
plot_seasonal_analysis <- function(seasonal_analysis) {
  
  library(ggplot2)
  
  data_plot <- seasonal_analysis$seasonal_comparison_full %>%
    filter(method != "RAW")
  
  # Plot 1: CRPS by season
  p1 <- ggplot(data_plot, 
               aes(x = season, y = mean_crps, fill = method)) +
    geom_bar(stat = "identity", position = "dodge") +
    facet_wrap(~city) +
    scale_fill_manual(values = c("EMOS" = "#2ca02c",
                                "QR" = "#ff7f0e",
                                "RF" = "#1f77b4")) +
    labs(title = "Seasonal CRPS Performance",
         x = "Season", y = "Mean CRPS") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p1)
  
  # Plot 2: Improvement percentages
  p2 <- ggplot(data_plot,
               aes(x = season, y = crps_improvement_pct, fill = method)) +
    geom_bar(stat = "identity", position = "dodge") +
    geom_text(aes(label = sprintf("%.1f%%", crps_improvement_pct)),
              position = position_dodge(width = 0.9),
              vjust = -0.5, size = 3) +
    facet_wrap(~city) +
    scale_fill_manual(values = c("EMOS" = "#2ca02c",
                                "QR" = "#ff7f0e",
                                "RF" = "#1f77b4")) +
    labs(title = "Seasonal Improvement over Raw Ensemble",
         x = "Season", y = "CRPS Improvement (%)") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  print(p2)
}

# ============================================
# EXECUTE ANALYSIS
# ============================================

# Run the seasonal analysis
seasonal_analysis <- analyze_seasonal_performance(
  results = results_vs_wow,  # Your post-processing results
  data_amsterdam = data_amsterdam,
  data_rotterdam = data_rotterdam,
  lead_time = 24
)

# Create visualizations
plot_seasonal_analysis(seasonal_analysis)

# Save results
write.csv(seasonal_analysis$seasonal_comparison_full,
          here("results", "some_results", "seasonal_crps_full.csv"), row.names = FALSE)

write.csv(seasonal_analysis$seasonal_avg,
          here("results", "some_results", "seasonal_summary.csv"), row.names = FALSE)

cat("\n✓ Seasonal analysis complete!\n")

```

#PEV framework
```{r}
# ============================================
# PEV ANALYSIS FOR WBGT POST-PROCESSING
# ============================================

library(dplyr)
library(tidyr)
library(ggplot2)

# Main PEV calculation function
calculate_pev <- function(obs, pred_mean, pred_sd, threshold, cost_loss_ratio) {
  
  # Remove N
  valid_idx <- !is.na(obs) & !is.na(pred_mean) & !is.na(pred_sd)
  obs <- obs[valid_idx]
  pred_mean <- pred_mean[valid_idx]
  pred_sd <- pred_sd[valid_idx]
  n <- length(obs)
  
  if(n < 10) return(NA)
  
  # Calculate forecast probability of exceeding threshold
  prob_exceed <- 1 - pnorm(threshold, pred_mean, pred_sd)
  
  # Binary decision based on cost-loss ratio
  take_action <- prob_exceed > cost_loss_ratio
  
  # Observed event
  event_occurred <- obs > threshold
  
  # Contingency table elements
  hits <- sum(take_action & event_occurred)
  false_alarms <- sum(take_action & !event_occurred)
  misses <- sum(!take_action & event_occurred)
  correct_negatives <- sum(!take_action & !event_occurred)
  
  # Observed relative frequency
  orf <- sum(event_occurred) / n
  
  # Handle edge cases
  if(orf == 0 || orf == 1) return(0)
  
  # Calculate expenses
  expense_forecast <- (hits + false_alarms) * cost_loss_ratio + misses * 1
  
  # Climatology strategy expense
  if(cost_loss_ratio < orf) {
    # Always protect
    expense_clim <- n * cost_loss_ratio
  } else {
    # Never protect
    expense_clim <- sum(event_occurred) * 1
  }
  
  # Perfect forecast expense
  expense_perfect <- sum(event_occurred) * cost_loss_ratio
  
  # PEV calculation
  if(abs(expense_clim - expense_perfect) < 1e-10) {
    pev <- 0
  } else {
    pev <- (expense_clim - expense_forecast) / (expense_clim - expense_perfect)
  }
  
  return(pev)
}

# Calculate PEV for raw ensemble
calculate_pev_raw <- function(data, threshold, cost_loss_ratio, lead_time = 6) {
  
  # Filter data
  data_filtered <- data %>%
    filter(lead_time_hrs == lead_time)
  
  # Aggregate ensemble
  data_agg <- data_filtered %>%
    group_by(Valid_datetime) %>%
    summarise(
      wow_max = first(wow_wbgt_max),
      ens_mean = mean(WBGT_C, na.rm = TRUE),
      ens_sd = sd(WBGT_C, na.rm = TRUE),
      .groups = 'drop'
    ) %>%
    filter(!is.na(wow_max))
  
  # Calculate PEV
  pev <- calculate_pev(
    obs = data_agg$wow_max,
    pred_mean = data_agg$ens_mean,
    pred_sd = data_agg$ens_sd,
    threshold = threshold,
    cost_loss_ratio = cost_loss_ratio
  )
  
  return(pev)
}

# Calculate PEV curves for all methods
calculate_pev_curves <- function(results, data_amsterdam, data_rotterdam,
                                thresholds = c(20, 25, 30),
                                cl_ratios = seq(0.01, 0.5, by = 0.02)) {
  
  all_pev_results <- list()
  
  for(city in unique(results$city)) {
    for(method in unique(results$method)) {
      for(threshold in thresholds) {
        
        # Filter results
        method_data <- results %>%
          filter(city == !!city, method == !!method)
        
        if(nrow(method_data) < 100) next
        
        # Check if threshold is reasonable
        if(threshold > quantile(method_data$wow_max, 0.99, na.rm = TRUE)) next
        
        # Calculate PEV for each cost-loss ratio
        pev_values <- sapply(cl_ratios, function(cl) {
          calculate_pev(
            obs = method_data$wow_max,
            pred_mean = method_data$pred_mean,
            pred_sd = method_data$pred_sd,
            threshold = threshold,
            cost_loss_ratio = cl
          )
        })
        
        # Store results
        all_pev_results[[length(all_pev_results) + 1]] <- data.frame(
          city = city,
          method = method,
          threshold = threshold,
          cost_loss_ratio = cl_ratios,
          pev = pev_values,
          stringsAsFactors = FALSE
        )
      }
    }
    
    # Add raw ensemble results
    raw_data <- if(city == "Amsterdam") data_amsterdam else data_rotterdam
    
    for(threshold in thresholds) {
      pev_values_raw <- sapply(cl_ratios, function(cl) {
        calculate_pev_raw(raw_data, threshold, cl, lead_time = 6)
      })
      
      all_pev_results[[length(all_pev_results) + 1]] <- data.frame(
        city = city,
        method = "RAW",
        threshold = threshold,
        cost_loss_ratio = cl_ratios,
        pev = pev_values_raw,
        stringsAsFactors = FALSE
      )
    }
  }
  
  return(bind_rows(all_pev_results))
}

# Calculate integrated PEV (area under curve)
calculate_integrated_pev <- function(pev_curves) {
  
  integrated <- pev_curves %>%
    group_by(city, method, threshold) %>%
    summarise(
      integrated_pev = {
        valid_idx <- !is.na(pev) & pev > -0.5  # Remove extreme negative values
        if(sum(valid_idx) < 2) {
          NA
        } else {
          x <- cost_loss_ratio[valid_idx]
          y <- pev[valid_idx]
          # Trapezoidal integration
          sum(diff(x) * (y[-1] + y[-length(y)]) / 2)
        }
      },
      max_pev = max(pev[!is.na(pev)], na.rm = TRUE),
      optimal_cl = cost_loss_ratio[which.max(pev)],
      positive_range = sum(pev > 0, na.rm = TRUE) / length(pev),
      .groups = 'drop'
    )
  
  return(integrated)
}

# Plot PEV curves
plot_pev_curves <- function(pev_curves, selected_threshold = 25) {
  
  # Filter data
  plot_data <- pev_curves %>%
    filter(threshold == selected_threshold,
           !is.na(pev),
           pev > -1)  # Remove extreme negative values for visualization
  
  # Define colors
  method_colors <- c("RAW" = "gray60",
                    "EMOS" = "#2ca02c",
                    "QR" = "#ff7f0e",
                    "RF" = "#1f77b4")
  
  # Create plot
  p <- ggplot(plot_data, aes(x = cost_loss_ratio, y = pev, 
                             color = method, linetype = method)) +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.3) +
    geom_line(size = 1.2) +
    facet_wrap(~city, ncol = 2) +
    scale_color_manual(values = method_colors) +
    scale_y_continuous(limits = c(-0.2, 1)) +
    labs(
      title = sprintf("Potential Economic Value Curves (Threshold = %d°C)", selected_threshold),
      subtitle = "Higher values indicate better economic value for decision-making",
      x = "Cost/Loss Ratio",
      y = "Potential Economic Value",
      color = "Method",
      linetype = "Method"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom",
          panel.grid.minor = element_blank())
  
  return(p)
}

# Create comparison table
create_pev_comparison_table <- function(integrated_pev) {
  
  # Reshape for comparison
  comparison <- integrated_pev %>%
    select(city, method, threshold, integrated_pev, max_pev, optimal_cl) %>%
    arrange(city, threshold, desc(integrated_pev)) %>%
    mutate(
      integrated_pev = round(integrated_pev, 3),
      max_pev = round(max_pev, 3),
      optimal_cl = round(optimal_cl, 3)
    )
  
  # Calculate improvement over RAW
  improvement <- comparison %>%
    group_by(city, threshold) %>%
    mutate(
      raw_integrated = integrated_pev[method == "RAW"],
      improvement_pct = round((integrated_pev - raw_integrated) / abs(raw_integrated) * 100, 1)
    ) %>%
    ungroup() %>%
    select(-raw_integrated)
  
  return(improvement)
}

# Generate LaTeX table
create_pev_latex_table <- function(pev_comparison) {
  
  cat("\n=== LATEX TABLE FOR PEV RESULTS ===\n")
  cat("\\begin{table}[h!]\n")
  cat("\\centering\n")
  cat("\\caption{Integrated PEV and maximum PEV values for different thresholds}\n")
  cat("\\label{tab:pev_analysis}\n")
  cat("\\begin{tabular}{llccccc}\n")
  cat("\\hline\n")
  cat("City & Method & Threshold & Integrated PEV & Max PEV & Optimal C/L & Improvement (\\%) \\\\\n")
  cat("\\hline\n")
  
  for(city_name in unique(pev_comparison$city)) {
    city_data <- pev_comparison %>% filter(city == city_name)
    
    first_row <- TRUE
    for(i in 1:nrow(city_data)) {
      if(first_row) {
        cat(sprintf("\\multirow{%d}{*}{%s}\n", nrow(city_data), city_name))
        first_row <- FALSE
      }
      
      improvement_str <- ifelse(city_data$method[i] == "RAW", 
                               "--", 
                               sprintf("%.1f", city_data$improvement_pct[i]))
      
      cat(sprintf(" & %s & %d & %.3f & %.3f & %.3f & %s \\\\\n",
                 city_data$method[i],
                 city_data$threshold[i],
                 city_data$integrated_pev[i],
                 city_data$max_pev[i],
                 city_data$optimal_cl[i],
                 improvement_str))
    }
    
    if(city_name == unique(pev_comparison$city)[1]) {
      cat("\\hline\n")
    }
  }
  
  cat("\\hline\n")
  cat("\\end{tabular}\n")
  cat("\\end{table}\n")
}

# ============================================
# MAIN PEV ANALYSIS EXECUTION
# ============================================

run_pev_analysis <- function(results, data_amsterdam, data_rotterdam) {
  
  cat("\n========================================\n")
  cat("   POTENTIAL ECONOMIC VALUE ANALYSIS    \n")
  cat("========================================\n\n")
  
  # Define thresholds based on data range
  # Check actual data range
  wow_range <- range(results$wow_max, na.rm = TRUE)
  cat(sprintf("WOW max range: %.1f to %.1f°C\n", wow_range[1], wow_range[2]))
  
  # Set meaningful thresholds
  thresholds <- c(20, 25)  # Focus on heat stress thresholds
  
  # Calculate PEV curves
  cat("\nCalculating PEV curves...\n")
  pev_curves <- calculate_pev_curves(
    results = results,
    data_amsterdam = data_amsterdam,
    data_rotterdam = data_rotterdam,
    thresholds = thresholds,
    cl_ratios = seq(0.01, 0.5, by = 0.02)
  )
  
  # Calculate integrated PEV
  cat("Calculating integrated PEV...\n")
  integrated_pev <- calculate_integrated_pev(pev_curves)
  
  # Create comparison table
  pev_comparison <- create_pev_comparison_table(integrated_pev)
  
  # Print summary
  cat("\n=== INTEGRATED PEV SUMMARY ===\n")
  print(pev_comparison)
  
  # Create plots
  cat("\nGenerating PEV curves...\n")
  
  # Plot for each threshold
  plots <- list()
  for(thresh in thresholds) {
    plots[[as.character(thresh)]] <- plot_pev_curves(pev_curves, thresh)
    print(plots[[as.character(thresh)]])
  }
  
  # Generate LaTeX table
  create_pev_latex_table(pev_comparison %>% filter(threshold == 25))
  
  # Save results
  write.csv(pev_curves, here("results", "some_results", "pev_curves_full.csv"), row.names = FALSE)
  write.csv(pev_comparison, here("results", "some_results", "pev_comparison_table.csv"), row.names = FALSE)
  
  cat("\n✓ PEV analysis complete!\n")
  
  return(list(
    curves = pev_curves,
    integrated = integrated_pev,
    comparison = pev_comparison,
    plots = plots
  ))
}

# Execute PEV analysis
pev_results <- run_pev_analysis(results_vs_wow, data_amsterdam, data_rotterdam)

# Additional analysis: Best method by cost-loss ratio range
analyze_pev_by_cl_range <- function(pev_curves) {
  
  # Define C/L ranges relevant for different users
  cl_ranges <- list(
    "Risk-averse (0.01-0.10)" = c(0.01, 0.10),
    "Moderate (0.10-0.25)" = c(0.10, 0.25),
    "Risk-tolerant (0.25-0.50)" = c(0.25, 0.50)
  )
  
  range_analysis <- list()
  
  for(range_name in names(cl_ranges)) {
    range_limits <- cl_ranges[[range_name]]
    
    range_pev <- pev_curves %>%
      filter(cost_loss_ratio >= range_limits[1],
             cost_loss_ratio <= range_limits[2]) %>%
      group_by(city, method, threshold) %>%
      summarise(
        mean_pev = mean(pev, na.rm = TRUE),
        .groups = 'drop'
      ) %>%
      group_by(city, threshold) %>%
      slice_max(mean_pev, n = 1) %>%
      mutate(cl_range = range_name)
    
    range_analysis[[range_name]] <- range_pev
  }
  
  final_analysis <- bind_rows(range_analysis)
  
  cat("\n=== BEST METHOD BY COST-LOSS RATIO RANGE ===\n")
  print(final_analysis)
  
  return(final_analysis)
}

# Run additional analysis
cl_range_analysis <- analyze_pev_by_cl_range(pev_results$curves)
```

