---
title: "preliminary_test_visualisation_forecast"
author: "Wenkai_Zhong"
date: "2025-07-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#change R language to english
Sys.setlocale("LC_TIME", "English")
rm(list = ls())

library(R.utils)
library(ggplot2)
library(patchwork)
library(lubridate)
library(here)
library(ncdf4)
library(ggrepel)
library(tidyverse)
library(plotly)
#library(sf)
#library(rnaturalearth)

# creat .gitignore file to avoid upload data(too large)
cat("# Ignore all data files
data/
*.RData
*.Rhistory
.Rproj.user/
.RDataTmp*
", file = ".gitignore")
```

## Reading in the netcdf

# Model: These are the files starting with "combined_raw_". It contains ECMWF-IFS ensemble forecasts (50+1 members) over the Netherlands at 6-h time resolution.
#check combined_raw_2d/2t_year data
#2d = dew point temperature
#2t = 2-meter temperature
#NetCDF data type

## There is an issue with how the dates are read in from the netcdf files. The order is mixed up, must look at the validtime to resolve this known issue. 

## Some varification and test for our dataset (ensemble forecasts)

```{r}
#read netcdf file
t2m_nc <- nc_open("data/ToSend-01-20-2025/combined_raw_2t_2021.nc") # temp data
td2m_nc <- nc_open("data/ToSend-01-20-2025/combined_raw_2d_2021.nc") #dew point data

#list all variables in this data set
names(t2m_nc$var) 
names(td2m_nc$var)

#get data
T2 <- ncvar_get(t2m_nc, "x2t")  # temp in Kelvin
Td <- ncvar_get(td2m_nc, "x2d") # dew point temperature

step <- ncvar_get(t2m_nc, "step") #Lead times
validTime_raw <- ncvar_get(t2m_nc, "validTime") ## ?? no idea what are those number means for date
#might be minute offsets from a reference time but dont know reference time
#validTime_raw

#close netcdfs
nc_close(t2m_nc)
nc_close(td2m_nc)

summary(T2)
summary(Td)

# dim(T2) # result: 38 41 51 730
# #str(t2m_nc)
# 
# validTime_raw
# 
# dim(t2m_nc)
# dim(T2)
# t2m_nc[[1]]
# 
# T2[1,1:41,1,1]
# 
# # From our meeting with Kiri
# names(t2m_nc$dim)
# t2m_nc$dim$runtime
# table(t2m_nc$dim$runtime$vals)
# t2m_nc$dim$step
# 
# # Making sense of meeting with Kir
str_data_reference_date = t2m_nc$dim$runtime$units
data_reference_date = as_date("2021-01-31")
# #TODO: automate this somehow
date_refs = data_reference_date + t2m_nc$dim$runtime$vals
# 
date_lookup_df = data.frame(day_i = 1:length(date_refs), date = date_refs)


# # dimension 1 is the grid cell locations (these may match more than one station) (Match these using the documentation - still need to figure this out)
# # dimension 2 is the number of lead times over the 10 days (6 hours) (In the documentation)
# # dimension 3 is the number of ensemble members (50) plus 1 high resolution run
# # dimension 4 is the number of forecasts 365 * 2 (2 forecasts per day)

```
#Here is basiclly what this nc data set looks like
combined_raw_2t_2021.nc (Temperature data)
combined_raw_2d_2021.nc (Dewpoint data)

Data Structure (4D array):
[location, lead_time, ensemble_member, forecasts number(two forecasts daily)]
[38,       41,        51,              730]

Visual Representation:
┌─────────────────────────────────────────────┐
│              Year 2021 Data                 │
├─────────────────────────────────────────────┤
│  Forecast Axis (730 forecasts)                        │
│  ↓                                          │
│  forecasts 1 
         ┌─────────────────────────┐         │
│        │ Loc1  Loc2 ... Loc38   │ ← 38 locations
│        ├─────────────────────────┤         │
│        │ 0h  ┌─────────────┐    │         │
│        │ 6h  │ M1 M2...M51 │    │ ← 51 ensemble members
│        │ 12h │ Temp values │    │         │
│        │ ... │   matrix    │    │         │
│        │240h └─────────────┘    │ ← 41 lead times
│        └─────────────────────────┘         │
│                                            │
│  forecasts 2 
         ┌─────────────────────────┐         │
│        │ (same structure)        │         │
│        └─────────────────────────┘         │
│  ...                                        │
│                                             │
│  forecasts 730 
           ┌───────────────────────┐         │
│          │ (same structure)      │         │
│          └───────────────────────┘         │
└─────────────────────────────────────────────┘

Example indexing:
all_data[["2021"]]$T2[1, 1, 1, 1] = Location 1, Hour 0, Member 1, Forecast 1
all_data[["2021"]]$T2[38, 41, 51, 730] = Location 38, Hour 240, Member 51, Forecast 730

Dimension meanings:
- gridpoint: [605, 639, 674, ...] (38 station IDs)
- step: [0, 6, 12, ..., 240] (41 forecast hours)
- member: 1-50 are ensemble members, 51 is control forecast
- validTime: [timestamp1, timestamp2, ..., timestamp730] (730 forecast times)

## Start visualization(test example created by Kate)
```{r}
lead_times_hours = seq(0, 240, length.out = 41)#

ggplot() + 
  geom_line(aes(x = lead_times_hours, T2[1,1:41,1,1])) + 
  geom_line(aes(x = lead_times_hours, T2[1,1:41,2,1]), col = "blue") +
  geom_line(aes(x = lead_times_hours, T2[1,1:41,3,1]), col = "red") 

raw_forecast_data = T2; loc_i = 1; day_i = 1
tidy_forecast <- function(raw_forecast_data, day_i, loc_i){
  daily_forecast = raw_forecast_data[loc_i, 1:41, 1:51, day_i] |>
    as.data.frame()
  names(daily_forecast) = paste0("M", 1:ncol(daily_forecast))
  daily_forecast = daily_forecast |>
    mutate(lead_time_hrs = seq(0, 240, length.out = 41)) |>
    pivot_longer(cols = 1:50, names_to = "Member", values_to = "Forecast_value")
  #TODO: fix this so columns aren't hard coded
  return(daily_forecast)
}

example_day = tidy_forecast(T2, 1, 1)
example_day

ggplot(example_day) + 
  geom_line(aes(x = lead_time_hrs, y = Forecast_value, group = Member), alpha = 0.6, col = "gray")


#TODO: automate this somehow
date_refs = data_reference_date + t2m_nc$dim$runtime$vals 

date_lookup_df = data.frame(day_i = 1:length(date_refs), date = date_refs)
date_lookup_df
```
