---
title: "wow_data"
author: "Wenkai_Zhong"
date: "2025-06-17"
output: html_document
---
```{r}
knitr::opts_chunk$set(echo = TRUE)
#change R language to english
Sys.setlocale("LC_TIME", "English")
#rm(list = ls())

library(here)       
library(tidyverse)  
library(ncdf4) 

```
# 1. different dates have been observed by different stations

# 2. only limit number of stations has recorded WetBulbTemperature_Celsius

# 3. 2021 data has different varaible name comapre to 22 and 23 data like ReportEndDateTime and LocalReportEndDateTime

# 4. 2021 data does not have ExternalSiteId,

#import data function
```{r}
import_WOW_day <- function(date_string) {
  # Parse date
  parts <- strsplit(date_string, "-")[[1]]
  year <- parts[1]
  month <- parts[2]
  day <- parts[3]
  
  cat("Importing WOW data:", date_string, "\n")
  
  all_data <- list()
  successful_hours <- c()
  failed_hours <- c()
  
  # Set path based on year
  if (year == "2021") {
    folder <- here("data", paste0("WOW_", year))
    file_ext <- "csv"
    
    # Loop through 00-23 hour files
    for (hour in 0:23) {
      hour_str <- sprintf("%02d", hour)
      # 修正文件名格式：WOW_NL_YYYYMMDD00.csv
      file_name <- paste0("WOW_NL_", year, month, day, hour_str, ".", file_ext)
      file_path <- file.path(folder, file_name)
      
      # Debug: 打印要查找的文件名
      if (hour == 0) {  # 只打印第一个，避免太多输出
        cat("Looking for file:", file_name, "\n")
      }
      
      if (file.exists(file_path)) {
        tryCatch({
          data <- read.csv2(file_path, stringsAsFactors = FALSE)
          if (nrow(data) > 0) {  # 只有当数据不为空时才添加
            all_data[[length(all_data) + 1]] <- data
            successful_hours <- c(successful_hours, hour)
          } else {
            failed_hours <- c(failed_hours, hour)
          }
        }, error = function(e) {
          cat("Error reading", file_name, ":", e$message, "\n")
          failed_hours <- c(failed_hours, hour)
        })
      } else {
        failed_hours <- c(failed_hours, hour)
      }
    }
    
  } else if (year %in% c("2022", "2023")) {
    library(jsonlite)
    folder <- here("data", paste0("WOW_", year), year)
    file_ext <- "json"
    
    # Loop through 00-23 hour files
    for (hour in 0:23) {
      hour_str <- sprintf("%02d", hour)
      # 2022-2023年也使用相同的文件名格式
      file_name <- paste0("WOW_NL_", year, month, day, hour_str, ".", file_ext)
      file_path <- file.path(folder, file_name)
      
      if (file.exists(file_path)) {
        tryCatch({
          # Check file size
          if (file.info(file_path)$size == 0) {
            failed_hours <- c(failed_hours, hour)
            next
          }
          
          # Read JSON
          json_data <- fromJSON(file_path)
          
          # Extract data
          if (!is.null(json_data$Object)) {
            all_data[[length(all_data) + 1]] <- json_data$Object
            successful_hours <- c(successful_hours, hour)
          } else {
            failed_hours <- c(failed_hours, hour)
          }
          
        }, error = function(e) {
          failed_hours <- c(failed_hours, hour)
        })
      } else {
        failed_hours <- c(failed_hours, hour)
      }
    }
  } else {
    cat("Unsupported year:", year, "\n")
    return(NULL)
  }
  
  # Summary
  cat("\nSummary:\n")
  cat("  Successfully read:", length(successful_hours), "hours of data\n")
  if (length(failed_hours) > 0) {
    cat("  Failed/Missing:", length(failed_hours), "hours:", paste(failed_hours, collapse=", "), "\n")
  }
  
  # Combine all files
  if (length(all_data) > 0) {
    combined_data <- tryCatch({
      do.call(rbind, all_data)
    }, error = function(e) {
      dplyr::bind_rows(all_data)
    })
    
    # 检查是否真的有数据
    if (nrow(combined_data) == 0) {
      cat("Warning: Combined data has 0 rows\n")
      return(NULL)
    }
    
    # Remove unnecessary columns based on year
    if (year == "2021") {
      # For 2021, remove columns that don't exist in JSON format
      columns_to_remove <- c("SiteId", "Id", "ImageBlobPath")
      combined_data <- combined_data %>%
        select(-any_of(columns_to_remove))
      
      # Handle 2021's different datetime format
      # LocalReportEndDateTime is in format like "15-07-2021 01:49:56"
      combined_data <- combined_data %>%
        mutate(
          # Convert LocalReportEndDateTime to POSIXct
          LocalReportEndDateTime = as.POSIXct(LocalReportEndDateTime, 
                                            format = "%d-%m-%Y %H:%M:%S", 
                                            tz = "Europe/Amsterdam"),
          # Convert to UTC and create ReportEndDateTime if it doesn't exist
          ReportEndDateTime = if("ReportEndDateTime" %in% names(.)) {
            as.POSIXct(ReportEndDateTime, format = "%Y-%m-%dT%H:%M:%S", tz = "UTC")
          } else {
            # Convert local time to UTC
            with_tz(LocalReportEndDateTime, "UTC")
          },
          # Handle CreatedDateTime
          CreatedDateTime = as.POSIXct(CreatedDateTime, 
                                     format = "%d-%m-%Y %H:%M:%S", 
                                     tz = "Europe/Amsterdam") %>%
                          with_tz("UTC")
        )
      
      # If ReportStartDateTime doesn't exist, create it (10 minutes before ReportEndDateTime)
      if (!"ReportStartDateTime" %in% names(combined_data)) {
        combined_data <- combined_data %>%
          mutate(ReportStartDateTime = ReportEndDateTime - 600) # 10 minutes
      }
      
    } else {
      # For 2022-2023, remove these columns if they exist
      columns_to_remove <- c("SiteId", "Id", "UserId", "ImageBlobPath")
      combined_data <- combined_data %>%
        select(-any_of(columns_to_remove))
      
      # Convert time columns for 2022-2023 (ISO format with timezone)
      combined_data <- combined_data %>%
        mutate(
          ReportStartDateTime = as.POSIXct(ReportStartDateTime, 
                                         format = "%Y-%m-%dT%H:%M:%S", 
                                         tz = "UTC"),
          ReportEndDateTime = as.POSIXct(ReportEndDateTime, 
                                       format = "%Y-%m-%dT%H:%M:%S", 
                                       tz = "UTC"),
          CreatedDateTime = as.POSIXct(CreatedDateTime, 
                                     format = "%Y-%m-%dT%H:%M:%S", 
                                     tz = "UTC")
        )
    }
    
    # Ensure we have consistent column names across years
    # Remove LocalReportEndDateTime as we've converted it to UTC
    combined_data <- combined_data %>%
      select(-any_of("LocalReportEndDateTime"))
    
    cat("  Total rows:", nrow(combined_data), "\n")
    cat("  Columns:", paste(names(combined_data)[1:min(10, length(names(combined_data)))], collapse=", "), 
        if(length(names(combined_data)) > 10) "...\n" else "\n")
    
    return(combined_data)
    
  } else {
    cat("No data successfully read\n")
    return(NULL)
  }
}


# Test with both years
data_2021 <- import_WOW_day("2021-07-22")
data_2022 <- import_WOW_day("2022-07-05")

data_2021
data_2022
```

#only return read from station close to target coord
```{r}
library(geosphere)
library(dplyr)

import_WOW_nearest_stations <- function(date_string, target_lat, target_lon, n_stations = 5) {
  
  # Import WOW data
  wow_data <- import_WOW_day(date_string)
  
  if (is.null(wow_data) || nrow(wow_data) == 0) {
    cat("Error: No WOW data available for", date_string, "\n")
    return(NULL)
  }
  
  # Check which station ID column is available
  station_id_col <- NULL
  if ("ExternalSiteId" %in% names(wow_data)) {
    station_id_col <- "ExternalSiteId"
  } else if ("SiteId" %in% names(wow_data)) {
    station_id_col <- "SiteId"
  } else if ("StationId" %in% names(wow_data)) {
    station_id_col <- "StationId"
  } else if ("SiteName" %in% names(wow_data)) {
    # For 2021 data, use SiteName as identifier
    station_id_col <- "SiteName"
  } else {
    # If no ID column found, create one based on lat/lon combination
    cat("Warning: No station ID column found. Creating ID from coordinates.\n")
    wow_data <- wow_data %>%
      mutate(StationId = paste(Latitude, Longitude, sep = "_"))
    station_id_col <- "StationId"
  }
  
  cat("Using", station_id_col, "as station identifier\n")
  
  # Rename the station ID column to a standard name for easier processing
  wow_data <- wow_data %>%
    rename(StationId = !!sym(station_id_col))
  
  # Get unique stations with their coordinates and calculate distances
  station_info <- wow_data %>%
    mutate(
      Latitude = as.numeric(Latitude),
      Longitude = as.numeric(Longitude)
    ) %>%
    filter(!is.na(Latitude) & !is.na(Longitude)) %>%
    group_by(StationId) %>%
    summarise(
      Latitude = first(Latitude),
      Longitude = first(Longitude),
      n_obs = n(),  # record how many observations per station
      .groups = 'drop'
    ) %>%
    mutate(
      distance_km = distHaversine(
        cbind(Longitude, Latitude),
        cbind(target_lon, target_lat)
      ) / 1000
    )
  
  # Check if we have any valid stations
  if (nrow(station_info) == 0) {
    cat("Error: No valid stations with coordinates found\n")
    return(NULL)
  }
  
  # Adjust n_stations if fewer stations are available
  n_available <- min(n_stations, nrow(station_info))
  if (n_available < n_stations) {
    cat("Note: Only", n_available, "stations available (requested", n_stations, ")\n")
  }
  
  # Get IDs of nearest n stations
  nearest_station_ids <- station_info %>%
    arrange(distance_km) %>%
    slice_head(n = n_available) %>%
    pull(StationId)
  
  # Filter original data to only include observations from nearest stations
  nearest_obs <- wow_data %>%
    filter(StationId %in% nearest_station_ids) %>%
    mutate(
      Latitude = as.numeric(Latitude),
      Longitude = as.numeric(Longitude)
    ) %>%
    # Add distance information
    left_join(
      station_info %>% select(StationId, distance_km),
      by = "StationId"
    ) %>%
    rename(distance_to_target_km = distance_km) %>%
    mutate(
      target_lat = target_lat,
      target_lon = target_lon
    ) %>%
    arrange(distance_to_target_km, ReportEndDateTime)
  
  # Rename StationId back to original column name if needed
  if (station_id_col != "StationId") {
    nearest_obs <- nearest_obs %>%
      rename(!!sym(station_id_col) := StationId)
  }
  
  # Print summary
  cat("\nSummary for", date_string, "\n")
  cat("Found", nrow(nearest_obs), "observations from", n_available, "nearest stations\n")
  
  if (nrow(nearest_obs) > 0) {
    cat("Distance range:", round(min(nearest_obs$distance_to_target_km), 2), "-", 
        round(max(nearest_obs$distance_to_target_km), 2), "km\n")
    
    # Show station details
    station_summary <- nearest_obs %>%
      group_by(!!sym(station_id_col), distance_to_target_km) %>%
      summarise(
        observations = n(),
        .groups = 'drop'
      ) %>%
      arrange(distance_to_target_km)
    
    cat("\nStation details:\n")
    print(station_summary)
  }
  
  return(nearest_obs)
}

# Test with both years
amsterdam_stations_2021 <- import_WOW_nearest_stations("2021-01-31", 52.37, 4.90, n_stations = 5)
amsterdam_stations_2022 <- import_WOW_nearest_stations("2022-07-15", 52.37, 4.90, n_stations = 5)

amsterdam_stations_2021
amsterdam_stations_2022

#####time is not continuous
```


#find station information in a specific date
```{r}
get_unique_wow_stations <- function(date_str) {
  # import date
  data_day <- import_WOW_day(date_str)
  
  # extract station info
  unique_stations <- data_day %>%
    select(ExternalSiteId,Latitude, Longitude, Height) %>%
    mutate(
      site_id = ExternalSiteId,
      Latitude = as.numeric(Latitude),
      Longitude = as.numeric(Longitude),
      Height = as.numeric(Height)
    ) %>%
    distinct()
  return(unique_stations)
}

unique_stations <- get_unique_wow_stations("2022-07-15")

unique_stations
```


