```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#change R language to english
Sys.setlocale("LC_TIME", "English")


#install.packages("R.utils")
library(R.utils)
#install.packages("ggplot2")
library(ggplot2)
#install.packages("patchwork")
library(patchwork)
#install.packages("lubridate")
library(lubridate)
#install.packages("here")
library(here)
#install.packages("ncdf4")
library(ncdf4)
#install.packages("ggrepel")
library(ggrepel)
#install.packages("tidyverse")
library(tidyverse)
#install.packages("plotly")
library(plotly)
#library(sf)
#library(rnaturalearth)

# creat .gitignore file to avoid upload data(too large)
cat("# Ignore all data files
data/
*.RData
*.Rhistory
.Rproj.user/
.RDataTmp*
", file = ".gitignore")
```

## Reading in the netcdf

# Model: These are the files starting with "combined_raw_". It contains ECMWF-IFS ensemble forecasts (50+1 members) over the Netherlands at 6-h time resolution.
#check combined_raw_2d/2t_year data
#2d = dew point temperature
#2t = 2-meter temperature
#NetCDF data type

#Here is basiclly what this nc data set looks like
combined_raw_2t_2021.nc (Temperature data)
combined_raw_2d_2021.nc (Dewpoint data)

Data Structure (4D array):
[location, lead_time, ensemble_member, forecasts number(two forecasts daily)]
[38,       41,        51,              730]

Visual Representation:
┌─────────────────────────────────────────────┐
│              Year 2021 Data                 │
├─────────────────────────────────────────────┤
│  Forecast Axis (730 forecasts)                        │
│  ↓                                          │
│  forecasts 1 
         ┌─────────────────────────┐         │
│        │ Loc1  Loc2 ... Loc38   │ ← 38 locations
│        ├─────────────────────────┤         │
│        │ 0h  ┌─────────────┐    │         │
│        │ 6h  │ M1 M2...M51 │    │ ← 51 ensemble members
│        │ 12h │ Temp values │    │         │
│        │ ... │   matrix    │    │         │
│        │240h └─────────────┘    │ ← 41 lead times
│        └─────────────────────────┘         │
│                                            │
│  forecasts 2 
         ┌─────────────────────────┐         │
│        │ (same structure)        │         │
│        └─────────────────────────┘         │
│  ...                                        │
│                                             │
│  forecasts 730 
           ┌───────────────────────┐         │
│          │ (same structure)      │         │
│          └───────────────────────┘         │
└─────────────────────────────────────────────┘

Example indexing:
all_data[["2021"]]$T2[1, 1, 1, 1] = Location 1, Hour 0, Member 1, Forecast 1
all_data[["2021"]]$T2[38, 41, 51, 730] = Location 38, Hour 240, Member 51, Forecast 730

Dimension meanings:
- gridpoint: [605, 639, 674, ...] (38 station IDs)
- step: [0, 6, 12, ..., 240] (41 forecast hours)
- member: 1-50 are ensemble members, 51 is control forecast
- validTime: [timestamp1, timestamp2, ..., timestamp730] (730 forecast times)

##after test and some preliminary research,we start to import whole dataset
##functions that help us to extract data from nc files
```{r}
#rm(list = ls())
#use example: temp_2021 <- read_data(2021, "2t")
read_data <- function(year, var_type, data_dir = here("data", "ToSend-01-20-2025")) {
  # Build filename
  filename <- file.path(data_dir, paste0("combined_raw_", var_type, "_", year, ".nc"))
  
  # Open file
  nc <- nc_open(filename)
  
  # Read main variable
  var_name <- paste0("x", var_type)  # x2t or x2d
  data <- ncvar_get(nc, var_name)
  
  # Read other information
  step <- ncvar_get(nc, "step")
  validTime <- ncvar_get(nc, "validTime")
  gridpoint <- ncvar_get(nc, "gridpoint")
  member <- if("member" %in% names(nc$dim)) ncvar_get(nc, "member") else NULL
  
  runtime_info <- nc$dim$runtime
  
  # Close file
  nc_close(nc)
  
  # Return
  return(list(
    data = data,
    step = step,
    validTime = validTime,
    gridpoint = gridpoint,
    member = member,
    runtime_units = runtime_info$units,
    runtime_vals = runtime_info$vals
  ))
}

# Test
temp_2023 <- read_data(2023, "2t")  # Read combined_raw_2t_2021.nc
# dewp_2021 <- read_data(2021, "2d")  # Read combined_raw_2d_2021.nc
# temp_2023_start_time <- temp_2023$runtime_units
# temp_2023_start_time
# dewp_2021_start_time <- dewp_2021$runtime_units
# dewp_2021_start_time
```

###function that help us to convert readed data to tidy format
```{r}
#example：example_day <- tidy_formation(temp_2021, gridpoint_idx = 1, validtime_idx = 100)
tidy_formation <- function(data, gridpoint_idx, validtime_idx) {
  # Extract reference datetime from runtime_units (e.g., "days since 2021-01-31 00:00:00")
  ref_datetime_str <- gsub(".*since\\s+([0-9-]+\\s+[0-9:]+).*", "\\1", data$runtime_units)
  ref_datetime <- ymd_hms(ref_datetime_str)
  
  # validTime[1, validtime_idx] gives hours from reference time for this forecast initialization
  init_hours_from_ref <- data$validTime[1, validtime_idx]
  forecast_init_datetime <- ref_datetime + (init_hours_from_ref * 3600)

  # Extract data slice for [gridpoint, step, member, validtime]
  data_slice <- data$data[gridpoint_idx, , , validtime_idx]
  df <- as.data.frame(t(data_slice))
  names(df) <- paste0("Step_", 0:40)
  df$Member <- paste0("M", seq_len(nrow(df)))
  
  # Create lead time hours vector (0 to 240 hours in 41 steps)
  lead_times_hours <- seq(0, 240, length.out = 41)
  
  # Pivot to long format and add metadata
  tidy_df <- df %>%
    pivot_longer(
      cols = starts_with("Step_"),
      names_to = "Step_idx",
      values_to = "Forecast_value"
    ) %>%
    mutate(
      Step_idx = as.numeric(gsub("Step_", "", Step_idx)),
      lead_time_hrs = lead_times_hours[Step_idx + 1],  # +1 because R is 1-indexed
      Gridpoint_idx = gridpoint_idx,
      ValidTime_idx = validtime_idx,
      Gridpoint = data$gridpoint[gridpoint_idx],
      Forecast_init_datetime = forecast_init_datetime,
      # Valid time = initialization time + lead time
      Valid_datetime = forecast_init_datetime + (lead_time_hrs * 3600),
    )
  
  return(tidy_df)
}

# Example usage and verification
# # Convert specific validtime to tidy format
temp_example_day <- tidy_formation(temp_2023, gridpoint_idx = 1, validtime_idx = 1)
temp_example_day
# 
# dewp_example_day <- tidy_formation(dewp_2021, gridpoint_idx = 1, validtime_idx = 1)
# dewp_example_day
```

##function that we only input forecats_time and gridpoint to generate tidy forecast table
```{r}
# Helper function to find runtime index for a given date

# Helper functions
find_runtime_index <- function(data, target_datetime) {
  # Check if input includes time or just date
  has_time <- grepl("\\d{2}:\\d{2}", target_datetime)
  
  # Parse reference datetime
  ref_datetime_str <- gsub(".*since\\s+([0-9-]+\\s+[0-9:]+).*", "\\1", data$runtime_units)
  ref_datetime <- as.POSIXct(ref_datetime_str, tz = "UTC")
  
  if (has_time) {
    # If time is specified, find exact forecast
    target_dt <- as.POSIXct(target_datetime, tz = "UTC")
    
    # Calculate hours since reference
    hours_since_ref <- as.numeric(difftime(target_dt, ref_datetime, units = "hours"))
    
    # Find matching index in validTime[1,]
    idx <- which(abs(data$validTime[1,] - hours_since_ref) < 0.1)
    
    if (length(idx) == 0) {
      # No exact match, find closest
      idx <- which.min(abs(data$validTime[1,] - hours_since_ref))
      warning(paste("No exact match for", target_datetime, 
                    ". Returning closest forecast at index", idx))
    } else if (length(idx) > 1) {
      # Multiple matches (shouldn't happen), take first
      idx <- idx[1]
      warning(paste("Multiple matches found for", target_datetime, 
                    ". Returning first match at index", idx))
    }
    
    return(idx)
    
  } else {
    # If only date is specified, return all forecasts for that day
    target_date <- as.Date(target_datetime)
    days_since_ref <- as.numeric(target_date - as.Date(ref_datetime))
    
    # Calculate hours for 00:00 and 12:00 UTC
    hours_00 <- days_since_ref * 24
    hours_12 <- days_since_ref * 24 + 12
    
    # Find indices
    indices_00 <- which(abs(data$validTime[1,] - hours_00) < 0.1)
    indices_12 <- which(abs(data$validTime[1,] - hours_12) < 0.1)
    
    all_indices <- c(indices_00, indices_12)
    
    # Sort by initialization time
    all_indices <- all_indices[order(data$validTime[1, all_indices])]
    
    # Print info about found forecasts
    for (i in seq_along(all_indices)) {
      init_hours <- data$validTime[1, all_indices[i]]
      init_time <- ref_datetime + (init_hours * 3600)
    }
    
    return(all_indices)
  }
}

# Test examples
# Test 1: Find specific forecast with time
# test1 <- find_runtime_index(temp_2023, "2023-01-21 00:00:00")
# test2 <- find_runtime_index(temp_2023, "2023-01-21 12:00:00")
# test3 <- find_runtime_index(dewp_2021, "2021-05-17 00:00:00")
# test4 <- find_runtime_index(dewp_2021, "2021-01-31 00:00:00")
# test1 
# test2 
# test3 
# test4 

find_gridpoint_index <- function(data, gridpoint_id) {
  idx <- which(data$gridpoint == gridpoint_id)
  if (length(idx) == 0) {
    stop("Gridpoint ID ", gridpoint_id, " not found")
  }
  return(idx)
}

# test_grid_1 = find_gridpoint_index(temp_2023, 605)
# test_grid_1
# test_grid_2 = find_gridpoint_index(dewp_2021, 605)
# test_grid_2

```

#check forecasts that be made in a specific date
```{r}

# Main function
tidy_table_ultimate <- function(forecast_datetime, gridpoint_id) {
  # Find relative data set
  year <- lubridate::year(as.POSIXct(forecast_datetime))
  
  temp_data <- read_data(year, "2t")
  dewp_data <- read_data(year, "2d")
  
  # Step 1: Find the runtime index for temperature and dewpoint
  runtime_temp_idx <- find_runtime_index(temp_data, forecast_datetime)
  runtime_dewp_idx <- find_runtime_index(dewp_data, forecast_datetime)
  
  # Check if unique runtime index was found
  if (length(runtime_temp_idx) != 1 || length(runtime_dewp_idx) != 1) {
    stop(paste("Could not uniquely identify forecast time", forecast_datetime, 
               "in one or both datasets. Please check time format and data."))
  }
  
  # Step 2: Find the gridpoint index
  grid_idx_temp <- find_gridpoint_index(temp_data, gridpoint_id)
  grid_idx_dewp <- find_gridpoint_index(dewp_data, gridpoint_id)
  
  # Step 3: Extract tidy data
  temp_tidy <- tidy_formation(temp_data, grid_idx_temp, runtime_temp_idx)
  dewp_tidy <- tidy_formation(dewp_data, grid_idx_dewp, runtime_dewp_idx)
  
  # Step 4: Combine and format
  tidy_combined <- temp_tidy %>%
    rename(Temperature_K = Forecast_value) %>%
    mutate(
      DewPoint_K = dewp_tidy$Forecast_value,
      # Convert to Celsius
      Temperature_C = Temperature_K - 273.15,
      DewPoint_C = DewPoint_K - 273.15,
      # Add time information
      Forecast_init_date = as.Date(Forecast_init_datetime),
      Forecast_init_time = format(Forecast_init_datetime, "%H:%M:%S"),
      Valid_date = as.Date(Valid_datetime),
      Valid_time = format(Valid_datetime, "%H:%M:%S"),
      # Gridpoint ID
      Gridpoint_ID = gridpoint_id
    ) %>%
    select(
      Member, 
      lead_time_hrs,
      Forecast_init_datetime,
      Forecast_init_date,
      Forecast_init_time,
      Valid_datetime,
      Valid_date,
      Valid_time,
      Temperature_K,
      Temperature_C,
      DewPoint_K,
      DewPoint_C,
      Gridpoint_ID,
      everything()
    )
  
  return(tidy_combined)
}


# Test the function
# tidy_result_2021_01_31_00_G605 <- tidy_table_ultimate("2021-05-17 00:00:00", 605)
# tidy_result_2021_01_31_00_G605
# # View the first few rows
# head(tidy_result_2021_01_31_00_G605)
# 
# # Check structure
# str(tidy_result_2021_01_31_00_G605)
# 
# # Test with different dates and times
# tidy_result_2021_01_31_12_G605 <- tidy_table_ultimate("2021-01-31 12:00:00", 605)
# tidy_result_2021_08_13_00_G605 <- tidy_table_ultimate("2023-01-21 00:00:00", 605)
# tidy_result_2021_08_13_00_G605
```


##import meta data to find locations(lon and lat) for gridpoints and their corresponding stations
```{r}
#import meta data
prediction_metadata <- read.csv(here("data", "ToSend-01-20-2025", "prediction_meta.csv"))
sta_gp_metadata <- read.csv(here("data", "ToSend-01-20-2025", "sta_gp_metadata.csv"))
sta_gp_metadata <- sta_gp_metadata %>%
  select(-X)

# all grid points appeared in our all_data data set
unique_gridpoints <- c(605, 639, 674, 676, 680, 715, 745, 747, 787, 818, 819, 821, 854, 857, 891, 896, 935, 965, 967, 969, 971, 1001, 1002, 1003, 1041, 1073, 1074, 1080, 1111, 1112, 1114, 1118, 1147, 1148, 1154, 1187, 1193, 1269)

#match them with meta

gridpoint_lookup <- data.frame(
  data_index = 1:length(unique_gridpoints),
  gridpoint = unique_gridpoints
)

# merge
gridpoint_lookup <- merge(gridpoint_lookup, prediction_metadata,
                         by = "gridpoint",
                         all.x = TRUE)%>%select(-data_index)
gridpoint_lookup <- gridpoint_lookup %>%
  left_join(sta_gp_metadata, by = c("gridpoint" = "gp"))%>%
  select(-sta_id,
         gp_lat = gp_lat.x, 
         gp_lon = gp_lon.x, 
         everything(),
         -gp_lat.y, 
         -gp_lon.y)

# one-to-many relationship when joining two datasets where one gridpoint maps to multiple stations, causing duplicate rows in the merged data 
gridpoint_station_table = gridpoint_lookup %>% 
  mutate(
    # determine primary or secondary
    station_type = ifelse(station_id == sta_id, "primary", "secondary")
  )%>%
  mutate(
    is_coast = ifelse(station_type == "secondary", NA, is_coast),
    clc_dist0 = ifelse(station_type == "secondary", NA, clc_dist0),
    dist = ifelse(station_type == "secondary", NA, dist)
  )%>%
  select(-station_id)

gridpoint_station_table

## Verify guess
## There are 38 grid point locations in the data but 46 stations so Kiri guessed that there may be more than one station per grid point - this is worth checking. We will need to follow up about the mapping from grid points to stations. 

station_count <- gridpoint_station_table %>%
  group_by(gridpoint) %>%
  summarise(
    n_stations = sum(!is.na(sta_id)),  
  ) %>%
  arrange(desc(n_stations))  

station_count
length(station_count$gridpoint)
sum(station_count$n_stations)

# only found 43 stations in 38 grid points

# In addition, for some grid points like 819 , it has 2 relate stations with different station_id, sta_lat and sta_lon
```
#city information
```{r}
cities <- data.frame(
    city = c("Amsterdam", "Rotterdam", "Utrecht", "The Hague", "Eindhoven", 
             "Groningen", "Tilburg", "Almere", "Breda", "Nijmegen",
             "Haarlem", "Arnhem", "Zaanstad", "Apeldoorn", "Enschede",
             "Amersfoort", "Zwolle", "Dordrecht", "Leiden", "Maastricht",
             "Delft", "Alkmaar", "Leeuwarden", "Middelburg", "Den Helder"),
    city_lat = c(52.37, 51.92, 52.09, 52.08, 51.44,
                 53.22, 51.56, 52.37, 51.59, 51.84,
                 52.38, 51.98, 52.44, 52.21, 52.22,
                 52.16, 52.51, 51.81, 52.16, 50.85,
                 52.01, 52.63, 53.20, 51.50, 52.96),
    city_lon = c(4.90, 4.48, 5.12, 4.30, 5.48,
                 6.57, 5.08, 5.22, 4.78, 5.87,
                 4.64, 5.90, 4.83, 5.97, 6.90,
                 5.39, 6.09, 4.67, 4.49, 5.69,
                 4.36, 4.75, 5.80, 3.61, 4.76),
    population_rank = c(1, 2, 4, 3, 5,
                        6, 7, 8, 9, 10,
                        11, 12, 13, 14, 15,
                        16, 17, 18, 19, 20,
                        21, 22, 23, 24, 25),
    region = c("North Holland", "South Holland", "Utrecht", "South Holland", "North Brabant",
               "Groningen", "North Brabant", "Flevoland", "North Brabant", "Gelderland",
               "North Holland", "Gelderland", "North Holland", "Gelderland", "Overijssel",
               "Utrecht", "Overijssel", "South Holland", "South Holland", "Limburg",
               "South Holland", "North Holland", "Friesland", "Zeeland", "North Holland"),
    elevation_m = c(-2, 0, 5, 1, 19,
                    0, 14, -4, 3, 30,
                    2, 15, 2, 30, 48,
                    10, 2, 0, 0, 49,
                    1, 1, 0, 2, 1)
  )
```

#tidy_forecast_with_station_grid_city_location and closest cities
```{r}
tidy_forecast_with_station_grid_city_location <- function(target_datetime, gridpoint_id, station_table = NULL) {
  
  # Use input to find related data set
  year <- lubridate::year(as.POSIXct(target_datetime))
  
  temp_data <- read_data(year, "2t")
  dewp_data <- read_data(year, "2d")
  if (is.null(station_table)) station_table <- gridpoint_station_table
  
  # Get forecast data using tidy_table_ultimate
  forecast_data <- tidy_table_ultimate(
    forecast_datetime = target_datetime, 
    gridpoint_id = gridpoint_id
  )
  
  # Add station information
  forecast_with_station <- forecast_data %>%
    left_join(
      station_table %>%
        select(gridpoint, sta_id, sta_lat, sta_lon, dist, is_coast, 
               gp_lat, gp_lon, clc_dist0),
      by = c("Gridpoint_ID" = "gridpoint")
    ) %>%
    # Rename columns for clarity
    rename(
      station_id = sta_id,
      station_lat = sta_lat,
      station_lon = sta_lon,
      gridpoint_to_station_dist = dist,
      gridpoint_lat = gp_lat,
      gridpoint_lon = gp_lon,
      coastal_distance = clc_dist0
    )
  
  # Add nearest city information
  # Get unique station for this gridpoint to avoid redundant calculations
  station_coords <- forecast_with_station %>%
    select(station_lat, station_lon) %>%
    distinct() %>%
    slice(1)  # Should only be one station per gridpoint
  
  if(nrow(station_coords) > 0 && !is.na(station_coords$station_lat)) {
    # Calculate distances to all cities
    distances <- geosphere::distHaversine(
      cbind(station_coords$station_lon, station_coords$station_lat),
      cbind(cities$city_lon, cities$city_lat)
    ) / 1000  # Convert to km
    
    # Find nearest city
    nearest_idx <- which.min(distances)
    
    # Add city information to forecast data
    forecast_with_station <- forecast_with_station %>%
      mutate(
        nearest_city = cities$city[nearest_idx],
        nearest_city_lat = cities$city_lat[nearest_idx],
        nearest_city_lon = cities$city_lon[nearest_idx],
        nearest_city_distance_km = distances[nearest_idx],
        nearest_city_population_rank = cities$population_rank[nearest_idx],
        nearest_city_region = cities$region[nearest_idx],
        nearest_city_elevation_m = cities$elevation_m[nearest_idx],
        station_elevation_m = NA  # Placeholder - could be added if you have station elevation data
      )
  } else {
    # Add NA columns if no station coordinates
    forecast_with_station <- forecast_with_station %>%
      mutate(
        nearest_city = NA,
        nearest_city_lat = NA,
        nearest_city_lon = NA,
        nearest_city_distance_km = NA,
        nearest_city_population_rank = NA,
        nearest_city_region = NA,
        nearest_city_elevation_m = NA,
        station_elevation_m = NA
      )
  }
  
  # Reorder columns for better readability
  forecast_with_station <- forecast_with_station %>%
    select(
      # Forecast timing info
      Member, lead_time_hrs,
      Forecast_init_datetime, 
      Valid_datetime, 
      # Weather values
      Temperature_K, Temperature_C, DewPoint_K, DewPoint_C,
      # Location info - Station
      Gridpoint_ID, station_id, 
      station_lat, station_lon,
      # Location info - Nearest City
      nearest_city, nearest_city_distance_km,
      nearest_city_lat, nearest_city_lon,
      nearest_city_region, nearest_city_population_rank,
      nearest_city_elevation_m, station_elevation_m,
      # Grid info
      gridpoint_lat, gridpoint_lon,
      gridpoint_to_station_dist,
      is_coast, coastal_distance
    )
  
  
  return(forecast_with_station)
}


# Test with specific datetime
tidy_result_2021_08_13_12_G605 <- tidy_forecast_with_station_grid_city_location(
  "2021-05-17 00:00:00",
  605
)

# Display result
tidy_result_2021_08_13_12_G605
names(tidy_result_2021_08_13_12_G605)
```

#function that input the time be forecasted and return relative tidy table with cities
```{r}
get_forecasts_for_valid_time <- function(target_valid_datetime, 
                                         gridpoint_id,
                                         max_days_back = 10,
                                         temp_data = NULL,
                                         dewp_data = NULL,
                                         station_table = NULL) {
  
  # Ensure target time is in POSIXct format
  target_time <- as.POSIXct(target_valid_datetime, tz = "UTC")
  
  # Extract year from target_valid_datetime for data loading
  year <- lubridate::year(target_time)
  
  # Load data if not provided
  if (is.null(temp_data)) temp_data <- read_data(year, "2t")
  if (is.null(dewp_data)) dewp_data <- read_data(year, "2d")
  if (is.null(station_table)) station_table <- gridpoint_station_table
  
  # Initialize results list
  all_forecasts <- list()
  
  # Loop through previous N days to find forecasts that can reach this valid time
  for (days_back in 0:max_days_back) {
    # For each day, check both 00:00 and 12:00 forecasts
    for (hour in c(0, 12)) {
      # Calculate potential forecast initialization time
      forecast_init_time <- target_time - (days_back * 24 + hour) * 3600
      forecast_datetime_str <- format(forecast_init_time, "%Y-%m-%d %H:%M:%S")
      
      # Skip if forecast time is in the future
      if (forecast_init_time > Sys.time()) next
      
      # Calculate lead time needed
      lead_time_hours <- as.numeric(difftime(target_time, forecast_init_time, units = "hours"))
      
      # Skip if lead time is beyond 240 hours (10 days) or negative
      if (lead_time_hours > 240 || lead_time_hours < 0) next
      
      tryCatch({
        # Get forecast data
        forecast_table <- tidy_forecast_with_station_grid_city_location(
          forecast_datetime_str, 
          gridpoint_id,
          station_table = station_table
        )
        
        # Filter rows where Valid_datetime matches target time
        matched_rows <- forecast_table %>%
          filter(abs(difftime(Valid_datetime, target_time, units = "secs")) < 1)
        
        # If matching rows found, add to results
        if (nrow(matched_rows) > 0) {
          matched_rows <- matched_rows %>%
            mutate(
              forecast_age_hours = lead_time_hours,
              forecast_age_days = round(lead_time_hours / 24, 1),
              forecast_origin = forecast_datetime_str
            )
          
          all_forecasts[[forecast_datetime_str]] <- matched_rows
          
          # Calculate number of ensemble members (assuming 51 total: 50 + 1 control)
          n_members <- length(unique(matched_rows$Member))
          message(paste("✓ Found forecast from", forecast_datetime_str,
                       "(", round(lead_time_hours), "hours ahead,",
                       n_members, "members)"))
        }
        
      }, error = function(e) {
        # Optionally show error for debugging
        # message(paste("  No data for", forecast_datetime_str, "-", e$message))
      })
    }
  }
  
  # Combine all results
  if (length(all_forecasts) > 0) {
    result <- bind_rows(all_forecasts) %>%
      arrange(desc(Forecast_init_datetime)) %>%
      # Add ranking by forecast recency
      mutate(
        forecast_rank = dense_rank(desc(Forecast_init_datetime))
      ) %>%
      # Reorder columns for clarity
      select(
        forecast_rank, forecast_origin, forecast_age_hours, forecast_age_days,
        Member, lead_time_hrs,
        Forecast_init_datetime, Valid_datetime,
        Temperature_K, Temperature_C, DewPoint_K, DewPoint_C,
        everything()
      )
    
    return(result)
  } else {
    warning(paste("No forecasts found for valid time:", target_valid_datetime))
    return(NULL)
  }
}


# Test the function
# Find all forecasts predicting temperature for 2021-08-15 12:00:00
system.time({forecasts_for_target <- get_forecasts_for_valid_time(
  "2022-08-15 12:00:00",
  gridpoint_id = 605,
  max_days_back = 10
)})

forecasts_for_target
```

################### ( Visualization starts here :) ######################


## find stations near cities
```{r}
# Find nearest station for each city
city_connections <- cities %>%
 rowwise() %>%
 mutate(
   # Calculate distances to all stations
   distances = list(sqrt((gridpoint_station_table$sta_lat - city_lat)^2 + 
                        (gridpoint_station_table$sta_lon - city_lon)^2) * 111),
   nearest_idx = which.min(distances),
   station_lat = gridpoint_station_table$sta_lat[nearest_idx],
   station_lon = gridpoint_station_table$sta_lon[nearest_idx],
   distance_km = round(min(distances), 1)
 )

# Create simple connection map
city_station_plot = ggplot() +
  # Connection lines
  geom_segment(data = city_connections,
               aes(x = city_lon, y = city_lat, xend = station_lon, yend = station_lat),
               alpha = 0.3) +
  
  # Primary Stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "primary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "red", size = 2) +
  
  # Secondary Stations (yellow.samll size)
  geom_point(data = gridpoint_station_table %>% 
               filter(station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat), 
             color = "gold", size = 1) +
 
 # Cities
 geom_point(data = cities,
            aes(x = city_lon, y = city_lat, size = 1/population_rank), color = "blue" ) +
 
 # Labels for major cities only
 geom_text_repel(data = cities ,
                 aes(x = city_lon, y = city_lat, label = city),
                 size = 3) +
  
 geom_text_repel(data = gridpoint_station_table ,
                 aes(x = sta_lon, y = sta_lat, label = sta_id),
                 size = 2) +
  
 labs(title = "Cities and Nearest Weather Stations",
     subtitle = "City points size is determinted by its population rank",
     x = "Longitude", y = "Latitude")+
 theme_minimal() +
 coord_fixed(1.3)+
 scale_size_continuous(guide = FALSE)

city_station_plot

ggsave(
  filename = "Cities and Nearest Weather Stations.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

```

## find stations near grid points,for some gridpoints like 819 , it has 2 relate stations but same station_id different sta_lat and sta_lon
```{r}
# Create visualization
#netherlands <- ne_countries(country = "netherlands", returnclass = "sf", scale = "medium")

gridpoint_station_map <- ggplot() +
  #geom_sf(data = netherlands, fill = NA, color = "black", size = 0.8) +
  # Connection lines
  geom_segment(data = gridpoint_station_table,
               aes(x = gp_lon, y = gp_lat, xend = sta_lon, yend = sta_lat),
               alpha = 0.3) +
  # Plot gridpoint points (using squares)
  geom_point(data = gridpoint_station_table,
             aes(x = gp_lon, y = gp_lat, shape = "Gridpoints"),
             color = "darkblue") +
  
  # Plot primary stations (red)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "primary"),
             aes(x = sta_lon, y = sta_lat, shape = "Primary Stations"),
             color = "red") +
  
  # Plot secondary stations (yellow)
  geom_point(data = gridpoint_station_table %>% 
               filter(!is.na(sta_id) & station_type == "secondary"),
             aes(x = sta_lon, y = sta_lat, shape = "Secondary Stations"),
             color = "gold") +
  
  # Set shapes
  scale_shape_manual(values = c("Gridpoints" = 15, 
                               "Primary Stations" = 16,
                               "Secondary Stations" = 17),
                     name = "Type") +
  
  # Add gridpoint labels
  geom_text_repel(data = gridpoint_station_table,
                  aes(x = gp_lon, y = gp_lat, label = gridpoint),
                  size = 2.5,
                  color = "darkblue",
                  box.padding = 0.3,
                  point.padding = 0.2,
                  max.overlaps = 20) +
  
  # Add primary station labels (red)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "primary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "red",
                  nudge_y = 0.02,
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  # Add secondary station labels (yellow)
  geom_text_repel(data = gridpoint_station_table %>% 
                    filter(!is.na(sta_id) & station_type == "secondary"),
                  aes(x = sta_lon, y = sta_lat, 
                      label = paste0("S", sta_id)),
                  size = 2,
                  color = "gold",
                  nudge_y = -0.02,  #avoid overlapping
                  box.padding = 0.2,
                  point.padding = 0.1,
                  max.overlaps = 20) +
  
  labs(title = "ECMWF Gridpoints and KNMI Stations in the Netherlands",
       subtitle = "Primary stations (red) vs Secondary stations (yellow)",
       x = "Longitude",
       y = "Latitude") +
  
  theme_minimal() +
  theme(legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))

gridpoint_station_map

ggsave(
  filename = "ECMWF Gridpoints and KNMI Stations in the Netherlands.png",
  path = "../Honours_project/graph",
  width = 822/100,  
  height = 694/100,
  dpi = 300
)

# every station is super close to its corresponding grid points
```
```{r}
#automate plot function using gridpoint_id date and members to plot temperature
auto_forecast_plot_faceted <- function(forecast_datetime, 
                                       gridpoint_id, 
                                       members = 1:51,
                                       variable = "Temperature_C",
                                       temp_data = NULL,
                                       dewp_data = NULL,
                                       station_table = NULL,
                                       show_spread = TRUE,
                                       show_mean = TRUE) {
  
  # Extract year from forecast_datetime
  forecast_time <- as.POSIXct(forecast_datetime, tz = "UTC")
  year <- lubridate::year(forecast_time)
  
  # Load data if not provided
  if (is.null(temp_data)) temp_data <- read_data(year, "2t")
  if (is.null(dewp_data)) dewp_data <- read_data(year, "2d")
  if (is.null(station_table)) station_table <- gridpoint_station_table
  
  # Get the tidy data with station info
  tidy_data <- tidy_forecast_with_station_grid_city_location(
    target_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id,
    station_table = station_table
  )
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names)
  
  # Extract station info for subtitle
  station_info <- unique(plot_data$station_id)[1]
  is_coastal <- unique(plot_data$is_coast)[1]
  coastal_dist <- round(unique(plot_data$coastal_distance)[1], 1)
  
  # Calculate ensemble statistics if needed
  if (show_spread || show_mean) {
    ensemble_stats <- plot_data %>%
      group_by(lead_time_hrs, Valid_datetime) %>%
      summarise(
        mean_val = mean(.data[[variable]], na.rm = TRUE),
        median_val = median(.data[[variable]], na.rm = TRUE),
        q25 = quantile(.data[[variable]], 0.25, na.rm = TRUE),
        q75 = quantile(.data[[variable]], 0.75, na.rm = TRUE),
        q10 = quantile(.data[[variable]], 0.10, na.rm = TRUE),
        q90 = quantile(.data[[variable]], 0.90, na.rm = TRUE),
        min_val = min(.data[[variable]], na.rm = TRUE),
        max_val = max(.data[[variable]], na.rm = TRUE),
        .groups = "drop"
      )
  }
  
  # Create base plot
  p <- ggplot(plot_data, aes(x = lead_time_hrs))
  
  # Check number of members
  n_members <- length(members)
  
  # Add ensemble spread visualization
  if (show_spread && n_members > 1) {
    p <- p +
      # 10-90 percentile range (lightest)
      geom_ribbon(data = ensemble_stats, 
                  aes(ymin = q10, ymax = q90), 
                  fill = "skyblue", alpha = 0.2) +
      # 25-75 percentile range (IQR)
      geom_ribbon(data = ensemble_stats, 
                  aes(ymin = q25, ymax = q75), 
                  fill = "steelblue", alpha = 0.3)
      # Min-max range (optional, can be noisy)
      # geom_ribbon(data = ensemble_stats, 
      #             aes(ymin = min_val, ymax = max_val), 
      #             fill = "gray90", alpha = 0.3)
  }  # This closing brace was causing the issue
  
  # Add individual member lines based on number of members
  if (n_members <= 10) {
    # Few members: use colors
    p <- p + 
      geom_line(aes(y = .data[[variable]], color = Member, group = Member), 
                size = 0.8, alpha = 0.7) +
      scale_color_viridis_d(option = "plasma", end = 0.9)
  } else if (n_members <= 25) {
    # Medium members: thinner colored lines
    p <- p + 
      geom_line(aes(y = .data[[variable]], color = Member, group = Member), 
                size = 0.5, alpha = 0.5) +
      scale_color_viridis_d(option = "viridis", guide = "none")
  } else {
    # Many members (like 51): use gray lines
    p <- p + 
      geom_line(aes(y = .data[[variable]], group = Member), 
                size = 0.3, alpha = 0.3, color = "gray60")
  }
  
  # Add ensemble mean and median
  if (show_mean && n_members > 1) {
    p <- p +
      # Ensemble mean
      geom_line(data = ensemble_stats, 
                aes(y = mean_val), 
                color = "red", size = 1.2, alpha = 0.8) +
      # Ensemble median
      geom_line(data = ensemble_stats, 
                aes(y = median_val), 
                color = "darkred", size = 1, linetype = "dashed", alpha = 0.8)
  }
  
  # Add labels and theme
  variable_label <- switch(variable,
    "Temperature_C" = "Temperature (°C)",
    "DewPoint_C" = "Dew Point (°C)",
    "Temperature_K" = "Temperature (K)",
    "DewPoint_K" = "Dew Point (K)",
    variable
  )
  
  p <- p +
    labs(
      title = paste("Ensemble Forecast initialized at", 
                   format(unique(plot_data$Forecast_init_datetime)[1], "%Y-%m-%d %H:%M UTC")),
      subtitle = paste("Gridpoint", gridpoint_id, "| Station:", station_info, 
                      "| Coastal:", ifelse(is_coastal, "Yes", "No"),
                      "| Distance to coast:", coastal_dist, "km",
                      "| Ensemble members:", n_members),
      x = "Lead Time (hours)",
      y = variable_label,
      color = if(n_members <= 10) "Member" else NULL,
      caption = if(show_mean) "Red line: ensemble mean | Dashed red: ensemble median | Blue shading: uncertainty bands" else NULL
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 11, color = "gray40"),
      plot.caption = element_text(size = 9, color = "gray50", hjust = 0),
      legend.position = if(n_members <= 10) "right" else "none",
      panel.grid.minor = element_blank(),
      panel.border = element_rect(fill = NA, color = "gray80"),
      axis.text.x = element_text(angle = 0, hjust = 0.5)
    )
  
  # Add x-axis with dates
  p <- p +
    scale_x_continuous(
      breaks = seq(0, 240, 24),
      minor_breaks = seq(0, 240, 12),
      labels = function(x) {
        dates <- unique(plot_data$Forecast_init_datetime)[1] + x*3600
        paste0("Day ", x/24, "\n", format(dates, "%m/%d"))
      }
    ) +
    coord_cartesian(xlim = c(0, max(plot_data$lead_time_hrs)))
  
  # Add reference lines for days
  p <- p +
    geom_vline(xintercept = seq(24, 240, 24), 
               alpha = 0.15, linetype = "dotted", color = "gray40")
  
  # Add annotation for spread information if shown
  if (show_spread && n_members > 1) {
    # Calculate spread at different lead times for annotation
    spread_info <- ensemble_stats %>%
      filter(lead_time_hrs %in% c(24, 120, 240)) %>%
      mutate(spread = q90 - q10) %>%
      summarise(
        mean_spread = round(mean(spread, na.rm = TRUE), 2),
        max_spread = round(max(spread, na.rm = TRUE), 2)
      )
    
    # Only add annotation if we have valid spread values
    if (!is.na(spread_info$mean_spread)) {
      p <- p +
        annotate("text", 
                 x = max(plot_data$lead_time_hrs) * 0.95, 
                 y = min(plot_data[[variable]], na.rm = TRUE) + 0.5,
                 label = paste("Mean spread (P90-P10):", spread_info$mean_spread, "°C"),
                 hjust = 1, size = 3, color = "gray40")
    }
  }
  
  return(p)
}


p1 <- auto_forecast_plot_faceted(
  "2021-01-31 00:00:00", 
  gridpoint_id = 605, 
  members = 0:50,  # Including control run (M0)
  show_spread = FALSE,
  show_mean = TRUE
)

print(p1)

```

# plot with pdf to be more clear to view the distribution
```{r}
library(patchwork)
library(ggplot2)
library(dplyr)

auto_forecast_plot_with_pdf_separate <- function(forecast_datetime, 
                                                gridpoint_id, 
                                                members = 0:50,  # Include control run
                                                variable = "Temperature_C",
                                                pdf_times = c(24, 48, 120, 240),
                                                temp_data = NULL,
                                                dewp_data = NULL,
                                                station_table = NULL) {
  
  # Extract year from forecast_datetime
  forecast_time <- as.POSIXct(forecast_datetime, tz = "UTC")
  year <- lubridate::year(forecast_time)
  
  # Load data if not provided
  if (is.null(temp_data)) temp_data <- read_data(year, "2t")
  if (is.null(dewp_data)) dewp_data <- read_data(year, "2d")
  if (is.null(station_table)) station_table <- gridpoint_station_table
  
  # Get tidy data using the corrected function
  tidy_data <- tidy_forecast_with_station_grid_city_location(
    target_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id,
    station_table = station_table
  )
  
  # Filter for selected members
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names)
  
  n_members <- length(members)
  
  # Calculate ensemble statistics for the main plot
  ensemble_stats <- plot_data %>%
    group_by(lead_time_hrs) %>%
    summarise(
      mean_val = mean(.data[[variable]], na.rm = TRUE),
      median_val = median(.data[[variable]], na.rm = TRUE),
      q25 = quantile(.data[[variable]], 0.25, na.rm = TRUE),
      q75 = quantile(.data[[variable]], 0.75, na.rm = TRUE),
      q10 = quantile(.data[[variable]], 0.10, na.rm = TRUE),
      q90 = quantile(.data[[variable]], 0.90, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Main plot with ensemble visualization
  p_main <- ggplot(plot_data, aes(x = lead_time_hrs)) +
    # Add uncertainty bands
    geom_ribbon(data = ensemble_stats, 
                aes(ymin = q10, ymax = q90), 
                fill = "lightblue", alpha = 0.3) +
    geom_ribbon(data = ensemble_stats, 
                aes(ymin = q25, ymax = q75), 
                fill = "steelblue", alpha = 0.4)
  
  # Add individual member lines
  if (n_members <= 10) {
    p_main <- p_main + 
      geom_line(aes(y = .data[[variable]], color = Member, group = Member), 
                alpha = 0.7, size = 0.6) +
      scale_color_viridis_d(option = "plasma", end = 0.9)
  } else {
    p_main <- p_main + 
      geom_line(aes(y = .data[[variable]], group = Member), 
                alpha = 0.3, color = "gray50", size = 0.3)
  }
  
  # Add ensemble mean
  p_main <- p_main +
    geom_line(data = ensemble_stats, 
              aes(y = mean_val), 
              color = "red", size = 1.2, alpha = 0.9) +
    # Add vertical lines for PDF times
    geom_vline(xintercept = pdf_times, 
               linetype = "dashed", alpha = 0.5, color = "darkgreen") +
    labs(
      title = paste("Ensemble Forecast initialized at", 
                   format(unique(plot_data$Forecast_init_datetime)[1], "%Y-%m-%d %H:%M UTC")),
      subtitle = paste("Gridpoint:", gridpoint_id, "| Members:", n_members),
      x = "Lead Time (hours)", 
      y = switch(variable,
                "Temperature_C" = "Temperature (°C)",
                "DewPoint_C" = "Dew Point (°C)",
                "Temperature_K" = "Temperature (K)",
                "DewPoint_K" = "Dew Point (K)",
                variable)
    ) +
    theme_minimal(base_size = 11) +
    theme(
      plot.title = element_text(face = "bold", size = 14),
      plot.subtitle = element_text(color = "gray40", size = 11),
      legend.position = if(n_members <= 10) "right" else "none"
    ) +
    scale_x_continuous(breaks = seq(0, 240, 24))
  
  # Create PDF plots for each specified lead time
  pdf_plots <- lapply(pdf_times, function(t) {
    # Filter data for specific lead time
    pdf_data <- plot_data %>%
      filter(abs(lead_time_hrs - t) < 0.1)
    
    # Calculate statistics for this lead time
    mean_val <- mean(pdf_data[[variable]], na.rm = TRUE)
    median_val <- median(pdf_data[[variable]], na.rm = TRUE)
    sd_val <- sd(pdf_data[[variable]], na.rm = TRUE)
    
    # Create the PDF plot
    p_pdf <- ggplot(pdf_data, aes(x = .data[[variable]])) +
      # Histogram
      geom_histogram(aes(y = after_stat(density)), 
                    bins = min(20, ceiling(sqrt(nrow(pdf_data)))), 
                    fill = "lightblue", 
                    color = "darkblue", 
                    alpha = 0.6) +
      # Density curve
      geom_density(color = "darkblue", size = 1.2, alpha = 0.8) +
      # Mean line
      geom_vline(xintercept = mean_val, 
                color = "red", linetype = "solid", size = 1) +
      # Median line
      geom_vline(xintercept = median_val, 
                color = "darkred", linetype = "dashed", size = 0.8) +
      # Add normal distribution overlay for comparison
      stat_function(fun = dnorm, 
                   args = list(mean = mean_val, sd = sd_val),
                   color = "gray40", linetype = "dotted", size = 0.8) +
      labs(
        title = paste0("t+", t, "h"),
        subtitle = paste0("μ=", round(mean_val, 1), "°C, σ=", round(sd_val, 2), "°C"),
        x = NULL,  # Remove individual x labels to save space
        y = "Density"
      ) +
      theme_minimal(base_size = 10) +
      theme(
        plot.title = element_text(size = 11, face = "bold"),
        plot.subtitle = element_text(size = 9, color = "gray50"),
        axis.title = element_text(size = 9),
        axis.text = element_text(size = 8),
        plot.margin = margin(5, 5, 5, 5)
      ) +
      # Set consistent x-axis limits across all PDFs
      coord_cartesian(xlim = c(
        min(plot_data[[variable]], na.rm = TRUE) - 1,
        max(plot_data[[variable]], na.rm = TRUE) + 1
      ))
    
    return(p_pdf)
  })
  
  # Arrange PDFs in a grid
  pdf_grid <- wrap_plots(pdf_plots, ncol = 2, nrow = 2) +
    plot_annotation(
      title = "Probability Distributions at Key Lead Times",
      subtitle = "Red: mean | Dashed red: median | Dotted gray: normal distribution",
      theme = theme(
        plot.title = element_text(size = 12, face = "bold"),
        plot.subtitle = element_text(size = 10, color = "gray50")
      )
    )
  
  # Combine main plot and PDF grid
  combined <- p_main / pdf_grid + 
    plot_layout(heights = c(2, 3)) +
    plot_annotation(
      caption = paste("Data from:", forecast_datetime, "| Variable:", variable),
      theme = theme(plot.caption = element_text(size = 9, hjust = 0.5, color = "gray40"))
    )
  
  return(combined)
}

# Enhanced version with additional statistics
auto_forecast_plot_with_stats <- function(forecast_datetime, 
                                         gridpoint_id, 
                                         members = 0:50,
                                         variable = "Temperature_C",
                                         pdf_times = c(6, 24, 72, 168)) {
  
  # Get the combined plot
  plot_combined <- auto_forecast_plot_with_pdf_separate(
    forecast_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id,
    members = members,
    variable = variable,
    pdf_times = pdf_times
  )
  
  # Extract year from forecast_datetime
  forecast_time <- as.POSIXct(forecast_datetime, tz = "UTC")
  year <- lubridate::year(forecast_time)
  
  # Get the data for statistics
  tidy_data <- tidy_forecast_with_station_grid_city_location(
    target_datetime = forecast_datetime,
    gridpoint_id = gridpoint_id
  )
  
  member_names <- paste0("M", members)
  plot_data <- tidy_data %>%
    filter(Member %in% member_names)
  
  # Calculate spread evolution
  spread_evolution <- plot_data %>%
    group_by(lead_time_hrs) %>%
    summarise(
      spread = sd(.data[[variable]], na.rm = TRUE),
      iqr = IQR(.data[[variable]], na.rm = TRUE),
      .groups = "drop"
    )
  
  # Create spread evolution plot
  p_spread <- ggplot(spread_evolution, aes(x = lead_time_hrs)) +
    geom_line(aes(y = spread), color = "blue", size = 1) +
    geom_line(aes(y = iqr), color = "green", size = 1, linetype = "dashed") +
    labs(
      title = "Ensemble Spread Evolution",
      x = "Lead Time (hours)",
      y = "Spread (°C)",
      subtitle = "Blue: Standard Deviation | Green: IQR"
    ) +
    theme_minimal(base_size = 10) +
    scale_x_continuous(breaks = seq(0, 240, 24))
  
  # Combine all plots
  final_plot <- plot_combined / p_spread +
    plot_layout(heights = c(5, 1))
  
  return(final_plot)
}

# Usage examples:
# Basic version with PDFs
p_pdf <- auto_forecast_plot_with_pdf_separate(
  forecast_datetime = "2021-01-31 00:00:00",
  gridpoint_id = 605,
  pdf_times = c(24, 48, 120, 240)
)

# Enhanced version with spread evolution
# p_enhanced <- auto_forecast_plot_with_stats(
#   forecast_datetime = "2021-01-31 00:00:00",
#   gridpoint_id = 605,
#   pdf_times = c(6, 24, 72, 168)
# )

# Display the plot
print(p_pdf)
```

