```{r}
#rm(list = ls())
#install.packages("readr")
library(readr)
#install.packages("dplyr")
library(dplyr)
#install.packages("lubridate")
library(lubridate)
#install.packages("ggplot2")
library(ggplot2)
```
output: html_document
---
#These are the files starting with "kis". It contains 10-min observations at stations between 2021 and 2024 following the link I sent you. You would have to subset it to match the time resolution of the forecasts, and combine the different years and months together.
#Source: https://dataplatform.knmi.nl/dataset/vochtigheid-en-temperatuur-1-0

#function to import official station data
```{r}
import_knmi_data <- function(date_str, 
                            data_path = "data/ToSend-01-20-2025/", 
                            skip_lines = 22,
                            filter_date = TRUE) {
  
  # Parse the date
  date_obj <- as.Date(date_str)
  
  # Extract year and month for filename
  year_month <- format(date_obj, "%Y%m")
  
  # Construct filename
  filename <- paste0(data_path, "kis_tot_", year_month, ".gz")
  
  # Check if file exists
  if (!file.exists(filename)) {
    stop(paste("File not found:", filename))
  }
  
  # Read the data with fixed width format
  data <- read_fwf(
    filename,
    skip = skip_lines,
    col_positions = fwf_positions(
      start = c(1,    # DTG
                22,   # LOCATION
                36,   # NAME
                84,   # LATITUDE
                105,  # LONGITUDE
                125,  # ALTITUDE
                145,  # U_BOOL_10
                165,  # T_DRYB_10
                185,  # TN_10CM_PAST_6H_10
                205,  # T_DEWP_10
                225,  # T_DEWP_SEA_10
                245,  # T_DRYB_SEA_10
                265,  # TN_DRYB_10
                285,  # T_WETB_10
                305,  # TX_DRYB_10
                325,  # U_10
                345), # U_SEA_10
      end = c(20,   # DTG
              34,   # LOCATION
              83,   # NAME
              103,  # LATITUDE
              123,  # LONGITUDE
              143,  # ALTITUDE
              163,  # U_BOOL_10
              183,  # T_DRYB_10
              203,  # TN_10CM_PAST_6H_10
              223,  # T_DEWP_10
              243,  # T_DEWP_SEA_10
              263,  # T_DRYB_SEA_10
              283,  # TN_DRYB_10
              303,  # T_WETB_10
              323,  # TX_DRYB_10
              343,  # U_10
              NA),  # U_SEA_10 (end of line)
      col_names = c("DTG", "LOCATION", "NAME", "LATITUDE", "LONGITUDE", "ALTITUDE", 
                    "U_BOOL_10", "T_DRYB_10", "TN_10CM_PAST_6H_10", "T_DEWP_10", 
                    "T_DEWP_SEA_10", "T_DRYB_SEA_10", "TN_DRYB_10", "T_WETB_10", 
                    "TX_DRYB_10", "U_10", "U_SEA_10")
    ),
    na = c("", "NA", "-999", "-999.0"),
    col_types = cols(
      DTG = col_datetime(format = "%Y-%m-%d %H:%M:%S"),
      LATITUDE = col_double(),
      LONGITUDE = col_double(),
      ALTITUDE = col_double(),
      U_BOOL_10 = col_integer(),
      T_DRYB_10 = col_double(),
      TN_10CM_PAST_6H_10 = col_double(),
      T_DEWP_10 = col_double(),
      T_DEWP_SEA_10 = col_double(),
      T_DRYB_SEA_10 = col_double(),
      TN_DRYB_10 = col_double(),
      T_WETB_10 = col_double(),
      TX_DRYB_10 = col_double(),
      U_10 = col_double(),
      U_SEA_10 = col_double(),
      .default = col_character()
    ),
    trim_ws = TRUE
  )
  
  # Filter to specific date if requested
  if (filter_date) {
    data <- data %>%
      filter(as.Date(DTG) == date_obj)
  }
  
  # Add some useful derived columns
  data <- data %>%
    mutate(
      date = as.Date(DTG),
      hour = hour(DTG),
      .after = DTG
    )%>%select(-U_SEA_10,-U_BOOL_10,-T_DRYB_SEA_10,-TN_DRYB_10,-TN_10CM_PAST_6H_10,-T_DEWP_SEA_10)
  
  return(data)
}

data <- import_knmi_data("2021-07-31")
data

location_table <- unique(data[, c("LOCATION", "NAME", "LATITUDE", "LONGITUDE","ALTITUDE")])
#location_table
```


#some visualisation tests
```{r}
print(paste("Number of stations:", n_distinct(data$LOCATION)))
print("Station names:")
print(unique(data$LOCATION))


data%>%filter(LOCATION == "201_T_DV")%>%ggplot(., aes(x = DTG, y = T_DRYB_10, color = LOCATION)) +
  geom_line(size = 1) +
  labs(title = "Temperature on June 3, 2021 - All Stations",
       x = "Time",
       y = "Temperature (°C)") +
  theme_minimal()

```


# Build KNMI sensor inventory (all stations -> metadata/)

Samples 4 mid-month days per year (1 per season) across 2021-2024 = 16 days
total, aggregates sensor-level metadata (LOCATION, NAME, lat/lon, ALTITUDE,
data coverage, mean temperature), and writes
`metadata/knmi_station_sensor_inventory.csv`. See `metadata/README.md` for
a full column dictionary and caveats.

Note: KNMI raw files carry no sensor mounting height. ALTITUDE = station
ground elevation (m AMSL). Variables `T_DRYB_10` / `T_DEWP_10` / `U_10`
follow the WMO/KNMI standard 1.5 m screen height by convention, not from
any field in the data.

```{r build-knmi-sensor-inventory, eval=FALSE}
# 4 seasons x 4 years = 16 sample days (mid-month each season).
# Spanning all 4 seasons catches sensors that may only be active part of the year.
sample_dates <- c(
  "2021-01-15","2021-04-15","2021-07-15","2021-10-15",
  "2022-01-15","2022-04-15","2022-07-15","2022-10-15",
  "2023-01-15","2023-04-15","2023-07-15","2023-10-15",
  "2024-01-15","2024-04-15","2024-07-15","2024-10-15"
)

# Build per-day inventory: one row per (LOCATION x sample_date)
all_inv <- list()
for (d in sample_dates) {
  message("Importing ", d, " ...")
  obs <- tryCatch(
    import_knmi_data(d, data_path = "data/ToSend-01-20-2025/"),
    error = function(e) { message("  failed: ", e$message); NULL }
  )
  if (is.null(obs)) next

  all_inv[[d]] <- obs %>%
    filter(!is.na(LOCATION)) %>%
    # station_id = prefix before the first "_" in LOCATION (e.g. "240_T_ISAD" -> "240")
    mutate(station_id = sub("_.*", "", LOCATION)) %>%
    group_by(station_id, LOCATION, NAME, LATITUDE, LONGITUDE, ALTITUDE) %>%
    summarise(
      sample_date = d,
      # n_obs: number of 10-min timestamps in this day (full day = 144 = 24h * 6)
      n_obs       = n(),
      # non-NA counts -- shows which sensors actually report each variable
      n_T_DRYB    = sum(!is.na(T_DRYB_10)),
      n_T_DEWP    = sum(!is.na(T_DEWP_10)),
      n_U_10      = sum(!is.na(U_10)),
      # daily mean temperature, used downstream as a cross-day average for sanity-checking
      T_mean      = mean(T_DRYB_10, na.rm = TRUE),
      .groups     = "drop"
    )
}

# Collapse across sample days: one row per sensor (LOCATION).
# Counts become totals across sampled days; ceiling = 16 * 144 = 2304.
inventory <- bind_rows(all_inv) %>%
  group_by(station_id, LOCATION, NAME, LATITUDE, LONGITUDE, ALTITUDE) %>%
  summarise(
    sample_dates   = paste(sort(unique(sample_date)), collapse = ";"),
    # n_sample_dates: in how many of the 16 sampled days the sensor was present
    n_sample_dates = n_distinct(sample_date),
    total_obs      = sum(n_obs),
    total_T_DRYB   = sum(n_T_DRYB),
    total_T_DEWP   = sum(n_T_DEWP),
    total_U_10     = sum(n_U_10),
    # mean of the per-day mean temperatures -- spans all 4 seasons, so closer to
    # the annual mean (~10 C in NL) than to summer-only mean. Pure sanity check.
    T_mean_sampled = round(mean(T_mean, na.rm = TRUE), 1),
    .groups        = "drop"
  ) %>%
  arrange(suppressWarnings(as.integer(station_id)), LOCATION)

out_path <- "metadata/knmi_station_sensor_inventory.csv"
write.csv(inventory, out_path, row.names = FALSE)

message(sprintf("Saved %d sensor locations across %d stations to %s",
                nrow(inventory),
                n_distinct(inventory$station_id),
                out_path))

# Quick view: Amsterdam (240) and Rotterdam (344) sensors
inventory %>% filter(station_id %in% c("240", "344"))
```

