#only return read from station close to target coord
```{r}
#install.packages("geosphere")
library(geosphere)
#install.packages("dplyr")
library(dplyr)
library(tidyverse)  
#install.packages("ncdf4")
library(ncdf4)


```

# 1. different dates have been observed by different stations

# 2. only limit number of stations has recorded WetBulbTemperature_Celsius

# 3. 2021 data has different varaible names comapre to 22 and 23 data, like ReportEndDateTime and LocalReportEndDateTime

# 4. 2021 data does not have ExternalSiteId,

#import data function
```{r}
import_WOW_day <- function(date_string) {
  # Parse date
  parts <- strsplit(date_string, "-")[[1]]
  year <- parts[1]
  month <- parts[2]
  day <- parts[3]
  
  all_data <- list()
  successful_hours <- c()
  failed_hours <- c()
  
  # Set path based on year
  if (year == "2021") {
    folder <- here("data", paste0("WOW_", year))
    file_ext <- "csv"
    
    # Loop through 00-23 hour files
    for (hour in 0:23) {
      hour_str <- sprintf("%02d", hour)
      file_name <- paste0("WOW_NL_", year, month, day, hour_str, ".", file_ext)
      file_path <- file.path(folder, file_name)
      
      if (file.exists(file_path)) {
        tryCatch({
          data <- read.csv2(file_path, stringsAsFactors = FALSE)
          if (nrow(data) > 0) {
            # Convert "False"/"True" strings to logical
            if("IsOfficial" %in% names(data) && is.character(data$IsOfficial)) {
              data$IsOfficial <- data$IsOfficial == "True"
            }
            
            # Create ExternalSiteId for 2021 data if it doesn't exist
            if(!"ExternalSiteId" %in% names(data)) {
              data <- data %>%
                mutate(
                  lat_rounded = round(as.numeric(Latitude), 6),
                  lon_rounded = round(as.numeric(Longitude), 6),
                  ExternalSiteId = paste0("WOW_", lat_rounded, "_", lon_rounded)
                ) %>%
                select(-lat_rounded, -lon_rounded)
            }
            
            all_data[[length(all_data) + 1]] <- data
            successful_hours <- c(successful_hours, hour)
          } else {
            failed_hours <- c(failed_hours, hour)
          }
        }, error = function(e) {
          cat("Error reading", file_name, ":", e$message, "\n")
          failed_hours <- c(failed_hours, hour)
        })
      } else {
        failed_hours <- c(failed_hours, hour)
      }
    }
    
  } else if (year %in% c("2022", "2023")) {
    # Original code for 2022-2023
    if (requireNamespace("RcppSimdJson", quietly = TRUE)) {
      install.packages("RcppSimdJson")
      library(RcppSimdJson)
      json_reader <- function(path) {
        json_text <- readLines(path, warn = FALSE)
        json_text <- paste(json_text, collapse = "")
        RcppSimdJson::fparse(json_text)
      }
    } else {
      install.packages("jsonlite")
      library(jsonlite)
      json_reader <- fromJSON
    }
    
    folder <- here("data", paste0("WOW_", year), year)
    file_ext <- "json"
    
    for (hour in 0:23) {
      hour_str <- sprintf("%02d", hour)
      file_name <- paste0("WOW_NL_", year, month, day, hour_str, ".", file_ext)
      file_path <- file.path(folder, file_name)
      
      if (file.exists(file_path)) {
        tryCatch({
          if (file.info(file_path)$size == 0) {
            failed_hours <- c(failed_hours, hour)
            next
          }
          
          json_data <- json_reader(file_path)
          
          if (!is.null(json_data$Object)) {
            all_data[[length(all_data) + 1]] <- json_data$Object
            successful_hours <- c(successful_hours, hour)
          } else {
            failed_hours <- c(failed_hours, hour)
          }
          
        }, error = function(e) {
          failed_hours <- c(failed_hours, hour)
        })
      } else {
        failed_hours <- c(failed_hours, hour)
      }
    }
  } else {
    cat("Unsupported year:", year, "\n")
    return(NULL)
  }
  
  # Combine all files
  if (length(all_data) > 0) {
    combined_data <- tryCatch({
      do.call(rbind, all_data)
    }, error = function(e) {
      dplyr::bind_rows(all_data)
    })
    
    if (nrow(combined_data) == 0) {
      cat("Warning: Combined data has 0 rows\n")
      return(NULL)
    }
    
    # === HANDLE DATETIME CONVERSIONS FIRST (BEFORE VARIABLE SELECTION) ===
    if (year == "2021") {
      # Check what datetime columns exist in the raw 2021 data
      datetime_cols_2021 <- intersect(names(combined_data), 
                                      c("CreatedDateTime", "ReportEndDateTime", 
                                        "ReportStartDateTime", "LocalReportEndDateTime"))
      
      # For 2021, the original data might have different column names or formats
      # Let's check and handle each possibility
      if ("ReportEndDateTime" %in% names(combined_data)) {
        # Try different possible formats for 2021
        combined_data$ReportEndDateTime <- tryCatch({
          as.POSIXct(combined_data$ReportEndDateTime, 
                    format = "%Y-%m-%dT%H:%M:%S", tz = "UTC")
        }, error = function(e) {
          tryCatch({
            as.POSIXct(combined_data$ReportEndDateTime, 
                      format = "%d-%m-%Y %H:%M:%S", tz = "Europe/Amsterdam") %>%
              with_tz("UTC")
          }, error = function(e2) {
            # If still fails, try another format
            as.POSIXct(combined_data$ReportEndDateTime, tz = "UTC")
          })
        })
      }
      
      if ("CreatedDateTime" %in% names(combined_data)) {
        combined_data$CreatedDateTime <- tryCatch({
          as.POSIXct(combined_data$CreatedDateTime, 
                    format = "%Y-%m-%dT%H:%M:%S", tz = "UTC")
        }, error = function(e) {
          tryCatch({
            as.POSIXct(combined_data$CreatedDateTime, 
                      format = "%d-%m-%Y %H:%M:%S", tz = "Europe/Amsterdam") %>%
              with_tz("UTC")
          }, error = function(e2) {
            as.POSIXct(combined_data$CreatedDateTime, tz = "UTC")
          })
        })
      }
      
      # Handle LocalReportEndDateTime if it exists (2021 specific)
      if ("LocalReportEndDateTime" %in% names(combined_data) && 
          !"ReportEndDateTime" %in% names(combined_data)) {
        combined_data$ReportEndDateTime <- as.POSIXct(combined_data$LocalReportEndDateTime,
                                                      format = "%d-%m-%Y %H:%M:%S",
                                                      tz = "Europe/Amsterdam") %>%
                                          with_tz("UTC")
      }
      
      # Create ReportStartDateTime if missing
      if (!"ReportStartDateTime" %in% names(combined_data)) {
        combined_data$ReportStartDateTime <- combined_data$ReportEndDateTime - 600
      } else if (!is.POSIXct(combined_data$ReportStartDateTime)) {
        combined_data$ReportStartDateTime <- tryCatch({
          as.POSIXct(combined_data$ReportStartDateTime, 
                    format = "%d-%m-%Y %H:%M:%S", 
                    tz = "Europe/Amsterdam") %>%
            with_tz("UTC")
        }, error = function(e) {
          combined_data$ReportEndDateTime - 600
        })
      }
      
    } else {
      # 2022-2023 datetime handling
      combined_data <- combined_data %>%
        mutate(
          ReportStartDateTime = as.POSIXct(ReportStartDateTime, 
                                         format = "%Y-%m-%dT%H:%M:%S", 
                                         tz = "UTC"),
          ReportEndDateTime = as.POSIXct(ReportEndDateTime, 
                                       format = "%Y-%m-%dT%H:%M:%S", 
                                       tz = "UTC"),
          CreatedDateTime = as.POSIXct(CreatedDateTime, 
                                     format = "%Y-%m-%dT%H:%M:%S", 
                                     tz = "UTC")
        )
    }
    
    # === NOW STANDARDIZE VARIABLE NAMES ===
    
    # Define core variables to keep
    core_vars <- c(
      "ExternalSiteId",
      "ReportStartDateTime", 
      "ReportEndDateTime",
      "CreatedDateTime",
      "Latitude",
      "Longitude", 
      "Height",
      "ObservationType",
      "SubmissionType",
      "CollectionName",
      "Version",
      "IsOfficial",
      "IsPublic",
      "IsFlagged",
      "VisibilityCode",
      "WeatherDiary",
      
      # Temperature variables
      "DryBulbTemperature_Celsius",
      "DewPointTemperature_Celsius",
      
      # Humidity
      "RelativeHumidity",
      
      # Pressure
      "AirPressure_Hectopascal",
      "MeanSeaLevelPressure_Hectopascal",
      
      # Rainfall
      "RainfallAmount_Millimetre",
      "RainfallRate_MillimetrePerHour",
      "IsTraceRainfallAmount",
      
      # Wind
      "WindDirection",
      "WindSpeed_MetrePerSecond",
      "WindGust_MetrePerSecond",
      "WindGustDirection",
      
      # Additional variables from 2022-2023
      "SoftwareType",
      "IsDcnn",
      "IsLatestVersion",
      "ExternalId",
      "SoilMoisture_Percent",
      "SoilTemperature10cm_Celsius",
      "PresentWeatherCodeSimple"
    )
    
    # Keep only variables that exist in the data
    vars_to_keep <- intersect(names(combined_data), core_vars)
    combined_data <- combined_data %>%
      select(all_of(vars_to_keep))
    
    # Add missing essential variables as NA if they don't exist
    essential_vars <- c("ExternalSiteId", "ReportEndDateTime", 
                       "Latitude", "Longitude", "DryBulbTemperature_Celsius", 
                       "RelativeHumidity")
    
    for(var in essential_vars) {
      if(!var %in% names(combined_data)) {
        combined_data[[var]] <- NA
        warning(paste("Essential variable", var, "was missing and added as NA"))
      }
    }
    
    # Final filtering - remove official stations
    combined_data <- combined_data %>%
      filter(IsOfficial == FALSE | is.na(IsOfficial))
    
    # Convert numeric columns
    numeric_cols <- c("Latitude", "Longitude", "Height",
                     "DryBulbTemperature_Celsius", "DewPointTemperature_Celsius",
                     "RelativeHumidity", "AirPressure_Hectopascal", 
                     "MeanSeaLevelPressure_Hectopascal",
                     "RainfallAmount_Millimetre", "RainfallRate_MillimetrePerHour",
                     "WindSpeed_MetrePerSecond", "WindGust_MetrePerSecond",
                     "SoilMoisture_Percent", "SoilTemperature10cm_Celsius",
                     "WindDirection")
    
    for(col in numeric_cols) {
      if(col %in% names(combined_data)) {
        combined_data[[col]] <- as.numeric(combined_data[[col]])
      }
    }
    
    # Sort by time and station for consistency
    combined_data <- combined_data %>%
      arrange(ReportEndDateTime, ExternalSiteId)
    
    return(combined_data)
    
  } else {
    cat("No data successfully read for", date_string, "\n")
    return(NULL)
  }
}


system.time({
  x <- import_WOW_day("2021-01-31")
})#8.4
#x%>%filter(ExternalSiteId == 926656002)

x
names(x)
```
#quality control
```{r}
# Quality Flag Definitions
# ========================

# **Flag 0 (Pass):**
# - All checks passed, no rules triggered

# **Flag 1 (Suspicious):**
# 1. Rapid temperature change: >5°C change within 1 hour
# 2. Stuck values: 3 consecutive identical temperature readings  
# 3. Spatial deviation: >5°C difference from median of stations within 5km

# **Flag 2 (Error):**
# 1. Temperature out of bounds: <-50°C or >60°C
# 2. Humidity out of bounds: <0% or >100%
# 3. Wind speed out of bounds: <0 m/s or >50 m/s
# 4. Pressure out of bounds: <870 hPa or >1080 hPa
# 5. Dew point paradox: dew point temperature > dry bulb temperature
# 6. Wind gust paradox: gust speed < average wind speed


# Layer 1: Rule-based Quality Control
qc_layer1 <- function(df) {
  
  # Initialize quality flags
  df$qc_flag <- 0  # 0=pass, 1=suspicious, 2=error
  
  # 1. Physical range checks
  df$qc_flag[df$DryBulbTemperature_Celsius < -50 | 
             df$DryBulbTemperature_Celsius > 60] <- 2
  df$qc_flag[df$RelativeHumidity < 0 | 
             df$RelativeHumidity > 100] <- 2
  df$qc_flag[df$WindSpeed_MetrePerSecond < 0 | 
             df$WindSpeed_MetrePerSecond > 50] <- 2
  df$qc_flag[df$MeanSeaLevelPressure_Hectopascal < 870 | 
             df$MeanSeaLevelPressure_Hectopascal > 1080] <- 2
  df$qc_flag[is.na(df$DryBulbTemperature_Celsius) | 
           is.na(df$RelativeHumidity)] <- 2#check NA
  
  # 2. Physical consistency checks
  # Dew point cannot exceed dry bulb temperature
  df$qc_flag[df$DewPointTemperature_Celsius > 
             df$DryBulbTemperature_Celsius] <- 2
  
  # Wind gust must be >= average wind speed
  df$qc_flag[!is.na(df$WindGust_MetrePerSecond) & 
             df$WindGust_MetrePerSecond < df$WindSpeed_MetrePerSecond] <- 2
  
  # 3. Temporal consistency checks (grouped by station)
  df <- df %>%
    group_by(ExternalSiteId) %>%
    arrange(ReportStartDateTime) %>%
    mutate(
      # Temperature change rate
      temp_change = abs(DryBulbTemperature_Celsius - 
                       lag(DryBulbTemperature_Celsius)),
      time_diff = as.numeric(difftime(ReportStartDateTime, 
                                      lag(ReportStartDateTime), 
                                      units = "hours")),
      # Check hourly change rate (>5°C/hour is suspicious)
      qc_flag = ifelse(!is.na(temp_change) & 
                      time_diff <= 1 & 
                      temp_change > 5, 
                      pmax(qc_flag, 1), qc_flag),
      # Check for stuck values (3 consecutive identical readings)
      temp_const = (DryBulbTemperature_Celsius == lag(DryBulbTemperature_Celsius) &
                   DryBulbTemperature_Celsius == lag(DryBulbTemperature_Celsius, 2)),
      qc_flag = ifelse(!is.na(temp_const) & temp_const, 
                      pmax(qc_flag, 1), qc_flag)
    ) %>%
    ungroup()
  
  # 4. Spatial consistency check (simplified version)
  # For each timestamp, calculate deviation from neighboring stations
  spatial_check <- function(df_time) {
    coords <- df_time[, c("Longitude", "Latitude")]
    dists <- as.matrix(dist(coords))
    
    for(i in 1:nrow(df_time)) {
      # Find neighbors within ~5km
      neighbors <- which(dists[i,] > 0 & dists[i,] < 0.05)  # ~5km in degrees
      if(length(neighbors) > 2) {
        neighbor_temps <- df_time$DryBulbTemperature_Celsius[neighbors]
        temp_diff <- abs(df_time$DryBulbTemperature_Celsius[i] - 
                        median(neighbor_temps, na.rm = TRUE))
        # Temperature difference >5°C from neighbors is suspicious
        if(!is.na(temp_diff) & temp_diff > 5) {
          df_time$qc_flag[i] <- pmax(df_time$qc_flag[i], 1)
        }
      }
    }
    return(df_time)
  }
  
  # Apply spatial check on sampled timestamps (for efficiency)
  sample_times <- sample(unique(df$ReportStartDateTime), 
                        min(50, length(unique(df$ReportStartDateTime))))
  
  df_spatial <- df %>%
    filter(ReportStartDateTime %in% sample_times) %>%
    group_by(ReportStartDateTime) %>%
    group_modify(~spatial_check(.x)) %>%
    ungroup()
  
  # Update original dataframe with spatial check results
  df <- df %>%
    left_join(df_spatial[, c("ExternalSiteId", "ReportStartDateTime", "qc_flag")],
              by = c("ExternalSiteId", "ReportStartDateTime"),
              suffix = c("", "_spatial")) %>%
    mutate(qc_flag = pmax(qc_flag, qc_flag_spatial, na.rm = TRUE))
  
  return(df)
}

# Usage example
library(dplyr)
df_cleaned <- qc_layer1(x)

# Keep only passed and suspicious data for analysis
df_for_analysis <- df_cleaned %>% 
  filter(qc_flag < 2)
```

#Divide station into different qulities
```{r}
station_classification_chen <- function(df_cleaned, reference_stations = NULL) {
  
  station_stats <- df_cleaned %>%
    group_by(ExternalSiteId) %>%
    summarise(
      total = n(),
      pass_count = sum(qc_flag == 0, na.rm = TRUE),
      suspicious_count = sum(qc_flag == 1, na.rm = TRUE),
      fail_count = sum(qc_flag == 2, na.rm = TRUE),
      pass_rate = pass_count / total,
      fail_rate = fail_count / total,
      
      # Critical failure check (physical impossibilities)
      critical_fails = sum(qc_flag == 2 & 
                          (DryBulbTemperature_Celsius < -50 | 
                           DryBulbTemperature_Celsius > 60 |
                           RelativeHumidity < 0 | 
                           RelativeHumidity > 100), na.rm = TRUE)
    ) %>%
    mutate(
      # Three-tier classification
      # quality_category = case_when(
      #   # Stations with critical failures → Low
      #   critical_fails > 0 ~ "Low",
      #   
      #   # Stations with any error flags → Low (your requirement)
      #   fail_count > 0 ~ "Low",
      #   
      #   # High quality: >95% pass rate
      #   pass_rate > 0.95 ~ "High",
      #   
      #   # Medium quality: >85% pass rate
      #   pass_rate > 0.85 ~ "Medium",
      #   
      #   # Otherwise Low
      #   TRUE ~ "Low"
      # ),
      
      quality_category = case_when(
      # Any error flags (fail_count > 0) → Low quality
      fail_count > 0 ~ "Low",
  
      # For stations with NO failures, classify by pass rate:
      # High quality: ≥90% pass rate
      pass_rate >= 0.9 ~ "High",
  
      # Medium quality: ≥70% pass rate but <90%
      pass_rate >= 0.5 ~ "Medium",
  
      # Otherwise Low (pass rate <70%)
      TRUE ~ "Low"
      ),
      
      )
    
  
  return(station_stats)
}

# Usage with your data
station_class <- station_classification_chen(df_cleaned)
station_class
```

#only return read from station close to target coord
```{r}
library(geosphere)
library(dplyr)

import_WOW_nearest_stations <- function(date_string, target_lat, target_lon, 
                                       n_stations = 5, 
                                       quality_filter = TRUE,
                                       min_quality = "Medium") {
  
  # Import WOW data - already standardized with ExternalSiteId
  wow_data <- import_WOW_day(date_string)
  
  if (is.null(wow_data) || nrow(wow_data) == 0) {
    return(NULL)
  }
  
  if (!"ExternalSiteId" %in% names(wow_data)) {
    stop("ExternalSiteId column missing - check import_WOW_day function")
  }
  
  # Apply quality control layer first
  wow_data_qc <- qc_layer1(wow_data)
  
  # Calculate station quality metrics
  station_quality <- wow_data_qc %>%
    filter(!is.na(Latitude) & !is.na(Longitude)) %>%
    group_by(ExternalSiteId) %>%
    summarise(
      Latitude = first(Latitude),
      Longitude = first(Longitude),
      n_obs = n(),
      
      # QC metrics
      pass_count = sum(qc_flag == 0, na.rm = TRUE),
      suspicious_count = sum(qc_flag == 1, na.rm = TRUE),
      fail_count = sum(qc_flag == 2, na.rm = TRUE),
      pass_rate = pass_count / n_obs,
      fail_rate = fail_count / n_obs,
      
      # Data completeness metrics
      temp_completeness = sum(!is.na(DryBulbTemperature_Celsius)) / n_obs,
      humidity_completeness = sum(!is.na(RelativeHumidity)) / n_obs,
      
      # Additional quality indicators
      temp_variance = var(DryBulbTemperature_Celsius, na.rm = TRUE),
      data_availability = sum(!is.na(DryBulbTemperature_Celsius) & 
                             !is.na(RelativeHumidity)) / n_obs,
      .groups = 'drop'
    ) %>%
    mutate(
      # Station classification based on your criteria
      quality_category = case_when(
        fail_count > 0 ~ "Low",              # Any failures → Low
        pass_rate >= 0.9 ~ "High",           # 90%+ pass → High  
        pass_rate >= 0.7 ~ "Medium",         # 70-90% pass → Medium
        TRUE ~ "Low"                         # Otherwise → Low
      ),
      
      # Calculate confidence score for weighted analysis
      confidence_score = case_when(
        quality_category == "High" ~ pass_rate * data_availability,
        quality_category == "Medium" ~ pass_rate * data_availability * 0.7,
        quality_category == "Low" ~ pass_rate * data_availability * 0.3
      ),
      
      # Calculate distance to target
      distance_km = distHaversine(
        cbind(Longitude, Latitude),
        cbind(target_lon, target_lat)
      ) / 1000
    )
  
  # Check if we have any valid stations
  if (nrow(station_quality) == 0) {
    return(NULL)
  }
  
  # Apply quality filter if requested
  if (quality_filter) {
    quality_levels <- c("High", "Medium", "Low")
    min_level_index <- which(quality_levels == min_quality)
    acceptable_levels <- quality_levels[1:min_level_index]
    
    station_quality <- station_quality %>%
      filter(quality_category %in% acceptable_levels)
    
    if (nrow(station_quality) == 0) {
      warning(paste("No stations meeting minimum quality level:", min_quality))
      return(NULL)
    }
  }
  
  # Adjust n_stations if fewer stations are available
  n_available <- min(n_stations, nrow(station_quality))
  
  # Select nearest stations with quality weighting
  # Option 1: Simple distance-based selection
  nearest_station_ids <- station_quality %>%
    arrange(distance_km) %>%
    slice_head(n = n_available) %>%
    pull(ExternalSiteId)
  
  # Option 2: Quality-weighted selection (uncomment to use)
  # nearest_station_ids <- station_quality %>%
  #   mutate(
  #     # Combine distance and quality scores
  #     # Lower distance and higher quality = better score
  #     selection_score = (1 / (distance_km + 1)) * confidence_score
  #   ) %>%
  #   arrange(desc(selection_score)) %>%
  #   slice_head(n = n_available) %>%
  #   pull(ExternalSiteId)
  
  # Return empty if no stations selected
  if (length(nearest_station_ids) == 0) {
    return(NULL)
  }
  
  # Filter QC'd data to only include observations from selected stations
  nearest_obs <- wow_data_qc %>%
    filter(ExternalSiteId %in% nearest_station_ids) %>%
    # Only keep passed and suspicious data (exclude failures)
    filter(qc_flag < 2) %>%
    # Add station metadata
    left_join(
      station_quality %>% 
        select(ExternalSiteId, distance_km, n_obs, 
               pass_rate, fail_rate,
               temp_completeness, humidity_completeness,
               quality_category, confidence_score),
      by = "ExternalSiteId"
    ) %>%
    rename(distance_to_target_km = distance_km) %>%
    mutate(
      target_lat = target_lat,
      target_lon = target_lon,
      search_date = date_string,
      # Add station ranking by distance
      station_rank = dense_rank(distance_to_target_km)
    ) %>%
    arrange(distance_to_target_km, ReportEndDateTime)
  
  return(nearest_obs)
}

# Usage examples:

# Get nearest 5 stations regardless of quality
nearest_all <- import_WOW_nearest_stations(
  date_string = "2021-01-15",
  target_lat = 52.5,
  target_lon = 4.9,
  n_stations = 5,
  quality_filter = FALSE
)

# Get only High and Medium quality stations
nearest_good <- import_WOW_nearest_stations(
  date_string = "2021-01-15", 
  target_lat = 52.5,
  target_lon = 4.9,
  n_stations = 5,
  quality_filter = TRUE,
  min_quality = "Medium"
)

# Get only High quality stations
nearest_best <- import_WOW_nearest_stations(
  date_string = "2021-01-15",
  target_lat = 52.5,
  target_lon = 4.9,
  n_stations = 5,
  quality_filter = TRUE,
  min_quality = "High"
)


#####time is not continuous
```


#find station information in a specific date
```{r}
get_unique_wow_stations <- function(date_str) {
  # import date
  data_day <- import_WOW_day(date_str)
  
  # extract station info
  unique_stations <- data_day %>%
    select(ExternalSiteId,Latitude, Longitude, Height) %>%
    mutate(
      site_id = ExternalSiteId,
      Latitude = as.numeric(Latitude),
      Longitude = as.numeric(Longitude),
      Height = as.numeric(Height)
    ) %>%
    distinct()
  return(unique_stations)
}

unique_stations <- get_unique_wow_stations("2022-07-15")

unique_stations
```


