---
title: "Visualisation 4.3 — CRPS Comparison: Post-Processing Methods vs WOW Max"
author: "Wenkai_Zhong"
output: html_document
---

Two-panel bar chart reproducing the figure from `main_analysis.Rmd`:

- **Top**: Mean CRPS of RAW / EMOS / QR / RF, evaluated against WOW max WBGT
- **Bottom**: % improvement of post-processed methods over the raw ensemble

The summary data (`crps_wow_comparison.rds`, 8 rows = 4 methods × 2 cities)
was pre-computed in `main_analysis.Rmd` via
`analyze_vs_wow() %>% create_wow_comparison_table()` and stored in
`Visualisation_data/`. This file just loads it and plots.

# Setup

```{r setup, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gridExtra)
library(here)
```

# Load summary data

```{r load-data}
data_path <- here("Visualisation_and_its_data", "Visualisation_data")
comparison_wow <- read.csv(file.path(data_path, "comparison_table_vs_wow.csv"))

print(comparison_wow)
```

# 4.3 Plot — CRPS Comparison + Improvement over Raw Ensemble

```{r plot-4.3, fig.width=10, fig.height=8}
plot_data <- comparison_wow %>%
  mutate(method = factor(method, levels = c("RAW", "EMOS", "QR", "RF")))

# Top panel — absolute mean CRPS
p1 <- ggplot(plot_data, aes(x = method, y = CRPS_vs_WOW, fill = method)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(label = sprintf("%.3f", CRPS_vs_WOW)),
            vjust = -0.5, size = 3) +
  facet_wrap(~ city) +
  scale_fill_manual(values = c("RAW"  = "gray60",
                               "EMOS" = "#2ca02c",
                               "QR"   = "#ff7f0e",
                               "RF"   = "#1f77b4")) +
  labs(title    = "CRPS Comparison: All Methods vs WOW Max",
       subtitle = "Lower values indicate better agreement with crowd-sourced maximum WBGT",
       x        = "Method",
       y        = "Mean CRPS (vs WOW max)") +
  theme_minimal() +
  theme(legend.position = "none")

# Bottom panel — % improvement over RAW
p2 <- plot_data %>%
  filter(method != "RAW") %>%
  ggplot(aes(x = method, y = CRPS_improvement_pct, fill = method)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", CRPS_improvement_pct)),
            vjust = -0.5, size = 3) +
  geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5) +
  facet_wrap(~ city) +
  scale_fill_manual(values = c("EMOS" = "#2ca02c",
                               "QR"   = "#ff7f0e",
                               "RF"   = "#1f77b4")) +
  labs(title    = "CRPS Improvement over Raw Ensemble",
       subtitle = "When comparing to WOW max observations",
       x        = "Post-Processing Method",
       y        = "Improvement (%)") +
  theme_minimal() +
  theme(legend.position = "none")

grid.arrange(p1, p2, ncol = 1)
```
